# Material and Methods {#matandmeth}
Based on the earlier made observation in chapter \@ref(intro), it is important to improve __early maturity__ in Swiss beef cattle. 
One possibility for improving a certain trait is to use this trait in a breeding program. 
An important prerequisite for the use of a certain trait in a breeding program is that we can precisely define the trait and that the trait can easily and efficiently be measured.

## Definition of Early Maturity {#defem}
In the context of this project, animals are earlier mature if they reach the state of carcass maturity faster than others. 
Animals reach carcass maturity when their carcass does not get any price reductions due to insufficient or excessive carcass fat. 

Price reductions are dependent on the price formation process of the slaughterhouse.
Since 1994 Swiss large-scale slaughterhouses price beef cattle based on the classification system CHTAX [Kaufmann1995]. 

The meat sector association "Proviande" is responsible for the implementation of CHTAX in the Swiss slaughterhouses and the cattle markets. 
There Proviande employees classify beef carcasses either as live or dead animals to determine their price and record the classification of each animal.
For we are interested in the carcass traits of the slaughtered animal, we only use the data coming from the records in the slaughterhouses.

The first step in the classification system CHTAX is placing the animal in the correct carcass category. 
The distinct carcass categories differ in physiological age at slaughter, sex and weight.
In this project the focus lies on the categories MT and KV [@Proviande2018].

```{r, results='asis'}
tbl_prop_sel <- tibble::data_frame(Abbreviation=c("KV", "JB", "MT", "MA", "OB", "RG", "RV", "VK"), Category=c("calves", "young cattle", "young bulls", "bulls or steers", "young steers", "young heifers", "Heifers or young cows", "cows"), Criteria=c("<161 days old", " >161 days <11 months old, <320 kg live weight", ">161 days old, no incissors", ">161 days old, >0 incissors for bulls, >4 incissors for steers", ">161 days old, <5 incissors", ">161 days old, <5 incissors", ">161 days old, >4 incissors for heifers, <5 incissors for young cows", ">161 days old"))

knitr::kable(tbl_prop_sel)
```

Within each category the animal the Proviande employees visually and gropingly classify the carcass in five classes of carcass fat (Tabelle) and carcass conformation (Tabelle).

The employes determine the class of carcass fat by the area and the accentuation of fat that covers the carcass.

```{r, results='asis', table.cap = "Classification for carcass conformation in CHTAX"}
tbl_prop_sel <- tibble::data_frame(Class = c("C", "H", "T", "A", "X"), Profile=c("very convex", "convex", "linear", "concave", "very concave"), Criteria=c("leg: accentedly wide; back: accentedly wide and full; shoulder: accentedly pronounced","leg: wide; back: wide and full; shoulder: pronounced", "leg: well developed, quite wide; back: average large; shoulder: accentedly pronounced", "leg: moderateley developed, slim, hollow; back: moderateley developed til slim ; shoulder: flat", "leg: poorly developed, very slim, very hollow; back: slim, thin, pointy wither; shoulder: flat, hollow"))

knitr::kable(tbl_prop_sel)
```


```{r, results='asis', table.cap = "Classification for carcass conformation in CHTAX"}
tbl_prop_sel <- tibble::data_frame(Class = c("C", "H", "T", "A", "X"), Profile=c("very convex", "convex", "linear", "concave", "very concave"), Criteria=c("leg: accentedly wide; back: accentedly wide and full; shoulder: accentedly pronounced","leg: wide; back: wide and full; shoulder: pronounced", "leg: well developed, quite wide; back: average large; shoulder: accentedly pronounced", "leg: moderateley developed, slim, hollow; back: moderateley developed til slim ; shoulder: flat", "leg: poorly developed, very slim, very hollow; back: slim, thin, pointy wither; shoulder: flat, hollow"))

knitr::kable(tbl_prop_sel)
```

When the animal does not belong to the optimal class of carcass fat (3) or the maximal class of carcass conformation (C) the carcass of the animal will obtain a lower price per carcass weight.

$\leqq$


## Improvement of Early Maturity


## Fat Coverage 
Why is fat coverage a good trait to describe early maturity? ... (Growth models give the answer)


## Index for Carcass Performance Traits

