---
output:
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE,out.width = "90%",fig.align = "center", fig.pos="H", fig.width = 10)
library(knitr)
library(kableExtra)
library(ggplot2)
library(extrafont)
library(fontcm)
library(dplyr)
```

# Material and Methods {#matandmeth}

## Index {#index}

The index consisted of the six traits carcass fat adults, carcass fat calves, carcass conformation adults, carcass conformation calves, carcass weight adults and carcass weight calves.
The index $I$ was computed for both breeds Angus and Limousin as shown in

\begin{equation}
\label{index}
I=a'\hat{u}
\end{equation}

where $a$ was the vector of economic weights and $\hat{u}$ was the vector of estimated breeding values.
Both vectors had one entry for each trait which took the same place in $a$ and $\hat{u}$ (length of $a$ and $\hat{u}$ = 6).
The estimated breeding values $\hat{u}$ were available for all carcass traits, but the economic weights not.
According to @brascamp1985, the economic weight of a given trait is defined as the change in profit caused by a small change in the population mean of the given trait.

### Material {#indexmat}

#### Payment System CHTAX {#CHTAX}

The only information available to compute the economic weights was the payment system CHTAX which determines the price per kg carcass weight for a beef carcass at large-scale slaughterhouses in Switzerland [@Proviande2015].
Therefore the change in profit was approximated by the difference in price per kg carcass weight determined by CHTAX.
The Swiss meat industry association Proviande is responsible for the implementation of CHTAX in Swiss slaughterhouses. 
Proviande employees subjectiveley classify beef carcasses to determine their price.
They carry out the same procedure for each beef carcass.
Firstly, Proviande employees assign the carcass to a carcass category. 
Carcass categories differ in the animals age at slaughter, number of incisors (front teeth), sex and carcass weight (see table  \@ref(tab:carcasscategory)). 
Secondly, Proviande employees assign the carcass to a carcass conformation class.
The assigned carcass conformation class depends on the accentuation of certain muscles of the carcass (see Table \@ref(tab:conformationclass)).
The meatier the carcass the higher the carcass conformation class.
The lowest carcass conformation class is called X and the highest class is called C.
Thirdly, Proviande employees assign the carcass to a carcass fat class.
Proviande employees determine the class of carcass fat by the area and the accentuation of fat that covers the carcass (see Table \@ref(tab:fatclass)).
The least fatty carcasses belong to carcass fat class 1 and the fattiest carcasses belong to carcass fat class 5.
```{r carcasscategory}
x <- data.frame(Abbreviation=c("KV", "JB", "MT", "MA", "OB", "RG", "RV", "VK"), 
                                   Category=c("Calves", "Young cattle", "Young bulls", "Bulls or steers", 
                                              "Young steers", "Young heifers", "Heifers or young cows", "Cows"), 
                                   Description=c("<161 days old", " >161 days <11 months old, <320 kg live weight", 
                                              ">161 days old, no incissors", 
                                              ">161 days old, >0 incissors for bulls, >4 incissors for steers", 
                                              ">161 days old, <5 incissors", ">161 days old, <5 incissors", 
                                              ">161 days old, >4 incissors for heifers, <5 incissors for young cows", 
                                              ">161 days old"))

kable(x, booktabs=T, caption="Description of carcass categories (Proviande, 2015).")
```
```{r fatclass}
x<-data.frame(Class = c("1", "2", "3", "4", "5"), Description=c("No fat coverage","Light fat coverage; muscels partially visible", "Average even fat coverage; muscles generally covered", "Strong fat coverage; excessive fat deposition", "Fat coverage generally excessive; bulging fat formations"))
kable(x, booktabs=T, caption="Description of carcass fat classes (Proviande, 2015).")
```
```{r conformationclass}
x<-data.frame(Class = c("C", "H","T","A","X"), Description=c("Leg: accentedly wide; back: accentedly wide and full; shoulder: accentedly pronounced","Leg: wide; back: wide and full; shoulder: pronounced", "Leg: well developed, quite wide; back: average large; shoulder: accentedly pronounced", "Leg: moderateley developed, slim, hollow; back: moderateley developed til slim ; shoulder: flat", "Leg: poorly developed, very slim, very hollow; back: slim, thin, pointy wither; shoulder: flat, hollow"))
kable(x, booktabs=T, caption="Description of carcass conformation classes (Proviande, 2015). Class T is divided into T+, T and T-.")
```
The values in carcass weight, carcass conformation and carcass fat all influence the price of a beef carcass in the slaughterhouses.
The price changes weekly for the different carcass fat classes and carcass conformation classes. 
The prices used in this Master Thesis were taken from August 2018 [@Proviande2018].
The ones depending on carcass weight were taken from August 2016 [@Proviande2016].
For each carcass category these prices differed.
MT, OB and RG formed the group *adults* and KV formed the group *calves*.
The mean of OB, RG and MT was formed to get the prices of the group *adults*.
To form the prices depending on carcass weight of *calves* it was assumed that their mean carcass conformation class was T+.
Not the absolute prices are shown, but the price reductions or increases depending on a reference price of a class or range of kg carcass weight.
The resulting prices depending on the carcass trait are shown in Figures \@ref(fig:cfprice), \@ref(fig:ccprice), \@ref(fig:cwaprice) and \@ref(fig:cwcprice).
They show that there are decreasing relative prices for too high carcass weights, increasing relative prices for increasing carcass conformation classes and high relative prices for carcass fat class 3 and the classes close to 3: 2 and 1.

```{r cfprice,fig.cap="Price reductions in carcass fat classes with class 3 as reference within the animal groups adults and calves."}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CFc_price_file <- system.file("extdata","CFc_price.csv", package="Exemplary")
CFc_price  <- read_csv2(file = CFc_price_file)
CFc_price$Group <- rep("Calves",times=5)
CFa_price_file <- system.file("extdata","CFa_price.csv", package="Exemplary")
CFa_price  <- read_csv2(file = CFa_price_file)
CFa_price$Group <- rep("Adults",times=5)
CF_price <- rbind(CFc_price,CFa_price)
Class <- rep(c(1:5),times=2)
x <- cbind(CF_price,Class)
g <- ggplot(x,aes(Class,price))
g + geom_bar(stat="identity")+
  theme_classic()+theme(text = element_text(size = 20))+
   facet_grid(.~Group)+
  ylab("Price reduction in Sfr. / kg")+
  xlab("Carcass fat class")+theme(text=element_text(family="CM Roman"))
```

```{r ccprice,fig.cap="Price increases in carcass conformation classes with class X as reference within the animal groups adults and calves."}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CCc_price_file <- system.file("extdata","CCc_price.csv", package="Exemplary")
CCc_price  <- read_csv2(file = CCc_price_file)
CCc_price$price <- CCc_price$price-min(CCc_price$price)
CCc_price$Group <- rep("Calves",times=7)
CCa_price_file <- system.file("extdata","CCa_price.csv", package="Exemplary")
CCa_price  <- read_csv2(file = CCa_price_file)
CCa_price$price <- CCa_price$price-min(CCa_price$price)
CCa_price$Group <- rep("Adults",times=7)
CC_price <- rbind(CCc_price,CCa_price)
Class <- rep(c("X","A","T-","T","T+","H","C"),times=2)
x <- cbind(CC_price,Class)
g <- ggplot(x,aes(x=factor(Class,levels=c("X","A","T-","T","T+","H","C")),price))
g + geom_bar(stat="identity")+
  facet_grid(.~Group)+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Price increase in Sfr. / kg")+
  xlab("Carcass conformation class")+theme(text=element_text(family="CM Roman"))
```

```{r cwaprice,fig.cap="Price reductions in ranges of kg carcass weight with < 290 kg as reference for the animal group adults."}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CWa_price_file <- system.file("extdata","CWa_price.csv", package="Exemplary")
CWa_price  <- read_csv2(file = CWa_price_file)
CWa_price$Group <- rep("Adults",times=11)
CWa_threshold_file <- system.file("extdata","CWa_threshold.csv", package="Exemplary")
CWa_threshold  <- read_csv2(file = CWa_threshold_file)
CWa_threshold[10,] <- ">380"
CWa_threshold <- rbind("<290",CWa_threshold)
CWa_threshold$threshold <- factor(CWa_threshold$threshold,levels=CWa_threshold$threshold)
CWa <- cbind(CWa_price,CWa_threshold)

CWa_plot <- ggplot(CWa,aes(threshold,price))
CWa_plot + geom_bar(stat="identity")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Price reduction in Sfr. / kg")+
  xlab("Carcass weight in kg")+theme(text=element_text(family="CM Roman"))
```

```{r cwcprice,fig.cap="Price reductions in ranges of kg carcass weight with < 140 kg as reference for the animal group calves."}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CWc_price_file <- system.file("extdata","CWc_price.csv", package="Exemplary")
CWc_price  <- read_csv2(file = CWc_price_file)
CWc_price$Group <- rep("Calves",times=12)
CWc_threshold_file <- system.file("extdata","CWc_threshold.csv", package="Exemplary")
CWc_threshold  <- read_csv2(file = CWc_threshold_file)
CWc_threshold[11,] <- ">150"
CWc_threshold <- rbind("<140",CWc_threshold)
CWc_threshold$threshold <- factor(CWc_threshold$threshold,levels=CWc_threshold$threshold)
CWc <- cbind(CWc_price,CWc_threshold)
CWc_plot <- ggplot(CWc,aes(threshold,price))
CWc_plot + geom_bar(stat="identity")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Price reduction in Sfr. / kg")+
  xlab("Carcass weight in kg")+theme(text=element_text(family="CM Roman"))
```

#### Population Distributions {#popdist}

The two breeds Angus and Limousin received the same prices, but their populations showed different distributions of the groups *calves* and *adults*.
These distributions were used to compute their economic weights respectiveley. 
The economic weights were derived from the carcass trait records of animals which were slaughtered between 2010 and 2015.
The number of animals are shown in Table \@ref(tab:numberofanimals).

```{r numberofanimals}
library(tidyr)
library(knitr)
library(kableExtra)
file_name <- system.file("extdata","number_of_animals.csv", package="Exemplary")
number_of_animals <- read.table(file = file_name, sep=";", header=TRUE)
number_of_animals <- data.frame(Breed=c("Angus", "Limousin"), Adults=c(26685, 85082), Calves=c(1957,3730))
kable(number_of_animals, booktabs=T, caption="Number of animals per breed and animal group which records were used to determine their population distributions in carcass traits.")%>%
kable_styling(latex_options=c("hold_position"))
```

While the population distributions for carcass fat and carcass conformation were determined as discrete distributions with known frequencies for each class (see Figures \@ref(fig:cffrequencies) and \@ref(fig:ccfrequencies)), the population distributions for carcass weight were assumed to be a normal distribution with a given mean and a given standard deviation (see Table \@ref(tab:cwmeansd)).

```{r cwmeansd}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
mean_sd <- system.file("extdata","mean_sd.csv", package="Exemplary")
mean_sd  <- read_csv2(file = mean_sd)
mean_sd$Mean[7:12]
mean_sd <- data.frame(Trait=c("aCF","cCF","aCC","cCC","aCW","cCW"),Unit=c("Class","Class","Class","Class","kg","kg") ,Mean=mean_sd$Mean[7:12], SD=mean_sd$Sd[7:12],Mean=mean_sd$Mean[1:6],SD=mean_sd$Sd[1:6])
colnames(mean_sd) <- c("Trait","Unit","Mean","SD","Mean","SD")
kable(mean_sd,booktabs=T,caption="Population mean and standard deviation for the traits cCC = Carcass conformation calves, aCC = Carcass conformation adults, cCF = Carcasss fat calves, aCF = Carcass fat adults, cCW = Carcass weight calves, aCW = Carcass weight adults in Angus and Limousin.")%>%
kable_styling(latex_options=c("hold_position"))%>%
 add_header_above(c("","","Angus"=2,"Limousin"=2))
```

```{r cffrequencies, fig.cap="Population frequencies of Angus and Limousin in carcass fat classes."}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
# Angus Adults
AN_CFa <- system.file("extdata","AN_CFa_freq.csv", package="Exemplary")
AN_CFa  <- read_csv2(file = AN_CFa)
colnames(AN_CFa) <- "Frequency"
AN_CFa$Breed <- c(rep("Angus",times=5))
AN_CFa$Group <- c(rep("Adults",times=5))
AN_CFa$Class <- c(1:5)

# Angus Calves
AN_CFc <- system.file("extdata","AN_CFc_freq.csv", package="Exemplary")
AN_CFc  <- read_csv2(file = AN_CFc)
colnames(AN_CFc) <- "Frequency"
AN_CFc$Breed <- c(rep("Angus",times=5))
AN_CFc$Group <- c(rep("Calves",times=5))
AN_CFc$Class <- c(1:5)

# Limousin Adults
LM_CFa <- system.file("extdata","LM_CFa_freq.csv", package="Exemplary")
LM_CFa  <- read_csv2(file = LM_CFa)
colnames(LM_CFa) <- "Frequency"
LM_CFa$Breed <- c(rep("Limousin",times=5))
LM_CFa$Group <- c(rep("Adults",times=5))
LM_CFa$Class <- c(1:5)

# Limousin Calves
LM_CFc <- system.file("extdata","LM_CFc_freq.csv", package="Exemplary")
LM_CFc  <- read_csv2(file = LM_CFc)
colnames(LM_CFc) <- "Frequency"
LM_CFc$Breed <- c(rep("Limousin",times=5))
LM_CFc$Group <- c(rep("Calves",times=5))
LM_CFc$Class <- c(1:5)

# Barplot
x <- rbind(AN_CFa,AN_CFc,LM_CFa,LM_CFc)
g <- ggplot(x,aes(Class,Frequency))
g + geom_bar(stat="identity",aes(fill=Group),position="dodge")+
  facet_grid(.~Breed)+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Population frequency")+
  xlab("Carcass fat class")+theme(text=element_text(family="CM Roman"))
```

```{r ccfrequencies, fig.cap="Population frequencies of Angus and Limousin in carcass conformation classes."}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
# Angus Adults
AN_CCa <- system.file("extdata","AN_CCa_freq.csv", package="Exemplary")
AN_CCa  <- read_csv2(file = AN_CCa)
colnames(AN_CCa) <- "Frequency"
AN_CCa$Breed <- c(rep("Angus",times=7))
AN_CCa$Group <- c(rep("Adults",times=7))
AN_CCa$Class <- c("X","A","T-","T","T+","H","C")

# Angus Calves
AN_CCc <- system.file("extdata","AN_CCc_freq.csv", package="Exemplary")
AN_CCc  <- read_csv2(file = AN_CCc)
colnames(AN_CCc) <- "Frequency"
AN_CCc$Breed <- c(rep("Angus",times=7))
AN_CCc$Group <- c(rep("Calves",times=7))
AN_CCc$Class <- c("X","A","T-","T","T+","H","C")

# Limousin Adults
LM_CCa <- system.file("extdata","LM_CCa_freq.csv", package="Exemplary")
LM_CCa  <- read_csv2(file = LM_CCa)
colnames(LM_CCa) <- "Frequency"
LM_CCa$Breed <- c(rep("Limousin",times=7))
LM_CCa$Group <- c(rep("Adults",times=7))
LM_CCa$Class <- c("X","A","T-","T","T+","H","C")

# Limousin Calves
LM_CCc <- system.file("extdata","LM_CCc_freq.csv", package="Exemplary")
LM_CCc  <- read_csv2(file = LM_CCc)
colnames(LM_CCc) <- "Frequency"
LM_CCc$Breed <- c(rep("Limousin",times=7))
LM_CCc$Group <- c(rep("Calves",times=7))
LM_CCc$Class <- c("X","A","T-","T","T+","H","C")

# Barplot
x <- rbind(AN_CCa,AN_CCc,LM_CCa,LM_CCc)
g <- ggplot(x,aes(x=factor(Class,levels=c("X","A","T-","T","T+","H","C")),Frequency))
g + geom_bar(stat="identity",aes(fill=Group),position="dodge")+
  facet_grid(.~Breed)+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Population frequency")+
  xlab("Carcass conformation class")+theme(text=element_text(family="CM Roman"))
```

### Method {#indexmet}

Regarding the mentioned material for the determination of economic weights in Section \@ref(CHTAX), the economic weights $a$ in the *Index over carcass traits* were computed as
\begin{equation}
\label{economicweight}
a=\frac{r_1'p-r_0'p}{\Delta_{\mu}}
\end{equation}
where $\Delta_{\mu}$ was a small increase in the present population mean of a trait (set to 0.1 [class] for carcass conformation and carcass fat and to 1 kg for carcass weight), $r_0$ was the vector of population frequencies belonging to each range in trait with the same price of the initial population distribution (= vector of price range), $r_1$ was the vector of population frequencies belonging to each price range after the increase in population mean and $p$ was the vector of relative prices within thresholds per kg carcass weight.
Normal distributions were assumed for all carcass traits.
They were determined by the population means and standard deviations contained in Section \@ref(popdist).
As an example this step is shown for the group *adults*, breed Angus and trait carcass fat in Figure \@ref(fig:normdistapprox).
To get the frequencies of $r_1$ for each price range in these distributions, thresholds defining the price ranges were needed.
These thresholds define at which point the price changes in the range of the normal distributions.
While the thresholds of carcass weight were available, they were not available for carcass fat and carcass conformation.
There the tresholds have been set in a way, that the population frequencies known by the discrete distribution (shown in Figures \@ref(fig:cfprice) and \@ref(fig:ccprice)) had the same value as the population frequencies in the approximated normal distribution (see Figure \@ref(fig:normdistapprox)).
The mean of the normal distributions was increased by $\Delta_{\mu}$ which resulted in the new distribution.
Thresholds were assumed to be constant, but the population frequencies within the thresholds changed (shown in Figure \@ref(fig:thresholdsconstant)). 
The population frequencies within each price class have been computed again using the characteristics of the normal distribution and using the computed thresholds.
The population frequencies from the initial distribution $r_0$ and the changed distribution $r_1$ enabled the computation of the mean price per kg carcass weight for a change in the population mean by $\Delta_{\mu}$.
Finally this price change was scaled up to unit entities ([class],[kg]).

```{r normdistapprox, fig.cap="Exemplary approximation of a normal distribution to a discrete distribution for the group adults, breed Angus and trait carcass fat.", echo=FALSE}
library(ggplot2)
mean_sd <- system.file("extdata","mean_sd.csv", package="Exemplary")
mean_sd  <- read_csv2(file = mean_sd)
mean_sd <- as.matrix(mean_sd)
AncfaS <- as.numeric(mean_sd[7,4])
AncfaM <- as.numeric(mean_sd[7,3])
# Angus Adults
AN_CFa <- system.file("extdata","AN_CFa_freq.csv", package="Exemplary")
AN_CFa  <- read_csv2(file = AN_CFa)
colnames(AN_CFa) <- "Frequency"
AN_CFa$Breed <- c(rep("Angus",times=5))
AN_CFa$Group <- c(rep("Adults",times=5))
AN_CFa$Class <- c(1:5)
x <- AN_CFa
g <- ggplot(x,aes(Class,Frequency))
g + geom_bar(stat="identity", width=0.5, fill="tomato2") +
  stat_function(fun = dnorm, args = list(mean = AncfaM, sd = AncfaS))+
  theme_classic()+
  ylab("Population frequency")+
  xlab("Carcass fat class")+theme(text = element_text(size = 20))+theme(text=element_text(family="CM Roman"))
```

```{r thresholdsconstant, fig.cap="Exemplary distribution shift whith constant thresholds for the group adults, breed Angus and trait carcass fat.", echo=FALSE}
library(ggplot2)
mean_sd <- system.file("extdata","mean_sd.csv", package="Exemplary")
mean_sd  <- read_csv2(file = mean_sd)
mean_sd <- as.matrix(mean_sd)
AncfaS <- as.numeric(mean_sd[7,4])
AncfaM <- as.numeric(mean_sd[7,3])
CFa_price_file <- system.file("extdata","CFa_price.csv", package="Exemplary")
CFa_price  <- read_csv2(file = CFa_price_file)
CFa_price$Group <- rep("Adults",times=5)
CFa_price$Class <- c(1:5)

g <- ggplot(CFa_price,aes(Class,price,linetype=NULL))
g+
  geom_bar(stat="identity",show_guide=FALSE,aes(linetype=NULL))+
 ylab("Relative price in Sfr. / kg")+
  xlab("Carcass fat class") + 
  stat_function(fun = dnorm, args = list(mean = AncfaM, sd = AncfaS), aes(linetype="Initial distribution"))+
  stat_function(fun = dnorm, args = list(mean = AncfaM+0.3, sd = AncfaS),aes(linetype="New distribution"))+
    scale_linetype_manual(values=c(NULL=NULL,"Initial distribution"="solid","New distribution"="dashed"), guide = guide_legend(title=NULL))+
  theme_classic()+theme(text = element_text(size = 20))+theme(text=element_text(family="CM Roman"))
```


## Genetic Gain {#gengain}

The value of genetic gain $Q$ predicts an aggregate genotype's improvement in a population in Sfr. / year [@Hazel1943].
For both strategies CFAT and IOCT this improvement was defined as an increase in the aggregate genotype $H$

\begin{equation}
\label{agggenotype}
H=a'u
\end{equation}

where $a$ was the vector of economic weights and $u$ was the vector of true breeding values.
Both vectors had one entry for each trait which took the same places in $a$ and $u$ (length of $a$ and $u$ = 6).

### Material {#matgengain}

Beside the economic weights (see Table \@ref(tab:ecweightstab)), residual and genetic variances / covariances of the six carcass traits were used to compute the genetic gain for the two strategies (see Tables \@ref(tab:genvarcov) and \@ref(tab:resvarcov)).
Estimated variance components and predicted breeding values for all traits from the periodic routine genetic evaluation were used [@Kunz2018].

```{r ecweightstab}
library(knitr)
AN_economic_weights_file <- system.file("extdata","AN_economic_values", package="Exemplary")
AN_economic_weights <- read.table(file = AN_economic_weights_file, sep=";", header=TRUE)
AN_economic_weights <- as.matrix(AN_economic_weights)
AN_economic_weights <- as.vector(AN_economic_weights)
LM_economic_weights_file <- system.file("extdata","LM_economic_values", package="Exemplary")
LM_economic_weights <- read.table(file = LM_economic_weights_file, sep=";", header=TRUE)
LM_economic_weights <- as.matrix(LM_economic_weights)
LM_economic_weights <- as.vector(LM_economic_weights)
table <- data.frame(Trait= c("Calves conformation [(Sfr. / kg carcass weight) / conformation class]", "Adults conformation [(Sfr. / kg carcass weight) / conformation class]", "Calves fat [(Sfr. / kg carcass weight) / fat class]", "Adults fat [(Sfr. / kg carcass weight) / fat class]", "Calves weight [(Sfr. / kg carcass weight) / kg carcass weight]", "Adults weight [(Sfr. / kg carcass weight) / kg carcass weight]"),Angus=AN_economic_weights,Limousin=LM_economic_weights)
kable(table, digits=2, booktabs=T,caption="Economic weights in Sfr. per trait unit determining the index for the strategy Index over carcass traits.")
```

```{r genvarcov}
genetic_var_cov <- system.file("extdata","adults_calves_genetic_variances_covariances", package="Exemplary")
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
# Add first column with names
Trait <- c("cCC","aCC","cCF","aCF","cCW","aCW")
genetic_var_cov <- cbind(Trait,genetic_var_cov)
kable(genetic_var_cov, digits=3, booktabs=T, caption="Genetic variance / covariance matrix for the traits cCC = Carcass conformation calves, aCC = Carcass conformation adults, cCF = Carcasss fat calves, aCF = Carcass fat adults, cCW = Carcass weight calves, aCW = Carcass weight adults, variance component estimation done by Kunz (2018).")
```

```{r resvarcov}
residual_var_cov <- system.file("extdata","adults_calves_residual_variances_covariances", package="Exemplary")
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
# Add first column with names
Trait <- c("cCC","aCC","cCF","aCF","cCW","aCW")
residual_var_cov <- cbind(Trait,residual_var_cov)
kable(residual_var_cov, digits=3, booktabs=T, caption="Residual variance / covariance matrix for the traits cCC = Carcass conformation calves, aCC = Carcass conformation adults, cCF = Carcasss fat calves, aCF = Carcass fat adults, cCW = Carcass weight calves, aCW = Carcass weight adults, variance component estimation done by Kunz (2018).")
```



### Methods {#metgengain}

The genetic gain was computed considering the "Bulmer effect" [@Bulmer1971].
This effect was considered, because it accounts for the decrease of genetic variance to a limit value during selection.
The resulting asymptotic genetic gain $Q_H^*$ was computed using the equation for two selection paths (derived from @VonRohr1998).
It was expressed as

\begin{equation}
\label{geneticgain}
Q_H^*= \frac {\sum_{y=1}^{2} i_y\sqrt{Var(I)^*}_y}{\sum_{y=1}^{2}L_y}
\end{equation}

where $i$ was the selection intensity, $Var(I)^*$ was the asymptotic variance of the selection index $I$, $L$ was the generation intervall, $y$ was the selection path with 1 = male and 2 = female and $*$ indicated, that the value was corrected for the "Bulmer effect".
From its value correlated genetic gains $Q_m^*$ were computed for all carcass traits $m$ individually using the equation

\begin{equation}
\label{corrgeneticgain}
Q^*_m=Q_H^*Cov(u_m,I)^*(Var(I)^*)^{-1}
\end{equation}

where $Cov(u_m,I)^*$ was the asymptotic covariance between a true breeding value of a trait $m$ and the aggregate genotype $H$ and $Var(I)^*$ was again the asymptotic variance of the selection index $I$.

The genetic gain was based on assumptions of a probable future breeding scenario.
It was the same for both breeding strategies.
This breeding scenario was determined by generation intervall $L$, proportion selected, number of offspring and the proportion of calves and adults in the offspring separateley for a male and female selection candidates (see Table \@ref(tab:breedingscenario)).

```{r breedingscenario}
library(dplyr)
# number of offspring
offspring_file <- system.file("extdata","number_of_offspring", package="Exemplary")
male_offspring <- read.table(file = offspring_file, sep=";", header=TRUE) %>%
  select(male)
male_offspring <- as.numeric(male_offspring)
female_offspring <- read.table(file = offspring_file, sep=";", header=TRUE) %>%
  select(female)
female_offspring <- as.numeric(female_offspring)
# generation intervall
generation_intervall <- system.file("extdata","generation_intervall", package="Exemplary")
male_generationintervall <- read.table(file = generation_intervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- read.table(file = generation_intervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)
# proportion calves adults
proportion_file <- system.file("extdata","proportion_calves_adults", package="Exemplary")
proportion_adults <- read.table(file = proportion_file, sep=";", header=TRUE) %>%
  select(adults)
proportion_adults <- as.numeric(proportion_adults)
proportion_calves <- read.table(file = proportion_file, sep=";", header=TRUE) %>%
  select(calves)
proportion_calves <- as.numeric(proportion_calves)
# proportion selected
proportionselected_file <- system.file("extdata","proportion_selected", package="Exemplary")
male_proportionselected <- read.table(file = proportionselected_file, sep=";", header=TRUE) %>%
  select(male)
male_proportionselected <- as.numeric(male_proportionselected)
female_proportionselected <- read.table(file = proportionselected_file, sep=";", header=TRUE) %>%
  select(female)
female_proportionselected <- as.numeric(female_proportionselected)

breeding_scenario <- data.frame(Determinant=c("Generation intervall [y]","Proportion selected","Number of offspring", "Proportion of adults","Proportion of calves"),Male=c(male_generationintervall,male_proportionselected,male_offspring,proportion_adults,proportion_calves),Female=c(female_generationintervall,female_proportionselected,female_offspring,proportion_adults,proportion_calves))
kable(breeding_scenario, digits=3, booktabs=T, caption="Breeding scenario determinants for male and female selection candidates.")

```

There it was assumed that: 

* the population size was infiniteley large, 

* the selection candidates were randomly mated, 

* the generations in the population were discrete, 

* all breeding values were computed using the same amount of information,

* the selection candidates had no record themselves,

* the traits stayed normally distributed after selection and

* an animal could not have a record as both *adult* and *calf*.

While the generation intervall $L$ was therefore determined, the intensity of selection $i$ was computed using the R command `dnorm(qnorm(1-p))/p` where `p` was the proportion selected.
The asymptotic covariance between a true breeding value of a trait $m$ and the aggregate genotype $H$ was computed as

\begin{equation}
\label{covtraitagg}
Cov(u_m,I)^*=b'G^*_m
\end{equation}

and the asymptotic variance of the selection index $I$ was computed as

\begin{equation}
\label{covindex}
Var(I)^*=b'P^*b
\end{equation}

where $P^*$ was the asymptotic variance covariance matrix between the information sources of the selection index $G^*_m$ was the asymptotic variance covariance matrix between a true breeding value and the selection index and $b$ was the vector of index weights to maximize the correlation between $I$ and the aggregate genotype $H$.
The vector of index weights $b$ was computed as

\begin{equation}
\label{regrcoeff}
b=P^{-1}Ga
\end{equation}

where $P$ was the variance covariance matrix between the information sources of $I$, $G$ was the covariance matrix between $I$ and $H$ and $a$ was the vector of economic weights.
Both $P^*$ and $b$ differed between the stratgies *Carcass fat as auxilliary trait* and *Index over carcass traits*, because their selection index $I$ was differently defined.
According to the selection index theory from @Hazel1943 the selection index is defined as linear regression from the information sources to the aggregate genotype $H$.

#### Characterization Of The Two Strategies By Selection Indices

##### Strategy Carcass Fat As Auxilliary Trait

For the strategy *Carcass fat as auxilliary trait* it was assumed that these information sources were the estimated breeding values of carcass fat for both *adults* and *calves*.
This resulted in the selection index

\begin{equation}
\label{selindcf}
I_{CF}= b\hat{u}_{CF}
\end{equation}

where $b$ was the vector of regression coefficients and $\hat{u}_{CF}$ was the vector of estimated breeding values of carcass fat for *adults* and *calves* (length of $b$ and $\hat{u}_{CF}$ = 2).
The assumption "the variance of BLUP computed estimated breeding values is the same as the variance of true breeding values" allowed to set $P^*$ to

\begin{equation}
\label{covcf}
P^*=C^*_{CF}
\end{equation}

where $C^*_{CF}$ was the asymptotic covariance matrix between true and estimated breeding values of the two estimated breeding values in $\hat{u}_{CF}$ (resulted in a 2 x 2 matrix).
Additionally the covariance matrix between selection index and aggregate genotype $G$ could be set to

\begin{equation}
\label{covindaggcf}
G=C_{CF,H}
\end{equation}

and the asymptotic variance covariance matrix between a true breeding value and the selection index could be set to

\begin{equation}
\label{covbvindcf}
G^*_m=C^*_{m,CF}
\end{equation}

where $C_{CF,H}$ was the covariance matrix between the two estimated breeding values in $\hat{u}_{CF}$ and the true breeding values in $H$ (resulted in a 2 x 6 matrix), and $C^*_{m,CF}$ was the covariance matrix between true and estimated breeding values of a trait $m$ and the two estimated breeding values in $\hat{u}_{CF}$ (resulted in a vector of length 2).

##### Strategy Index Over Carcass Traits

For the strategy *Index over carcass traits* the information sources consisted of predicted breeding values based on BLUP  for all traits in the aggregate genotype.
Due to the properties of BLUP breeding values, the matrices $P$ and $G$ were the same.
Therefore the vector of index weights $b$ was equal to  the vector of economic weights $a$. 
This resulted in the selection index

\begin{equation}
\label{selindindex}
I_{Index}= a\hat{u}_{Index}
\end{equation}

where $a$ was the vector of economic weights and $\hat{u}_{Index}$ was the vector of estimated breeding values of all six carcass traits (length of $a$ and $\hat{u}_{Index}$ = 6).
The asymptotic variance covariance matrix between the information sources of the selection index $I$ was set to

\begin{equation}
\label{covind}
P^*=C^*_{Index}
\end{equation}

where $C^*_{Index}$ was the covariance matrix between the six estimated breeding values $\hat{u}_{Index}$ and the true breeding values in $H$ (resulted in a 6 x 6 matrix).

Additionally the asymptotic variance covariance matrix between a true breeding value and the selection index could be set to

\begin{equation}
\label{covbvindind}
G^*_m=C^*_{m,Index}
\end{equation}

where $C^*_{m,CF}$ was the covariance matrix between true and estimated breeding values of a trait $m$ and the two estimated breeding values in $\hat{u}_{Index}$ (resulted in a vector of length 6).

#### Asymptotic Covariance Matrix Between True and Estimated Breeding Values

The asymptotic covariance matrix between true and estimated breeding values of all carcass traits was therefore necessary to compute the covariances in $C^*_{CF}$, $C_{CF,H}$, $C^*_{m,CF}$, $C^*_{Index}$ and $C^*_{m,Index}$.
To get $C^*$ of the male $1$ and female $2$ the following equation was used

\begin{equation}
\label{Casympt}
\begin{bmatrix}
C_1^* \\
C_2^*
\end{bmatrix}
=
\left( 
\begin{bmatrix}
1+1/2k_1  &  1/2k_2 \\
1/2k_1    &  1+1/2k_2
\end{bmatrix}^{-1}
\otimes I_n
\right)
\begin{bmatrix}
C_1 \\
C_2
\end{bmatrix}
\end{equation}

where $k$ was the factor of variance reduction, $n$ was the number of traits involved and $I$ was the identity matrix of dimension $n$ (which is 6).
The factor of variance reduction $k$ was computed using the equation

\begin{equation}
\label{kvarred}
k_y=i_y(i_y-x_y)
\end{equation}

where $x$ was the value of trunctation on the x-axis of the population's normal distribution in standard deviations.
The value of trunctation $x_y$ was computed from the proportion selected using the R command `qnorm(p, lower.tail = FALSE)` where `p` was the proportion selected.
To get the covariance matrix between true and estimated breeding value before selection $C_y$ the following equation was used

\begin{equation}
\label{covmat}
C_y=A_y \otimes V-PEV_y
\end{equation}

where $A$ was the numerator relationship matrix of dimension q x q (q = number of offspring), $\otimes$ symbolized the kronecker multiplication, $V$ was the genetic variance/covariance matrix (see Table \@ref(tab:genvarcov)) and $PEV$ was the prediction error variance matrix.
Ignoring fixed effects the prediction error variance matrix $PEV$ was computed using the equation derived from @Mrode2003

\begin{equation}
\label{kvarred}
PEV_y=(Z_y'R_y^{-1}Z_y+A_y^{-1} \otimes G^{-1})^{-1}[1:n,1:n]
\end{equation}

where $Z$ was the design matrix, $R$ was the residual variance / covariance matrix expanded for all animals in the breeding scenario (see Table \@ref(tab:resvarcov)) and $[1:n,1:n]$ signaled that only the first $n$ rows and columns were used as $PEV$ (belonged to the selection candidate).
The numerator relationship matrix $A$ was computed using the R package `pedigreem`.

## Rank Correlations {#rankcorr}

Rank correlations were used to compare the different rankings of animals using the strategies CFAT and IOCT.

### Material {#matrankcorr}

To compute the rank correlations, breeding values of all six carcass traits were used. 
The originated from a set of each Angus and Limousin Swiss animals.
The set of Angus animals consisted in 83 males and the set of Limousin animals consisted in 354 males.
All these animals had at least 20 descendants and possessed breeding values for all six traits.

### Methods {#metrankcorr}

Rank correlations were computed using the R command `cor(method ="spearman")`.
To get the different ranks, the animals were assigned to a rank according to the values

* breeding value for carcass fat of *adults*,

* breeding value for carcass fat of *calves* or

* index value.














