# Results {#results}

In this section results for index weights, genetic gains and rank correlations for the breeds Angus and Limousin are presented

## Index {#indexresults}

When using an index over all six carcass traits as selection criterion, the index weights are the economic weights for all six carcass traits.
This is the case in strategy *Index over carcass traits*.
In Figure \@ref(fig:ecweightsgensdfig) the economic weights are shown per genetic standard deviation in the Swiss beef population.
Expressing economic weights per genetic standard deviation allows to compare the economic weights not only between breeds but also between traits.

```{r ecweightsgensdfig, fig.cap="Economic weights in Sfr. per genetic standard deviation for all carcass traits."}
library(ggplot2)
AN_economic_weights_file <- system.file("extdata","AN_economic_values", package="Exemplary")
AN_economic_weights <- read.table(file = AN_economic_weights_file, sep=";", header=TRUE)
AN_economic_weights <- as.matrix(AN_economic_weights)
AN_economic_weights <- as.vector(AN_economic_weights)
LM_economic_weights_file <- system.file("extdata","LM_economic_values", package="Exemplary")
LM_economic_weights <- read.table(file = LM_economic_weights_file, sep=";", header=TRUE)
LM_economic_weights <- as.matrix(LM_economic_weights)
LM_economic_weights <- as.vector(LM_economic_weights)
genetic_var_cov <- system.file("extdata","adults_calves_genetic_variances_covariances", package="Exemplary")
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
gen_sd <- sqrt(diag(genetic_var_cov))
AN_table <- data.frame(Trait=rep(c("Conformation","Fat","Weight"),each=2), Group=rep(c("Calves","Adults"),times=3),Weight=AN_economic_weights)
AN_table$Weight <- AN_table$Weight*gen_sd

LM_table <- data.frame(Trait=rep(c("Conformation","Fat","Weight"),each=2), Group=rep(c("Calves","Adults"),times=3),Weight=LM_economic_weights)
LM_table$Weight <- LM_table$Weight*gen_sd

table <- rbind(AN_table,LM_table)
table$Breed <- rep(c("Angus","Limousin"),each=6)

g <- ggplot(table,aes(Trait,Weight))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Sfr. per genetic SD")+facet_grid(.~Group)+
  xlab("Carcass trait")+theme(text=element_text(family="CM Roman"))
```


Figure \@ref(fig:ecweightsgensdfig) shows that carcass conformation was the most important trait for both animal groups and both breeds, followed by carcass fat.
The economic weights for carcass weight showed the lowest absolute values within the groups *adults* and *calves* and were all negative.
The absolute economic weights were higher for *calves* than for *adults*.
Economic weights for all six carcass traits were different between the two breeds Angus and Limousin.
These differences behaved the same for both animal groups *adults* and *calves*.
Firstly, the economic weights for carcass weight were more negative in Limousin than in Angus.
Secondly, the economic weights for carcass conformation were higher in Angus than in Limousin.
Thirdly, the economic weights for carcass fat were higher in Limousin than in Angus.
Additionally the economic weight for carcass fat in the animal group adults and in the breed Angus was negative.

```{r indexweightscffig, fig.cap="Index weights for carcass fat adults and carcass fat calves of strategy Carcass fat as auxiliary trait."}
library(ggplot2)
library(Exemplary)
AN_LM_index_values_file <- system.file("extdata","AN_LM_index_values_CF", package="Exemplary")
AN_LM_index_values <- read.table(file = AN_LM_index_values_file, sep=";", header=TRUE)
#AN_economic_weights <- as.matrix(AN_economic_weights)
#AN_economic_weights <- as.vector(AN_economic_weights)
#genetic_var_cov <- system.file("extdata","adults_calves_genetic_variances_covariances", package="Exemplary")
#genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
#genetic_var_cov <- as.matrix(genetic_var_cov)
#gen_sd <- sqrt(diag(genetic_var_cov))
#gen_sd_cf <- rep(gen_sd[3:4],4)
#table <- data.frame(Trait=rep(c("Conformation","Fat","Weight"),each=2), Group=rep(c("Calves","Adults"),times=3),Weight=AN_economic_weights)
#AN_LM_index_values$Weight <- AN_LM_index_values$Weight*gen_sd_cf

g <- ggplot(AN_LM_index_values,aes(Path,Weight))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Sfr. per genetic SD")+facet_grid(.~Group)+
  xlab("Selection path")+theme(text=element_text(family="CM Roman"))
```

When using an index over the traits carcass fat *calves* and carcass fat *adults*, the index weights maximize the correlation between the index $I$ and the aggregate genotype $H$.
This was the case in strategy *Carcass fat as auxiliary trait*.
In this case the index weights were not the economic weights of carcass fat *calves* and carcass fat *adults*.
These index weights differed between the male and the female selection path, and are shown in Figure \@ref(fig:indexweightscffig).
The index weights of carcass weight adults within breed were higher in the female selection path than in the male selection path.
For the index weights of carcass weight calves the opposite was the case.
This was due to?
In Angus the index weights had lower values than in Limousin.
The carcass fat adults index values of strategy *Carcass fat as auxiliary trait* were higher than the economic weights of carcass fat adults in the *Index over carcass traits*.
For carcass fat calves the opposite was the case in Angus, but not in Limousin.
In Limousin the economic weights of carcass fat calves in *Index over carcass traits* were lower than the index weights for carcass fat calves in *Carcass fat as auxiliary trait*.

## Genetic Gain {#gengainresults}

Both breeding strategies *Index over carcass traits* and *Carcass fat as auxilliary trait* led to positive genetic gains (see Figure \@ref(fig:gengainagggenotypefig)).
This shows that breeding for them would result in generally higher prices per kg carcass weight for beef carcasses in the Swiss breed populations Angus and Limousin.
The genetic gains of both breeds were higher for the strategy *Index over carcass traits* than for the strategy *Carcass fat as auxilliary trait*.
The difference in genetic gain between the two strategies was lower in Limousin than in Angus.

```{r inputgengain}
library(dplyr)
library(Exemplary)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- system.file("extdata","adults_calves_genetic_variances_covariances", package="Exemplary")
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- system.file("extdata","adults_calves_residual_variances_covariances", package="Exemplary")
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)

# herd x year
herdyear_var_cov <- system.file("extdata","adults_calves_herdyear_variances_covariances", package="Exemplary")
herdyear_var_cov <- read.table(file = herdyear_var_cov, sep=";", header=TRUE)
herdyear_var_cov <- as.matrix(herdyear_var_cov)
#residual_var_cov <- residual_var_cov+herdyear_var_cov

# number of offspring
offspring_file <- system.file("extdata","number_of_offspring", package="Exemplary")
male_offspring <- read.table(file = offspring_file, sep=";", header=TRUE) %>%
  select(male)
male_offspring <- as.numeric(male_offspring)
female_offspring <- read.table(file = offspring_file, sep=";", header=TRUE) %>%
  select(female)
female_offspring <- as.numeric(female_offspring)

# proportion selected of offspring
proportionselected_file <- system.file("extdata","proportion_selected", package="Exemplary")
male_proportionselected <- read.table(file = proportionselected_file, sep=";", header=TRUE) %>%
  select(male)
male_proportionselected <- as.numeric(male_proportionselected)
female_proportionselected <- read.table(file = proportionselected_file, sep=";", header=TRUE) %>%
  select(female)
female_proportionselected <- as.numeric(female_proportionselected)

# proportion of adults and calves in offspring
proportion_file <- system.file("extdata","proportion_calves_adults", package="Exemplary")
proportion_adults <- read.table(file = proportion_file, sep=";", header=TRUE) %>%
  select(adults)
proportion_adults <- as.numeric(proportion_adults)
proportion_calves <- read.table(file = proportion_file, sep=";", header=TRUE) %>%
  select(calves)
proportion_calves <- as.numeric(proportion_calves)

# Generation Intervall
generation_intervall <- system.file("extdata","generation_intervall", package="Exemplary")
male_generationintervall <- read.table(file = generation_intervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- read.table(file = generation_intervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)
```

```{r gengainangus}
economic_weights <- system.file("extdata","AN_economic_values", package="Exemplary")
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

Sfr_AN_index <- compute_genetic_gain_overall_index(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)

Sfr_AN_CF <- compute_genetic_gain_overall_CF(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)

# Loop that produces a matrix with all correlated genetic gains
list_of_traits <- colnames(genetic_var_cov)
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_AN_index <- mat_correlated_gen_gain
# Loop that produces a matrix with all correlated genetic gains
list_of_traits <- colnames(genetic_var_cov)
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait_CF(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait_CF(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_AN_CF <- mat_correlated_gen_gain
```

```{r gengainlimousin}
economic_weights <- system.file("extdata","LM_economic_values", package="Exemplary")
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

Sfr_LM_index <- compute_genetic_gain_overall_index(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)

Sfr_LM_CF <- compute_genetic_gain_overall_CF(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)

# Loop that produces a matrix with all correlated genetic gains
list_of_traits <- colnames(genetic_var_cov)
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_LM_index <- mat_correlated_gen_gain
# Loop that produces a matrix with all correlated genetic gains
list_of_traits <- colnames(genetic_var_cov)
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait_CF(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait_CF(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_LM_CF <- mat_correlated_gen_gain
```

```{r gengainagggenotypefig, fig.cap="Genetic gain in Angus and Limousin when selecting for the strategies Index over carcass traits and Carcass fat as auxilliary trait."}
library(ggplot2)
x <-data.frame(Gain=c(Sfr_AN_index,Sfr_LM_index,Sfr_AN_CF,Sfr_LM_CF),Breed=rep(c("Angus", "Limousin"),times=2),Strategy=rep(c("Index over carcass traits","Carcass fat as auxilliary trait"),each=2))
# Plot
g <- ggplot(x,aes(Strategy,Gain))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in Sfr. / y")+theme(text=element_text(family="CM Roman"))

```

Strategy *Carcass fat as auxilliary trait* showed a high genetic gain in carcass fat in contrast to strategy *Index over carcass traits*.
This was more favorable for the mean aggregate genotype of Limousin than of Angus (see Figure \@ref(fig:corrgengaincffig)).
The correlated genetic gains of strategy *Carcass fat as auxilliary trait* did only differ slightly between breeds (see Table \@ref(fig:corrgengaintab)).
The correlated genetic gains for carcass conformation were positive in the group *adults* but negative in the group *calves*.
These gains were on low absolute levels in comparison to the gains in carcass fat.
The correlated genetic gains of carcass weight were also positive for *adults* but negative for *calves*.

```{r corrgengaintab}
library(ggplot2)
library(varhandle)
library(knitr)
library(kableExtra)
table_AN_index <- as.data.frame(Trait_AN_index)
table_AN_index$V2 <- unfactor(table_AN_index$V2)
table_LM_index <- as.data.frame(Trait_LM_index)
table_LM_index$V2 <- unfactor(table_LM_index$V2)
table_AN_CF <- as.data.frame(Trait_AN_CF)
table_AN_CF$V2 <- unfactor(table_AN_CF$V2)
table_LM_CF <- as.data.frame(Trait_LM_CF)
table_LM_CF$V2 <- unfactor(table_LM_CF$V2)
names <- data.frame(Trait=c("Calves conformation [Conformation class / y]", "Adults conformation [Conformation class / y]", "Calves fat [Fat class / y]", "Adults fat [Fat class / y]", "Calves weight [kg carcass weight / y]", "Adults weight [kg carcass weight / y]"))
table <- cbind(names,table_AN_CF$V2,table_LM_CF$V2,table_AN_index$V2,table_LM_index$V2)
colnames(table) <- c("Trait","Angus","Limousin","Angus","Limousin")
kable(table, digits=3, booktabs=T, caption="Correlated genetic gains of Angus and Limousin when selecting for the strategy Carcass fat as auxilliary trait and the strategy Index over carcass traits in trait unit per year.")%>%
 add_header_above(c("","Carcass fat as auxilliary trait"=2,"Index over carcass traits"=2))

```

```{r corrgengaincffig, fig.cap="Correlated genetic gains in Angus and Limousin when selecting for the strategy Carcass fat as auxilliary trait in genetic standard deviation per year."}
# Per genetic standard deviation
library(ggplot2)
library(varhandle)
x <- rbind(Trait_AN_CF,Trait_LM_CF)
x <- as.data.frame(x)
x$Strategy <- rep(c("Index over carcass traits","Carcass fat as auxilliary trait"),each=6)
x$Breed <- rep(c("Angus","Limousin"),each=6)
x$Group <- rep(rep(c("Calves","Adults"),times=3),times=2)
x$Trait <- rep(rep(c("Conformation","Fat","Weight"),each=2),times=2)
colnames(x)[2] <- "Gain"
x$Gain <- unfactor(x$Gain)

SD <- as.matrix(genetic_var_cov)
SD <- diag(SD)
SD <- sqrt(SD)
x$SD <- rep(SD,times=2)
x$GainSD <- x$Gain/x$SD

g <- ggplot(x,aes(Trait,GainSD))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in genetic SD / y")+facet_grid(.~Group)+
  xlab("Carcass trait")+theme(text=element_text(family="CM Roman"))
```

```{r corrgengainindexfig, fig.cap="Correlated genetic gains in Angus and Limousin when selecting for the strategy Index over carcass traits in genetic standard deviation per year."}
# Per genetic standard deviation
library(ggplot2)
library(varhandle)
x <- rbind(Trait_AN_index,Trait_LM_index)
x <- as.data.frame(x)
x$Breed <- rep(c("Angus","Limousin"),each=6)
x$Strategy <- rep(c("Index over carcass traits","Carcass fat as auxilliary trait"),each=6)
x$Group <- rep(rep(c("Calves","Adults"),times=3),times=2)
x$Trait <- rep(rep(c("Conformation","Fat","Weight"),each=2),times=2)
colnames(x)[2] <- "Gain"
x$Gain <- unfactor(x$Gain)

SD <- as.matrix(genetic_var_cov)
SD <- diag(SD)
SD <- sqrt(SD)
x$SD <- rep(SD,times=2)
x$GainSD <- x$Gain/x$SD

g <- ggplot(x,aes(Trait,GainSD))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in gen. SD / y")+facet_grid(.~Group)+
  xlab("Carcass trait")+theme(text=element_text(family="CM Roman"))
```

Strategy *Index over carcass traits* led to positive genetic gains of carcass weight (see Figure \@ref(fig:corrgengainindexfig)).
The correlated gains for the strategy *Index over carcass traits* differed substantially between Angus and Limousin.
Firstly, the correlated genetic gains of carcass weight was lower in Limousin than in Angus.
Secondly, the gain of carcass conformation was higher in Angus than in Limousin.
The opposite could be observed for the gain of carcass fat.
The correlated genetic gain of carcass fat *adults* for Angus was positive.

## Rank Correlations {#rankcorresults}

Rank correlations between predicted breeding values for carcass fat and the index values over all six carcass traits were computed for Angus and Limousin.
The ranks of the 83 Angus animals and the 354 Limousin animals were computed using their predicted breeding values of carcass fat adults, carcass fat calves and using their index value.
The ranks used to compute the rank correlations are shown in  Figures \@ref(fig:rankcorcfaangus), \@ref(fig:rankcorcfcangus), \@ref(fig:rankcorcfalimousin) and \@ref(fig:rankcorcfclimousin).
The ranks were generally very different for the same animals, which is shown by the massive scattering these figures.
The correlation coefficients, also shown in these figures, were higher between the ranks in carcass fat calves and the ranks in the index, than between carcass fat adults and the ranks of the index.
Limousin showed higher rank correlations between both carcass fat traits and the index than Angus.
The rank correlations between carcass fat and index of the Angus animals were not higher than 0.2.


```{r rankcorcfaangus, fig.cap = "Rank correlation (R) and regression (blue line) between the ranks of breeding value carcass fat adults and the index for Angus.",out.width="60%",fig.width=7}
library(dplyr)
tbl_result <- read.table(
  system.file("extdata","AN_tbl_result", package="Exemplary"),
  sep="\t", header=TRUE)
tbl_idx_comp <- read.table(
  system.file("extdata","AN_tbl_idx_comp", package="Exemplary"),
  sep="\t", header=TRUE)
cfa_index_r<- cor(tbl_result$cfa_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
cfc_index_r <- cor(tbl_result$cfc_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
data <- inner_join(tbl_result,tbl_idx_comp,by="tvdnr")
library(ggplot2)
library(tidyr)
library(ggpubr)
library(extrafont)
font_install("fontcm")
# Rank correlation between CF adults and index
cfa_index_plot <- ggscatter(data, x = "cfa_rank", y = "ca_index_rank",
                 add = "reg.line",  # Add regressin line
                 add.params = list(color = "blue", fill = "lightgray")
 )
 # Add correlation coefficient
 cfa_index_plot + annotate(x=10, y=85, 
               label=paste("R = ", round(cfa_index_r,2)), 
               geom="text", size=10)+ 
   theme(text = element_text(size = 20))+
   xlab("Carcass fat adults rank")+
   ylab("Index rank")+theme(text=element_text(family="CM Roman"))
```

```{r rankcorcfcangus, fig.cap = "Rank correlation (R) and regression (blue line) between the ranks of breeding value carcass fat calves and the index for Angus.",out.width="60%",fig.width=7}
library(dplyr)
tbl_result <- read.table(
  system.file("extdata","AN_tbl_result", package="Exemplary"),
  sep="\t", header=TRUE)
tbl_idx_comp <- read.table(
  system.file("extdata","AN_tbl_idx_comp", package="Exemplary"),
  sep="\t", header=TRUE)
cfa_index_r<- cor(tbl_result$cfa_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
cfc_index_r <- cor(tbl_result$cfc_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
data <- inner_join(tbl_result,tbl_idx_comp,by="tvdnr")
library(ggplot2)
library(tidyr)
library(ggpubr)
library(extrafont)
font_install("fontcm")
# Rank correlation between CF calves and index
cfa_index_plot <- ggscatter(data, x = "cfc_rank", y = "ca_index_rank",
                 add = "reg.line",  # Add regressin line
                 add.params = list(color = "blue", fill = "lightgray")
 )
 # Add correlation coefficient
 cfa_index_plot + annotate(x=10, y=85, 
               label=paste("R = ", round(cfc_index_r,2)), 
               geom="text", size=10)+ 
   theme(text = element_text(size = 20))+
   xlab("Carcass fat calves rank")+
   ylab("Index rank")+theme(text=element_text(family="CM Roman"))
```

```{r rankcorcfalimousin, fig.cap = "Rank correlation (R) and regression (blue line) between the ranks of breeding value carcass fat adults and the index for Limousin.",out.width="60%",fig.width=7}
library(dplyr)
tbl_result <- read.table(
  system.file("extdata","LM_tbl_result", package="Exemplary"),
  sep="\t", header=TRUE)
tbl_idx_comp <- read.table(
  system.file("extdata","LM_tbl_idx_comp", package="Exemplary"),
  sep="\t", header=TRUE)
cfa_index_r<- cor(tbl_result$cfa_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
cfc_index_r <- cor(tbl_result$cfc_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
data <- inner_join(tbl_result,tbl_idx_comp,by="tvdnr")
library(ggplot2)
library(tidyr)
library(ggpubr)
library(extrafont)
font_install("fontcm")
# Rank correlation between CF adults and index
cfa_index_plot <- ggscatter(data, x = "cfa_rank", y = "ca_index_rank",
                 add = "reg.line",  # Add regressin line
                 add.params = list(color = "blue", fill = "lightgray")
 )
 # Add correlation coefficient
 cfa_index_plot + annotate(x=40, y=350, 
               label=paste("R = ", round(cfa_index_r,2)), 
               geom="text", size=10)+ 
   theme(text = element_text(size = 20))+
   xlab("Carcass fat adults rank")+
   ylab("Index rank")+theme(text=element_text(family="CM Roman"))
```

```{r rankcorcfclimousin, fig.cap = "Rank correlation (R) and regression (blue line) between the ranks of breeding value carcass fat calves and the index for Limousin.",out.width="60%",fig.width=7}
library(dplyr)
tbl_result <- read.table(
  system.file("extdata","LM_tbl_result", package="Exemplary"),
  sep="\t", header=TRUE)
tbl_idx_comp <- read.table(
  system.file("extdata","LM_tbl_idx_comp", package="Exemplary"),
  sep="\t", header=TRUE)
cfa_index_r<- cor(tbl_result$cfa_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
cfc_index_r <- cor(tbl_result$cfc_rank, tbl_idx_comp$ca_index_rank, method = c("spearman"))
data <- inner_join(tbl_result,tbl_idx_comp,by="tvdnr")
library(ggplot2)
library(tidyr)
library(ggpubr)
library(extrafont)
font_install("fontcm")
# Rank correlation between CF calves and index
cfa_index_plot <- ggscatter(data, x = "cfc_rank", y = "ca_index_rank",
                 add = "reg.line",  # Add regressin line
                 add.params = list(color = "blue", fill = "lightgray")
 )
 # Add correlation coefficient
 cfa_index_plot + annotate(x=40, y=350, 
               label=paste("R = ", round(cfc_index_r,2)), 
               geom="text", size=10)+ 
   theme(text = element_text(size = 20))+
   xlab("Carcass fat calves rank")+
   ylab("Index rank")+theme(text=element_text(family="CM Roman"))
```






