--- 
title: "Early Maturity in Swiss Beef Cattle"
author: "Silvan Wyss"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: "`r system.file('extdata','library.bib',package='Exemplary')`"
biblio-style: apalike
link-citations: yes
github-repo: charlotte-ngs/EarlyMaturityBeef
description: "Master thesis on early maturity in Swiss Beef Cattle."
lof: TRUE
lot: TRUE
---

```{r setup-preq, echo=FALSE, results='hide'}
### # required packages from CRAN
vec_reqpkgs_cran <- c("knitr", "rmarkdown", "roxygen2", "bookdown", "caTools", "citr", "devtools", "tidyverse", "huxtable")
vec_instpkgs <- installed.packages()
for (p in vec_reqpkgs_cran){
  if (!p %in% vec_instpkgs)
    install.packages(pkgs = p, repos = "https://cran.rstudio.com")
}

### # required packages from github
list_reqpkgs_github <- list(repo=c("charlotte-ngs"), package = c("rmddochelper"))
for (idx in seq_along(1:length(list_reqpkgs_github$package))){
  p <- list_reqpkgs_github$package[idx]
  if (!p %in% vec_instpkgs)
    devtools::install_github(paste(list_reqpkgs_github$repo[idx], p, sep = "/"))
}
```

```{r, echo=F}
# R settings
# set PDF as default for graphics
options(knitr.graphics.auto_pdf = TRUE)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

# Summary {-}

Up until summer 2018, the Swiss beef cattle breeders association "Mutterkuh Schweiz" focused their genetic evaluations mainly on growth rate and carcass conformation.  
Lately, it has been observed that carcass fat is decreasing at least for some beef cattle breeds. 
Several stakeholders derive from the decreasing levels of carcass fat, that Swiss beef cattle does not show any improvements in the trait early maturity. 
In the context of the present study, the term "Early maturity" means early maturity of carcasses at slaughter and is related to a carcass classification system.
Two strategies were proposed to breed for early maturity in Switzerland and are evaluated in this Master thesis: *Carcass fat as auxiliary trait* and *Index over carcass traits*.
Economic weights for all carcass traits were computed using the payment system CHTAX in the beef breeds Angus and Limousin.
Two tools were used to predict the effects of the two strategies: The genetic gain and the rank correlations.
The genetic gain of strategy *Index over carcass traits* was higher than of strategy *Carcass fat as auxiliary trait* in both breeds.
The result indicates that the strategy *Index over carcass traits* is more suitable to breed for early maturity than the strategy *Carcass fat as auxiliary trait*.
The most important advantage of strategy *Index over carcass traits* is, that it improves early maturity by increasing carcass traits according to the breed-specific potentials.
Strategy *Carcass fat as auxiliary trait* would mainly increase the trait carcass fat in Swiss beef populations.
In Angus this would not be favorable, because this beef breed population is already sufficiently high in carcass fat.


# Task Description {-}

__Background__

Up until summer 2018, the Swiss beef cattle breeders association has been focusing their genetic evaluations
mainly on traits such as growth rate and proportion of carcass lean meat. There might be evidence that
the level of carcass fatness is decreasing at least for some beef cattle breeds (see @Hospenthal2016 for a
possible source). Decreasing levels of carcass fatness has a negative effect on time of carcass maturity and an
important economic impact for beef cattle producers, because slaughterhouses reduce the price for carcasses
with an insufficient fatness level. To address this problem, beef cattle breeders in Switzerland have decided
to estimate breeding values for carcass fatness. These breeding value estimates represent a first tool for
improving early maturity in beef cattle. The first results of the routine breeding value estimation for carcass
fatness will be published in summer 2018.

__Aim__

This project aims at comparing different breeding strategies for improving early maturity in beef cattle. The
different strategies that are proposed are described in the following section.

__Strategies__

Breeding value estimation for carcass fatness: Starting in summer 2018 breeding values for
carcass fatness are estimated for beef cattle. The estimated breeding values for carcass fatness are a first
tool to improve early maturity. At this stage it is important to describe how the estimated breeding
values of carcass fatness as a single trait can be used to improve early maturity in beef cattle.

• Carcass trait index: In most cases, animal breeders are interested to consider more than one trait
simultaneously for their selection decisions. Selection index theory provides an approach to optimally
combine a set of traits when selecting animals as potential parents.

• Approach by @Berry2017 defined a new trait called “deviation in age
at slaughter” (DAGE). They used this trait to access the genetic potential of selection candidates for
early maturity.

• Growth models: In pigs, @Greef1992 used specialized growth models to quantify the transformation
of nutrients into the deposition of protein and fat in a carcass. The same type of models can also be
applied to beef cattle. Based on the results of these growth models, the property of early maturity can
be derived.

__Requirements__

The following points are required for a successful result of this Masters Thesis
1. The literature in the area of early maturity in meat production in general and specifically for beef cattle
is to be thoroughly reviewed.

2. The relevance of early maturity in beef cattle has to be described in a convincing manner.

3. The proposed strategies for improving early maturity in beef cattle must be described.

4. A Proposal of an implementation of the improvement of early maturity via traits that are easily and
effectively measurable in a sufficiently large population of animals must be given.

5. An Implementation of a carcass trait index consisting of the most characteristic traits for which
observations are currently available must be described.

6. First Addition: Setting up the statistical analysis for the carcass index trait with real data from the
field.

7. Second Addition: Implementation of the approach by @Berry2017 and or
starting to develop the analysis by growth curve models.

__Assessment__

For a successful completion of this Masters Thesis, requirements 1-3 are absolutely required. If requirements
1-5 are fulfilled, the Thesis will be graded as very good. Results from requirements 6 and 7 can be used to
improve the overall grade of the thesis.

