--- 
title: "Early Maturity in Swiss Beef Cattle"
author: "Silvan Wyss"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: "`r system.file('extdata','library.bib',package='Exemplary')`"
biblio-style: apalike
link-citations: yes
github-repo: charlotte-ngs/EarlyMaturityBeef
description: "Master thesis on early maturity in Swiss Beef Cattle."
lof: TRUE
lot: TRUE
---

```{r setup-preq, echo=FALSE, results='hide'}
### # required packages from CRAN
vec_reqpkgs_cran <- c("knitr", "rmarkdown", "roxygen2", "bookdown", "caTools", "citr", "devtools", "tidyverse", "huxtable")
vec_instpkgs <- installed.packages()
for (p in vec_reqpkgs_cran){
  if (!p %in% vec_instpkgs)
    install.packages(pkgs = p, repos = "https://cran.rstudio.com")
}

### # required packages from github
list_reqpkgs_github <- list(repo=c("charlotte-ngs"), package = c("rmddochelper"))
for (idx in seq_along(1:length(list_reqpkgs_github$package))){
  p <- list_reqpkgs_github$package[idx]
  if (!p %in% vec_instpkgs)
    devtools::install_github(paste(list_reqpkgs_github$repo[idx], p, sep = "/"))
}
```

```{r, echo=F}
# R settings
# set PDF as default for graphics
options(knitr.graphics.auto_pdf = TRUE)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

# Summary {-}

Up until summer 2018, the Swiss beef cattle breeders association "Mutterkuh Schweiz" has focused their genetic evaluations on growth rate and carcass conformation.  
Lately, it has been observed that carcass fat is decreasing at least for some beef cattle breeds. 
Several stakeholders derive from the decreasing levels of carcass fat, that Swiss beef cattle does not show any improvements in the trait early maturity. 
In the context of the present study, the term "Early maturity" means early maturity of carcasses at slaughter and is related to a carcass classification system.
Two strategies were proposed to breed for early maturity in Switzerland and are evaluated in this Master thesis: *Carcass fat as auxiliary trait* and *Index over carcass traits*.
Economic weights for all carcass traits were computed using the payment system CHTAX in the beef breeds Angus and Limousin.
Genetic gain was estimated to evaluate both strategies.
Rank correlations were used to assess the differences between the two strategies. 
The genetic gain of strategy *Index over carcass traits* was higher than of strategy *Carcass fat as auxiliary trait* in both breeds.
The result indicates that the strategy *Index over carcass traits* is more suitable to breed for early maturity than the strategy *Carcass fat as auxiliary trait*.
The most important advantage of strategy *Index over carcass traits* is, that it improves early maturity by increasing carcass traits according to the breed-specific potentials in increasing the average price per kg carcass weight.
Strategy *Carcass fat as auxiliary trait* would mainly increase the trait carcass fat in Swiss beef populations.
In Angus this would not be favorable, because this beef breed population is already sufficiently high in carcass fat.
