---
title: "Response to selection"
author: "Silvan"
date: "20 8 2018"
output: html_document
bibliography: 
- /Users/silvan/Documents/EarlyMaturityBeef/References/library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The change produced by selection that chiefly interests us is the change of the population mean. Th is is the response to selection, which will be symbolized by R. It is the difference of mean phenotypic value between the offspring of the selcted parents and the whole of the parental generation before selection. The measure of the selection applied is the average superiority of the selected parents, which is called the selection differential, and will be symbolized by S.
If you can assume that there is no natural selection (fertility and viability not correlated with trait), you can say the ratio of response to selection differential is equal to the heritability [@Falconer1996].
$$R = h^2S$$
Assortative mating can be disregarded, because it has very little effect on the mid-parent regression.
The response to selection is dependent on the parameters:

1. Selection intensity (si)
2. Selection accuracy (sa)
3. Genetic standard deviation (gsd)
4. Generation intervall [y] (gi)
5. The sex of the candidate (m/f)

In this example I calculate the response to selection for the both sexes as shown on page 135 [@VonRohr1998]. The abbreviation "m or f" in front of the parameters will show if the parameter is from a male or female candidate.
The first R chunk will define the necessary paramters:

```{r}
msi <- 1.4
mgi <- 1.25
fsi <- 0.8
fgi <- 1.75
msa <- 500
gsd <- 500
fsa <- 500



```


The second R chunk will calculate the asymptotic response to selection (R) per year for the total breeding value:

```{r}
x <- msi * msa * gsd + fsi * fsa * gsd
y <- mgi + fgi

R<- x/y
print(R)
```


# References

