---
title: "ResponseToSelection_CarcassTraits_Multivariate"
author: "Silvan"
date: "18 10 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
```

# Goal

To compute genetic gains of the traits carcass fatt, carcass conformation and carcass weight.

# Plan

Firstly, to record and name all input parameters either as tables or as variables in separate files.
Secondly, show all necessary equations/descriptions from bottom to top.
Thirdly, create R chunks that read the input parameters and solve the equations.

# Material

* Residual, phenotypic and genetic variances and covariances of all traits.
* Breeding scenario (number of records of offspring/itself/half siblings/full siblings per selection candidate).
* Generation intervall and proportion selected of the population.
* Economic value for each trait

# Implementation

## Input parameters

```{r calvesvariancecomponents, echo=FALSE}
library(knitr)
library(kableExtra)
g<-data.frame(c("cCC","cCF", "cCW"), c(0.4015, -0.00993, 0.01828), c( -0.00993, 0.12067,0.00050), c(0.01828,0.00050,0.00311))
colnames(g) <- c(" ","cCC","cCF", "cCW")

r<-data.frame(c(0.35845, 0.13154, 0.02907), c( 0.35845, 0.23651,0.02463), c(0.02907,0.23651,0.00904))
colnames(r) <- c("cCC","cCF", "cCW")

p<-data.frame(c(0.79947, 0.14951, 0.05394), c( 0.14951, 0.39365,0.02979), c(0.05394,0.02979,0.06395), c(0.50221, 0.30654, 0.22078))
colnames(p) <- c("cCC","cCF", "cCW", "heritability")

cvc<-cbind(g,r,p)
kable(cvc, digits=5, booktabs=T, caption="Genetic and phenotypic variances-covariances for calves (c) derived from Kunz (2018)") %>%
kable_styling(latex_options=c("hold_position")) %>%
 add_header_above(c(" ","genetic"=3,"residual"=3, "phenotypic"=3," ")) %>%
  column_spec(c(1,4,7,10), border_right = T)

```


```{r stirksvariancecomponents, echo=FALSE}
library(knitr)
library(kableExtra)
sg<-data.frame(name=c("sCC","sCF", "sCW"),sCC= c(0.4013, -0.00655, 0.03387), sCF=c( -0.00655, 0.13028,0.01322), sCW=c(0.03387,0.01322,0.01947))
colnames(sg) <- c(" ","sCC","sCF", "sCW")

sr<-data.frame(sCC=c(0.26631, 0.00931, 0.04903),sCF= c( 0.00931, 0.19451,0.02162),sCW= c( 0.04903,0.02162,0.03466))
colnames(sr) <- c("sCC","sCF", "sCW")

sp<-data.frame(sCC=c(0.71754, 0.07159, 0.09911), sCF=c(0.07159, 0.36439,0.04989), sCW=c(0.09911,0.04989,0.06395), heritability=c(0.55928, 0.35752, 0.30447))
colnames(sp) <- c("sCC","sCF", "sCW", "heritability")
svc<-cbind(sg,sr,sp)
kable(svc, digits=5, booktabs=T, caption="Genetic, phenotypic and residual variances-covariances for stirks (s) derived from Kunz (2018)") %>%
 add_header_above(c("","genetic"=3,"residual"=3, "phenotypic"=3,""))

```




