---
title: "Response to selection"
author: "Silvan"
date: "20 8 2018"
output:
  html_document: default
  pdf_document: default
bibliography: /Users/silvan/Documents/EarlyMaturityBeef/References/library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The change produced by selection that chiefly interests us is the change of the population mean. Th is is the response to selection, which will be symbolized by R. 
It is the difference of mean phenotypic value between the offspring of the selcted parents and the whole of the parental generation before selection. 
The measure of the selection applied is the average superiority of the selected parents, which is called the selection differential, and will be symbolized by S.
If you can assume that there is no natural selection (fertility and viability not correlated with trait), you can say the ratio of response to selection differential is equal to the heritability [@Falconer1996].
$$R = h^2S$$
$$S = i\sigma_{P}$$
$$R = ih^2\sigma_{P}$$
$$h = \sigma_{A}/\sigma_{P}$$
$$R = ih\sigma_{A}$$


Assortative mating can be disregarded, because it has very little effect on the mid-parent regression. 
The chief use of this equation is for predicting the response to selection. The knowledge of heritability can be obtained from previous generations. The selection differential can not be known, but its expected value can be predicted.

In the following example you can see how the response to selection for abdominal bristle number in drosophila.

```{r echo=FALSE}
x <- data.frame(c("Parents", "Offspring"), c(35.3, 37.9), c(40.6, "-"), c(5.3, "-"), c(2.8,"-"), c("-", 2.6))
colnames(x) <- c("Generation", "Mean of all measured", "Mean of those selected", "Selection differential", "Experienced response", "Observed response")
library(knitr)
kable(x)

```

```{r}
h2 <- 0.52
S <- 40.6 - 35.3
R <- h2 * S
oR <- 37.9 - 35.3
```

The heritability `r h2` of the bristle number was estimated in the previous generations. The selected parents had a mean superiority of `r S`. The predicted response is S * h2 = `r R`. The observed response was `r oR`.
However this result is only valid for this generation, because heritability is expected to change in each generation.

When a normal distribution of the values for a trait in a population can be assumed, which is usually the case you can derivate the intensity of selection of the proportion selected.

The goal is of course to increase the response to selection when we are breeding. 
Increasing intensity of selection seems at first sight to be a straightforward  way of improving the response.
However there are two factors that limit increasing intensity of selection:
1. The reproductive rate
2. Inbreeding






The response to selection is dependent on the parameters:

1. Selection intensity (si)
2. Selection accuracy (sa)
3. Genetic standard deviation (gsd)
4. Generation intervall [y] (gi)
5. The sex of the candidate (m/f)

In this example I calculate the response to selection for the both sexes as shown on page 135 [@VonRohr1998]. The abbreviation "m or f" in front of the parameters will show if the parameter is from a male or female candidate.
The first R chunk will define the necessary paramters:

```{r}
msi <- 1.4
mgi <- 1.25
fsi <- 0.8
fgi <- 1.75
msa <- 500
gsd <- 500
fsa <- 500



```


The second R chunk will calculate the asymptotic response to selection (R) per year for the total breeding value:

```{r}
x <- msi * msa * gsd + fsi * fsa * gsd
y <- mgi + fgi

R<- x/y
print(R)
```


# References

