---
title: "ResponseToSelection_CarcassTraits_Multivariate"
author: "Silvan"
date: "18 10 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
```

# Goal

To compute genetic gains of the traits carcass fatt, carcass conformation and carcass weight. Each trait for adults and calves. (6 traits in total).

# Plan

* Firstly, to record and name all input parameters either as tables or as variables in separate files.

* Secondly, show all necessary equations/descriptions from bottom to top.

* Thirdly, create R chunks that read the input parameters and solve the equations.

# Material

* Residual, phenotypic and genetic variances and covariances of and between all traits.

* Breeding scenario (number of records of offspring per selection candidate). The scenario will result in a relationsship matrix. For male and female selection paths each a separate relationsship matrix.

* Generation intervall and proportion selected of the population for male and female selection paths.

* Economic value for each trait.

# Implementation

First I import the input parameters using read.table(). 
Then I compute paramteres that do not require equations.
Then I compute all necessary steps using equations (derived from @Phocas1998).

## Input parameters

### Genetic, Residual and Phenotypic Variances/Covariances

With CC,CF,CW.
```{r VariancesCovariances}
# Set working directory
setwd("~/Documents/EarlyMaturityBeef/ResponseToSelection/rmd")
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)
## phenotypic
phenotypic_var_cov <- "adults_calves_phenotypic_variances_covariances"
phenotypic_var_cov <- read.table(file = phenotypic_var_cov, sep=";", header=TRUE)
phenotypic_var_cov <- as.matrix(phenotypic_var_cov)
```

### Number of Offspring

First the number of relatives is imported.
```{r NumberofRelatives}
library(dplyr)
# Set working directory
setwd("~/Documents/EarlyMaturityBeef/ResponseToSelection/rmd")
## male
male_offspring <- "number_of_offspring"
male_offspring <- read.table(file = male_offspring, sep=";", header=TRUE) %>%
  select(male)
male_offspring <- as.numeric(male_offspring)
male_offspring
## female
female_offspring <- "number_of_offspring"
female_offspring <- read.table(file = female_offspring, sep=";", header=TRUE) %>%
  select(female)
female_offspring <- as.numeric(female_offspring)
female_offspring
```


### Generation intervall $L$

```{r GenerationIntervall}
library(dplyr)
# Set working directory
setwd("~/Documents/EarlyMaturityBeef/ResponseToSelection/rmd")
## male
male_generationintervall <- "generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
male_generationintervall
## female
female_generationintervall <- "generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)
female_generationintervall
```



### Proportion selected

```{r ProportionSelected}
library(dplyr)
# Set working directory
setwd("~/Documents/EarlyMaturityBeef/ResponseToSelection/rmd")
## male
male_proportionselected <- "proportion_selected"
male_proportionselected <- read.table(file = male_proportionselected, sep=";", header=TRUE) %>%
  select(male)
male_proportionselected <- as.numeric(male_proportionselected)
male_proportionselected
## female
female_proportionselected <- "proportion_selected"
female_proportionselected <- read.table(file = female_proportionselected, sep=";", header=TRUE) %>%
  select(female)
female_proportionselected <- as.numeric(female_proportionselected)
female_proportionselected
```

### Economic values $a$

```{r}
library(dplyr)
# Set working directory
setwd("~/Documents/EarlyMaturityBeef/ResponseToSelection/rmd")
# always calves first and CC,CF,CW
a <- "economic_values_breeding_for_aCF"
a <- read.table(file = a, sep=";", header=TRUE)
a <- as.numeric(a)
a
```

## Computations without equations

### Number of traits $n$

```{r}
n <- as.numeric(nrow(phenotypic_var_cov))
```

### Variance Covariance Matrices $G$ (genetic) and $R_y$ (residual)

```{r}
G <- genetic_var_cov
male_R <- residual_var_cov %x% diag(male_offspring)
female_R <- residual_var_cov %x% diag(female_offspring)
```


### Relationship Matrix $A_y$ and Inverse $A_y^{-1}$

```{r RelationshipMatrix}
## male
# Compute the relationsship matrix dependent on the number of offspring of the selection candidate. The selection candidate is the first animal.
suppressPackageStartupMessages(library(pedigreemm))
mnumb <- male_offspring+1
male_A <- pedigree(sire = c(NA,rep(1,times = male_offspring)), dam =c(NA,rep(NA,times = male_offspring)), label = 1:mnumb)
# Compute inverse of relationsship matrix.
male_Ainv <- getAInv(male_A)
##  female
# Compute the relationsship matrix dependent on the number of offspring of the selection candidate. The selection candidate is the first animal.
suppressPackageStartupMessages(library(pedigreemm))
mnumb <- female_offspring+1
female_A <- pedigree(sire = c(NA,rep(1,times = female_offspring)), dam =c(NA,rep(NA,times = female_offspring)), label = 1:mnumb)
# Compute inverse of relationsship matrix.
female_Ainv <- getAInv(female_A)
```

### Design matrix $Z_y$

```{r DesignMatrix}
# male
male_Z<-cbind(matrix(0, nrow=male_offspring*n,ncol=n),diag(male_offspring*n))
dim(male_Z)
# female
female_Z<-cbind(matrix(0, nrow=female_offspring*n,ncol=n),diag(female_offspring*n))
dim(female_Z)
```


### Selection intensity $i_y$ and value of trunctation $x_y$

```{r}
# male
male_i <- dnorm(qnorm(1-male_proportionselected))/male_proportionselected
male_x <- qnorm(male_proportionselected, lower.tail = FALSE)
# female
female_i <- dnorm(qnorm(1-female_proportionselected))/female_proportionselected
female_x <- qnorm(female_proportionselected, lower.tail = FALSE)
```

## Computations with Equations

### Factor of variance reduction $k_y$

$$k_y=i_y(i_y-x_y)$$

```{r}
# male
male_k <- male_i*(male_i-male_x)
# female
female_k <- female_i*(female_i-female_x)
```


### Prediction error variance $PEV_y$

$$PEV_y=(Z_y^TR_y^{-1}Z_y+A_y^{-1} \otimes G^{-1})^{-1}[1:n,1:n]$$

```{r PEV}
# male
male_PEV <- solve(t(male_Z)%*%solve(male_R)%*%male_Z+male_Ainv%x%solve(G))[1:n,1:n]
# female
female_PEV <- solve(t(female_Z)%*%solve(female_R)%*%female_Z+female_Ainv%x%solve(G))[1:n,1:n]
```

### Covariance matrix between true and estimated breeding values $C_y$

$$C_y=G-PEV_y $$

```{r CovarianceMatrix}
# male
male_C <- G-male_PEV
# female
female_C <- G-female_PEV
```

### Asymptotic covariance matrix $C_y^*$ between true and estimated breeding values

$$
\begin{bmatrix}
C_1^* \\
C_2^*
\end{bmatrix}
=
\left( 
\begin{bmatrix}
1+1/2k_1  &  1/2k_2 \\
1/2k_1    &  1+1/2k_2
\end{bmatrix}^{-1}
\otimes I_n
\right)
\bullet
\begin{bmatrix}
C_1 \\
C_2
\end{bmatrix}
$$

```{r AsymptoticCovarianceMatrix}
Ca <- (solve(matrix(c(1+0.5*male_k, 0.5*female_k,0.5*male_k, 1+0.5*female_k),nrow = 2, ncol = 2, byrow=TRUE))%x%diag(n))%*%rbind(male_C,female_C)
# male
male_Ca <- Ca[1:n,]
# female
female_Ca <- Ca[(1+n):(2*n),]
```

### Asymptotic genetic variance/covariance matrix $G^*$

$$G^*=G-1/2{\sum_{y=1}^{2}(k_y(a^TC_y^*a)^{-1}C_y^*aa^TC_y^*)}$$

```{r AsymptoticGeneticMatrix}
Ga<-G-0.5*((solve(as.numeric(male_k*(t(a)%*%male_Ca%*%a)))*as.numeric(male_Ca%*%a%*%t(a)%*%male_Ca))+(solve(as.numeric(male_k*(t(a)%*%male_Ca%*%a)))*as.numeric(male_Ca%*%a%*%t(a)%*%male_Ca)))
```

### Accuracy of the estimated overall breeding value $r_y^*$

$$r_y^*=\sqrt{\frac {a^TC_y^*a}{a^TG^*a}}$$

```{r AccuracyOverall}
# male
male_ra <- sqrt(as.numeric((t(a)%*%male_Ca%*%a)/as.numeric(t(a)%*%Ga%*%a)))
# female
female_ra <- sqrt(as.numeric((t(a)%*%female_Ca%*%a)/as.numeric(t(a)%*%Ga%*%a)))
male_ra
female_ra
```

### Standard deviation of the estimated overall breeding value $\sigma^*$

$$\sigma^*=\sqrt{a^TG^*a}$$

```{r StandardDeviationOverall}
stdev_overall<-sqrt(as.numeric(t(a)%*%Ga%*%a))
stdev_overall
```

### Asymptotic genetic gain of the estimated overall breeding value

$$Q= \frac {\sum_{y=1}^{2} i_yr_y^*\sigma^*}{\sum_{y=1}^{2}L_y}$$

```{r GeneticGainOverall}
Qoverall <- (male_i*male_ra*stdev_overall+female_i*female_ra*stdev_overall)/(male_generationintervall+female_generationintervall)
Qoverall
```

### Asymptotic genetic gain of a trait (here carcass fat)

$$Q_m^*= \frac {\sum_{y=1}^{2} i_ya^T(C_y^*)_m \sqrt{a^TC_y^*a}}{\sum_{y=1}^{2}L_y}$$

```{r GeneticGainTrait}
Qtrait<- (male_i*as.numeric(t(a)%*%male_Ca[,"aCF"])*sqrt(as.numeric(t(a)%*%male_Ca%*%a))+female_i*as.numeric(t(a)%*%female_Ca[,"aCF"])*sqrt(as.numeric(t(a)%*%female_Ca%*%a)))/(male_generationintervall+female_generationintervall)
Qtrait
```





