---
title: "Response to selection"
author: "Silvan"
date: "20 8 2018"
output: html_document
bibliography: 
- /Users/silvan/Documents/EarlyMaturityBeef/References/library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The response to selection is dependent on the parameters:

1. Selection intensity (si)
2. Selection accuracy (sa)
3. Genetic standard deviation (gsd)
4. Generation intervall [y] (gi)
5. The sex of the candidate (m/f)

In this example I calculate the response to selection for the both sexes as shown on page 135 [@VonRohr1998]. The abbreviation "m or f" in front of the parameters will show if the parameter is from a male or female candidate.
The first R chunk will define the necessary paramters:

```{r}
msi <- 1.4
mgi <- 1.25
fsi <- 0.8
fgi <- 1.75



```


The second R chunk will calculate the asymptotic response to selection (R) per year for the total breeding value:

```{r}
x <- msi * msa * gsd + fsi * fsa * gsd
y <- mgi + fgi

R<- x/y
print(R)
```


# References

