---
title: "ResponseToSelection_CarcassTraits_Multivariate"
author: "Silvan"
date: "18 10 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
```

# Goal

To compute genetic gains of the traits carcass fatt, carcass conformation and carcass weight. Each trait for adults and calves. (6 traits in total).

# Plan

Firstly, to record and name all input parameters either as tables or as variables in separate files.
Secondly, show all necessary equations/descriptions from bottom to top.
Thirdly, create R chunks that read the input parameters and solve the equations.

# Material

* Residual, phenotypic and genetic variances and covariances of and between all traits.
* Breeding scenario (number of records of offspring/itself/half siblings/full siblings per selection candidate).
* Generation intervall and proportion selected of the population.
* Economic value for each trait.

# Implementation

First I import the input parameters using read.table

## Input parameters

#### Variances/Covariances

```{r VariancesCovariances}
# Set working directory
setwd("~/Documents/EarlyMaturityBeef/ResponseToSelection/rmd")
# define file name
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov
## phenotypic
phenotypic_var_cov <- "adults_calves_phenotypic_variances_covariances"
phenotypic_var_cov <- read.table(file = phenotypic_var_cov, sep=";", header=TRUE)
phenotypic_var_cov

```

#### 




