---
title: "Response to selection"
author: "Silvan"
date: "20 8 2018"
output:
  html_document: default
  pdf_document: default
bibliography: /Users/silvan/Documents/EarlyMaturityBeef/References/library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Introduction derived from [@Falconer1996]
The change produced by selection that chiefly interests us is the change of the population mean. Th is is the response to selection, which will be symbolized by R. 
It is the difference of mean phenotypic value between the offspring of the selcted parents and the whole of the parental generation before selection. 
The measure of the selection applied is the average superiority of the selected parents, which is called the selection differential, and will be symbolized by S.
If you can assume that there is no natural selection (fertility and viability not correlated with trait), you can say the ratio of response to selection differential is equal to the heritability [@Falconer1996].
$$R = h^2S$$
$$S = i\sigma_{P}$$
$$R = ih^2\sigma_{P}$$
$$h = \sigma_{A}/\sigma_{P}$$
$$R = ih\sigma_{A}$$


Assortative mating can be disregarded, because it has very little effect on the mid-parent regression. 
The chief use of this equation is for predicting the response to selection. The knowledge of heritability can be obtained from previous generations. The selection differential can not be known, but its expected value can be predicted.

In the following example you can see how the response to selection for abdominal bristle number in drosophila.

```{r}
x <- data.frame(c("Parents", "Offspring"), c(35.3, 37.9), c(40.6, "-"), c(5.3, "-"), c(2.8,"-"), c("-", 2.6))
colnames(x) <- c("Generation", "Mean of all measured", "Mean of those selected", "Selection differential", "Experienced response", "Observed response")
library(knitr)
```

```{r}
h2 <- 0.52
S <- 40.6 - 35.3
R <- h2 * S
oR <- 37.9 - 35.3
```

The heritability `r h2` of the bristle number was estimated in the previous generations. The selected parents had a mean superiority of `r S`. The predicted response is S * h2 = `r R`. The observed response was `r oR`.
However this result is only valid for this generation, because heritability is expected to change in each generation.

When a normal distribution of the values for a trait in a population can be assumed, which is usually the case you can derivate the intensity of selection of the proportion selected.

The goal is of course to increase the response to selection when we are breeding. 
Increasing intensity of selection seems at first sight to be a straightforward  way of improving the response.
However there are two factors that limit increasing intensity of selection:
1. The reproductive rate
2. Inbreeding



# Response to selection in index derived from [VonRohr1998]

The response to selection of the total breeding value $R^*$ is dependent on the parameters:

1. Intensity of selection $i$
2. Selection accuracy $r^*$
3. Genetic standard deviation $\sigma^*$
4. Generation intervall $L$[y] 

It has to be calculated separateley for each sex $y$ ($_1=male$, $_2=female$) and then summed up in the end. Selection accuracy and standard deviation are calculated with the total breeding value $^*$.
In this example I calculate the response to selection for the both sexes by the formula as shown on page 135 [@VonRohr1998]:

$$R^*= \frac {\sum_{y=1}^{2} i_yr_y^*\sigma^*}{\sum_{y=1}^{2}L_y}$$

The following table will define the given necessary parameters for two sexes $male=_1$ and $female=_2$: Selection intensity, generation intervall, number of evaluated full siblings (fs), number of evaluated half siblings (hs).

```{r, results='asis'}
tbl_given <- tibble::data_frame(male=c(.2, 1.4, 1.25, 4, 16), female=c(.5, 0.798, 1.75, 4, 8))
rownames(tbl_given) <- c("Proportion selected $P$ [%]", "Intensity of selection $i$ [units of standard deviations]", "Generation intervall $L$ [y]", "Number of full siblings", "Number of half siblings")
```

```{r}
i1 <- 1.4
i2 <- 0.8
p1 <- 0.2
p2 <- 0.8
L1 <- 1.25
L2 <- 1.75
mfs <- 4
mhs <- 16
ffs <- 4
fhs <- 8
n <- 8

```

The variables $r^*$ and $\sigma^*$  have to be calculated first with the variables deviation of the vector of the economical weights $a'$, the asymptotic covariance $C_y^*$ between true and estimated breeding values of the male or female candidates before the selection, the vector of the economical weights $a$ and the asymptotic genetic variance-covariance $G^*$:
$$r^*=\sqrt{\frac {a^TC_y^*a}{a^TG^*a}}$$

$$\sigma^*=\sqrt{a^TG^*a}$$

The vector of the economical weights $a$ is the change in revenue [Sfr.] per genetic standard deviation and $a^T$ is the transpose of $a$.

```{r}
a <- as.matrix(c(5.5, -7.56, 14.07, 8.32, 1.76, 0, -3.16,0))

```

However to solve these equations you need to first calculate the $C_y^*$ by the formula:

$$
\begin{bmatrix}
C_1^* \\
C_2^*
\end{bmatrix}
=
\left( 
\begin{bmatrix}
1+1/2k_1  &  1/2k_2 \\
1/2k_1    &  1+1/2k_2
\end{bmatrix}^{-1}
\otimes I_n
\right)
\begin{bmatrix}
C_1 \\
C_2
\end{bmatrix}
$$

In this equation you have the factors of variance reduction based on the selection of the male or female candidates $k_1$, $k_2$, the covariance matrices $C_1$, $C_2$ between true and estimated breeding values of the male or female candidates before the selection and the identity matrix $I_n$ of $n$ traits existing in the total breeding value.

You can derive $k_1$ and $k_2$ from the intensities of selection $i_1$, $i_2$ and from the value of trunctation $x_1$, $x_2$ for male and female candidates ,
$$k_y=i_y(i_y-x_y)$$
The intensities of selection are given $i_1$=`r i1`, $i_2$=`r i2` and can also be calculated by the proportion selected $p_1$, $p_2$. 
Given the proportion selected, we want to compute the selection intensity. For this we need some properties of the normal distribution.

The first quantity to compute are the quantiles ($x_y$) that belong to the proportions.
```{r, results='asis'}
tbl_prop_sel <- tibble::data_frame(male=.2, female=.5)
rownames(tbl_prop_sel) <- "proportion selected"
```


```{r}
(quant_male <- qnorm(tbl_prop_sel$male, lower.tail = FALSE))
(quant_female <- qnorm(tbl_prop_sel$female, lower.tail = FALSE))
(sel_quant <- qnorm(c(tbl_prop_sel$male, tbl_prop_sel$female), lower.tail = FALSE))

```
From the quantiles we can compute the ordinates ($z$)

```{r}
sel_ords <- dnorm(c(quant_male, quant_female))
```

Finally the selection intensity is computed as

$$i_y = z_y/p_y$$

```{r}
(sel_int <- sel_ords/tbl_prop_sel["proportion selected",])
```

Computing the values of the variance reductions ($k$)

```{r}
(sel_k <- sel_int * (sel_int - sel_quant))
mk<-sel_k[,"male"]
fk<-sel_k[,"female"]
```

The next variable we need to know is the identity matrix $I_n$. It is defined by the number of traits existing in the total breeding value $n$. In this example we have `r n` traits, which results in the following identity matrix:

```{r}
In<-diag(n)
```

The only variables not yet defined in the equation above are the covariance matrices $C_1$, $C_2$ ($C_y$) between true and estimated breeding values of the male or female candidates before the selection.

The true breeding value is the genetic merit of an individual which can be conceptually defined as twice the average deviation of its offspring from the population mean when mated randomly to an infinite population.

The estimated breeding value is only based on phenotypic values of itself or its relatives, but not on those of its progeny.

$C_y$ is defined by the prediction error variance ($PEV_y$) and the additive genetic variance-covariance matrix ($G$) multiplied by the relationship matrix $A_y$ the kronecker operator $\otimes$ before the selection.
$$C_y=A_y \otimes G-PEV_y$$
You can compute $PEV_y$ and $A_y \otimes G$ with the available data.
$A_y \otimes G$ owns as values the covariances between each trait and the relationship matrix.
The covariances of $G$ are dependent on the genetic standard deviation of each trait ($\sigma_g$), the genetic correlations between the traits ($r_{x,y}$) and the genetic variance of each trait ($\sigma_g^2$).

The variances of the traits are the diagonal values of the matrix $G$ for the covariance between the same trait is the variance of the trait:
$$Cov(x, x)=\sigma_x^2$$
The covariance between different traits is defined by the correlation between them and the variance of each trait:
$$Cov(x,y)=r_{x,y}\sigma_x\sigma_y$$
In the following table the necessary information to compute the covariances are listed: The diagonal values are the genetic standard deviations $\sigma_g$ and the the others the genetic correlations between the traits ($r_{x,y}$).
```{r}
tbl_cov <-data.frame(c(42.31, -0.15, -0.33, 0.11, -0.02, 0.15, 0.04, -2.4), 
                     c(-0.15, 0.09, -0.66, 0.16, -0.14, -0.04, -0.09, -0.06),
                     c(-0.33, -0.66, 1.78, -0.07, -0.09, -0.04, 0.08, 0.54), 
                     c(0.110, 0.16,  -0.07, 0.33, 0.36, 0.24, -0.08, -0.326), 
                     c(-0.020, -0.14, -0.09, 0.36, 0.09, 0.43, -0.7, -0.5), 
                     c(0.150, -0.04, -0.04, 0.24, 0.43, 0.02, -0.36, -0.008), 
                     c(0.040, -0.09, 0.08, -0.08, -0.7, -0.36, 1.58, -0.08), 
                     c(-2.40, -0.06, 0.54, -0.326, -0.5, -0.008, -0.08, 0.86))
colnames(tbl_cov) <- c("MTZ", "FV", "AwF", "ImF", "pH1", "pH30", "H30", "FEZ")
rownames(tbl_cov) <- c("MTZ", "FV", "AwF", "ImF", "pH1", "pH30", "H30", "FEZ")
```

I can transform the data frame into a matrix.
```{r, results='asis'}
matrix_cov <- as.matrix(tbl_cov)
```

The problem is now that the diagonal elements should be squared and the correlation should be multiplied with the variances of the involved traits respecteveley.
This can be done by matrix scalar multiplication.
We build a diagonal matrix with the standard deviations as diagonal elements $D$ and a matrix with all the correlation but with 1,1,1,... as diagonal elements $E$.

First $D$:
```{r}
matD <- diag(diag(matrix_cov), nrow = 8, ncol = 8)
```

Then $E$:
```{r}
matE <- matrix_cov
diag(matE) <- 1
```

Then we get the required matrix $G$ by the following equation:
$$G=DED$$
It works:

```{r}
42.31*-0.15*0.09
G <-matD %*% matE %*% matD
dim(G)
```
Now we have $G$, it describes how the variances of different traits in the index are related to each other.

The next variable we need is $A_y$ and $PEV_y$ which depends on $A_y$ aswell.
I can compute $PEV_y$ with the formula derived from [@Phocas1996].
$$
PEV_y
=
\left( 
\begin{matrix}
X^T_yR^{-1}_yX_y  &  X_y^TR^{-1}_yZ_y \\
Z^T_yR^{-1}_yX_y   &  Z_y^TR^{-1}_yZ_y+A_y^{-1} \otimes G^{-1}
\end{matrix}
\right)^{-1}
$$

For this formula I need the relationship matrix $A_y$, but also the genetic and phenotypic variances $\sigma_g$ and $\sigma_p$ and $G$.
I will not need any other data.

$Z$ is a design matrix that connects the records of observations (does not include the breeding candidate and its parents) with the breeding values (includes the candidate and its parents).

$X$ is a design vector of the values 1,1,1, as long as there are animals involved. 
It could connect the observations to fixed factors, but we do not have any fixed factors.

$R^{-1}_y$ is the inverse diagonal matrix of the values of variance of the environment/residuals for the traits and the recorded animals. 
The diagonal values of $R^{-1}_y$ are consisting of the repetition of residual variances of each trait. 
The number of repetitions of here `r n` values is dependent on the number of records.

The environmental/residual variance $\sigma_e$ is the difference between $\sigma_g$ and $\sigma_p$ for each trait.
$$\sigma_e=\sigma_p-\sigma_g$$
For we need to compute $\sigma_e$ for each trait, it will be a vector of `r n` values.
$\sigma_g$ is available and $\sigma_p$ is possible to compute from the heritability $h^2$ and $\sigma_g$ for each trait:
$$\sigma_p=\sigma_g^2/h^2$$
$h^2$ for all traits is available.
According to the model, the environomental or residual variances exist only for those animals that have a record.
The candidate and the parents do not have a record.
Therefore the candidate and the parents should not own an element in the matrix, but all other animals that have a record own an element of each trait. 

This leads to a diagonal matrix $R_1$ with a `r n*(mfs+mhs)` x `r n*(mfs+mhs)` dimension for a male candidate.

```{r}
h2 <- c(0.32,0.469,0.6,0.51,0.29,0.16,0.22,0.42)
sigg<- diag(matrix_cov)
sigp<-sigg/h2
sige<-sigp-sigg
mR <- matrix(0,nrow=(mfs+mhs)*n,ncol=(mfs+mhs)*n)
diag(mR)=rep(as.vector(sige),each=mfs+mhs)
mRinv <- solve(mR)
dim(mRinv)
```
Now I have $R^{-1}_1$.

Here I have to compute $R^{-1}_2$ aswell, which is
```{r}
fR <- matrix(0,nrow=(ffs+fhs)*n,ncol=(ffs+fhs)*n)
diag(fR)=rep(as.vector(sige),each=ffs+fhs)
fRinv <- solve(fR)
dim(fRinv)
```

The next variable I need is the inverse of the relationship matrix $A_y$ for each sex.

I know that the male candidate has `r mfs` full siblings, `r mhs` half siblings and a female has `r ffs` full siblings and `r fhs` half siblings.
Based on the number of siblings I can create a relationship matrix.
I can compute the genetic additive relationship matrix $A$ for a given pedigree using the `pedigreemm` package.
I need to identify the parents of each animal, not known parents I name NA.

First I compute the pedigree of a male candidate. 
There are 2 parents, 20 siblings and the candidate wich in total are 23 animals. 
I do not know the parents of the parents.
Number 1 and 2 are the parents and number 3 is the selection candidate.

```{r}
suppressPackageStartupMessages( library(pedigreemm))
mnumb <- mfs+mhs+3
mped <- pedigree(sire = c(NA,NA,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1), dam = c(NA,NA,2,2,2,2,2,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA), label = 1:mnumb)
```

Then I create a matrix out of the pedigree:
The function `getA` computes the additive relationship matrix $A_1$.
```{r}
mA<-getA(mped)
```

Then I compute the inverse of $A_1$.
```{r}
mAinv <- getAInv(mped)
```

I need to do the same for a female candidate.
A female candidate has `r ffs` full siblings and `r fhs` half siblings and 2 parents. Including the candidate this is a total of `r ffs+fhs+3` animals.
Number 1 and 2 are the parents and number 3 is the selection candidate.
```{r}
suppressPackageStartupMessages( library(pedigreemm))
fnumb <- ffs+fhs+3
fped <- pedigree(sire = c(NA,NA,1,1,1,1,1,1,1,1,1,1,1,1,1), dam = c(NA,NA,2,2,2,2,2,NA,NA,NA,NA,NA,NA,NA,NA), label = 1:fnumb)
```

Then I create a matrix out of the pedigree.
The function `getA` computes the additive relationship matrix $A_2$.
```{r}
fA<-getA(fped)
```

Then I compute the inverse $A^{-1}_2$.
```{r}
fAinv<-getAInv(fped)
```

Then I compute $X_y$.
$X_y$ is a matrix that connects the records with the levels of fixed effects.
I do not have any fixed effects.
Therefore I can assume that $X_y$ is just a vector with the number of values that correspond to the number of records.

First I compute $X_1$
The number of records for a male candidate is here `r (mfs+mhs)*n`.
```{r}
mX <- rep.int(1, times=(mfs+mhs)*n)
```

Then I compute $X_2$.
$X_2$ is `r ffs+fhs+3` times 1 level of fixed effects.
```{r}
fX <- rep.int(1, times=(ffs+fhs)*n)
```

Then I compute $Z_y$.
$Z_y$ should exclude the animals without records.
For both sexes there are 3 animals that do not have records.

First I compute $Z_1$.
I can exclude the 3 animals attaching a zero matrix of the dimensions `(mfs+mhs)*n` x `3*n` on the left side to the columns of the identity matrix with dimensions  `(mfs+mhs)*n` x `(mfs+mhs)*n`.
```{r}
mZ<-cbind(matrix(0, nrow=(mhs+mfs)*n,ncol=3*n),diag((mhs+mfs)*n))
dim(mZ)
```

Then I compute $Z_2$.
```{r}
fZ<-cbind(matrix(0, nrow=(fhs+ffs)*n,ncol=3*n),diag((fhs+ffs)*n))
dim(fZ)
```

Then I compute the inverse of $G$.
```{r}
Ginv<-solve(G)
```

Now I can compute the matrix $PEV_1$.
To compute it I have to compute all four parts of the whole matrix. 
Then I will bind the part together in the right order.
How ever you can skip to the right bottom part right now.
It is sufficient for the moment.

First I will compute the left top part of the matrix.
$$X_y^TR^{-1}_yX_y$$
which is
```{r}

mXX<-t(mX)%*%mRinv%*%mX
dim(mXX)
```

Then I compute the right top part
$$X_y^TR^{-1}_yZ_y$$
which is
```{r}
mXZ <- t(mX)%*%mRinv%*%mZ
dim(mXZ)
```

Then I compute the left bottom part
$$Z^T_yR^{-1}_yX_y$$
which is
```{r}
mZX <- t(mZ)%*%mRinv%*%mX
dim(mZX)
```

Then I compute the right bottom part
$$Z_y^TR^{-1}Z_y+A_y^{-1} \otimes G^{-1}$$
which is
```{r}
dim(mRinv)
dim(mZ)
dim(t(mZ))
dim(mAinv)
dim(Ginv)
mZZ <- t(mZ)%*%mRinv%*%mZ+mAinv%x%Ginv
```

Actually I can at this moment say that $PEV_1$ is the right bottom part of the matrix $PEV_1$ and for $PEV_2$ the same.

Therefore I only compute the right bottom part of $PEV_2$ at the moment.
$$Z_y^TR^{-1}Z_y+A_y^{-1} \otimes G^{-1}$$
which is
```{r}
fZZ <- t(fZ)%*%fRinv%*%fZ+fAinv%x%Ginv
dim(fZZ)
```

```{r}
mPEV<-mZZ
fPEV<-fZZ
```

Now I should be able to compute $C_y$ out of $PEV_y$ and $A_y \otimes G$.
First I compute $C_1$
```{r}
dim(mA%x%G)
dim(mPEV)
mC<-mA%x%G-mPEV
```

Then $C_1$
```{r}
dim(fA%x%G)
dim(fPEV)
fC<-fA%x%G-fPEV
```

$C_1$ and $C_2$ been the last variable not yet defined in the following formula.
In this formula I only use the values of the selection candite as $C_1$ and $C_2$.
First select for $C_1$
```{r}
dim(fC)
fC<-fC[17:24,17:24]
dim(fC)
```

Then for $C_2$
```{r}
dim(mC)
mC<-mC[17:24,17:24]
dim(mC)
```

$$
\begin{bmatrix}
C_1^* \\
C_2^*
\end{bmatrix}
=
\left( 
\begin{bmatrix}
1+1/2k_1  &  1/2k_2 \\
1/2k_1    &  1+1/2k_2
\end{bmatrix}^{-1}
\otimes I_n
\right)
\bullet
\begin{bmatrix}
C_1 \\
C_2
\end{bmatrix}
$$

First I compute the inner matrix
```{r}
Sinv<-solve(matrix(c(1+0.5*mk, 0.5*fk,0.5*mk, 1+0.5*fk),nrow = 2, ncol = 2))
dim(Sinv)
```
Then the whole matrix
```{r}
dim(mC)
dim(fC)
dim(Sinv)
dim(In)
dim(Sinv%x%In)
Ca <- (Sinv%x%In)%*%rbind(mC,fC) 
```
Now I have $C_y^*$.

With the following formula I can compute $G^*$:
$$G^*=G-1/2{\sum_{y=1}^{2}(k_y(a^TC_y^*a)^{-1}C_y^*aa^TC_y^*)}$$

First I compute the part of the sum including $C_1^*$. 
I call it $S1$.
```{r}
mCa<-Ca[1:8,]
dim(mCa)
dim(a)
dim(t(a)%*%mCa%*%a)
S1<-mk*(solve(t(a)%*%mCa%*%a)%*%mCa%*%a%*%t(a)%*%mCa)
dim(S1)
```







# Annex



I can compute the required matrix by a kronecker product.
I have a matrix that tells us what $Z_1$ would be for only one trait and I have a unit matrix that has the size of the number of traits.
Together as kronecker product they form the required matrix $Z_1$ for all traits.

```{r}
mZ<-diag(n)%x%cbind(matrix(0, nrow=mhs+mfs,ncol=3),diag(mhs+mfs))
dim(mZ)
```




The following formula is not important yet.
```{r, eval=FALSE}
mPEV <- rbind(cbind(mXX, mXZ), cbind(t(mXZ), mZZ))
dim(mPEV)
```

The vector of the economical weights $a$ is the change in revenue [Sfr.] per genetic standard deviation.

```{r}
a <- c(5.5, -7.56, 14.07, 8.32, 1.76, 0, -3.16,0)
```

# References

