---
title: "Early Maturity in Swiss Beef Cattle"
author: "Silvan Wyss, Sophie Kunz and Peter von Rohr"
date: "7/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome
This website is a repository for material related to the master thesis project on "Early Maturity in Swiss Beef Cattle". The reason for having this repository is that it allows for great flexibility in how and from where the material stored here can be accessed. 


## What Is Where?
During the whole project, documentation, literature articles, software programs and other types of data will be generated. This material is going to be stored in different places. The following list is a rough plan on what should going to be stored where.

* Documents and software source code can be put under this repository which is located on [github](https://github.com/charlotte-ngs/EarlyMaturityBeef)
* Literature articles should be added to our Mendely group account
* Large data sets will be stored on our cloud server (1-htz) at Hetzner. On this server all data analyses will be run.


## Project Material
* [How to contribute to this repository](how_to_contribute/how_to_contribute.html)
* [Project Plan](project_plan/project_plan.html)




```{r, results='asis'}
cat(rmddochelper::get_latest_change(), "\n")
```
