---
title: "Function_GeneticGain"
author: "Silvan"
date: "30 11 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
```

# Functions
## Function for covariance matrix between true and estimated breeding values

```{r FunCovarianceMatrix}
#' @title
#' Asymptotic covariance matrices between true and estimated breeding values.
#' @description
#' This function creates two covariance matrices between true and estimated breeding values of a male and a female selection candidate. These matrices are used to compute the genetic gain of an aggregate genotype when selection is based on multiple breeding values. The computation of the matrix is based on a possible scenario with known numbers of related animals, known genetic and residual variances and covariances. Here it is assumed, that there exist 6 breeding values which are present in the covariance matrix. This should result in two 6 x 6 matrices. Special is that it is also assumed, that the selection candidate has no records itself and that its relatives can have maximally have records of three of the six traits. This because they can not have both a record as calf and as adult. The variance-covariance matrices need the order calf, adult, calf, adult, calf, adult. In the result the matrices are bond together to one matrix, where the male covariance matrix is the matrix from row 1 to 6 and the female matrix is the matrix from row 7 to 12.
#' @param genetic_var_cov   The genetic variance-covariance matrix between the involved traits in the aggregate genotype.
#' @param residual_var_cov  The genetic variance-covariance matrix between the involved traits in the aggregate genotype.
#' @param male_offspring    Number of the assumed offspring of the male selection candidate when selection occurs.
#' @param female_offspring    Number of the assumed offspring of the female selection candidate when selection occurs.
#' @param proportion_calves Proportion of calves in the offspring.
#' @param proportion_adults Proportion of adults in the offspring.
#' @param male_proportionselected Proportion selected of the offspring of a male selection candidate
#' @param female_proportionselected Proportion selected of the offspring of a female selection candidate
#' @return                 Asymptotic Covariance Matrices between true and estimated breeding values
compute_asymptotic_covariance_matrices <- function(genetic_var_cov,
                                            residual_var_cov,
                                            offspring,
                                            proportion_calves,
                                            proportion_adults,
                                            male_proportionselected,
                                            female_proportionselected){
        # define number of traits
        n <- as.numeric(nrow(genetic_var_cov))
        
        # Compute the relationsship matrix dependent on the number of offspring of the selection candidate. The selection candidate is the first animal. Male
        suppressPackageStartupMessages(library(pedigreemm))
        mnumb <- male_offspring+1
        male_A <- pedigree(sire = c(NA,rep(1,times = male_offspring)), dam =c(NA,rep(NA,times = male_offspring)), label = 1:mnumb)
        # Compute inverse of relationsship matrix.
        male_Ainv <- getAInv(male_A)
        
        # Compute the relationsship matrix dependent on the number of offspring of the selection candidate. The selection candidate is the first animal. Female
        suppressPackageStartupMessages(library(pedigreemm))
        mnumb <- female_offspring+1
        female_A <- pedigree(sire = c(NA,rep(NA,times = female_offspring)), dam =c(NA,rep(1,times = female_offspring)), label = 1:mnumb)
        # Compute inverse of relationsship matrix.
        female_Ainv <- getAInv(female_A)
        
        # Compute Relationship Matrix Z
        # numbers of adults and calves in scenario
        male_number_adults <- floor(proportion_adults*male_offspring)[[1]]
        male_number_calves <- male_offspring-male_number_adults
        female_number_adults <- floor(proportion_adults*female_offspring)[[1]]
        female_number_calves <- female_offspring-female_number_adults
        # Kronecker
        kronecker_calves <- cbind(c(1,0,0),c(0,0,0),c(0,1,0),c(0,0,0),c(0,0,1),c(0,0,0))
        kronecker_adults <- cbind(c(0,0,0),c(1,0,0),c(0,0,0),c(0,1,0),c(0,0,0),c(0,0,1))
        # male Z
        male_calves <- diag(1,male_number_calves)%x%kronecker_calves
        male_calves <- cbind(male_calves,matrix(0, nrow=nrow(male_calves),ncol=male_number_adults*n))
        male_adults <- diag(male_number_adults)%x%kronecker_adults
        male_adults <- cbind(matrix(0, nrow=nrow(male_adults),ncol=male_number_calves*n),male_adults)
        male_Z <- rbind(male_calves, male_adults)
        male_Z<-cbind(matrix(0, nrow=male_offspring*(n/2),ncol=n),male_Z)
        # female Z
        female_calves <- diag(1,female_number_calves)%x%kronecker_calves
        female_calves <- cbind(female_calves,matrix(0, nrow=nrow(female_calves),ncol=female_number_adults*n))
        female_adults <- diag(female_number_adults)%x%kronecker_adults
        female_adults <- cbind(matrix(0, nrow=nrow(female_adults),ncol=female_number_calves*n),female_adults)
        female_Z <- rbind(female_calves, female_adults)
        female_Z<-cbind(matrix(0, nrow=female_offspring*(n/2),ncol=n),female_Z)
        
        # Genetic Variance Covariance Matrix G
        G <- genetic_var_cov
        
        # Residual Variance Covariance Matrix R
        residual_var_cov_calves <- residual_var_cov[c(1,3,5),c(1,3,5)]
        residual_var_cov_adults <- residual_var_cov[c(2,4,6),c(2,4,6)]
        # male 
        male_calves_kronecker_residual <- diag(male_number_calves) %x% residual_var_cov_calves 
        male_adults_kronecker_residual <- diag(male_number_adults) %x% residual_var_cov_adults
        male_calves_kronecker_residual_extended <- cbind(male_calves_kronecker_residual, matrix(0,nrow=nrow(male_calves_kronecker_residual),ncol=ncol(male_adults_kronecker_residual)))
        male_adults_kronecker_residual_extended <- cbind( matrix(0,nrow=nrow(male_adults_kronecker_residual),ncol=ncol(male_calves_kronecker_residual)), male_adults_kronecker_residual)
        male_R <- rbind(male_calves_kronecker_residual_extended,male_adults_kronecker_residual_extended)
        # female 
        female_calves_kronecker_residual <- diag(female_number_calves) %x% residual_var_cov_calves 
        female_adults_kronecker_residual <- diag(female_number_adults) %x% residual_var_cov_adults
        female_calves_kronecker_residual_extended <- cbind(female_calves_kronecker_residual, matrix(0,nrow=nrow(female_calves_kronecker_residual),ncol=ncol(female_adults_kronecker_residual)))
        female_adults_kronecker_residual_extended <- cbind( matrix(0,nrow=nrow(female_adults_kronecker_residual),ncol=ncol(female_calves_kronecker_residual)), female_adults_kronecker_residual)
        female_R <- rbind(female_calves_kronecker_residual_extended,female_adults_kronecker_residual_extended)
       
        # Selection intensity i and value of truncation x
        # male
        male_i <- dnorm(qnorm(1-male_proportionselected))/male_proportionselected
        male_x <- qnorm(male_proportionselected, lower.tail = FALSE)
        # female
        female_i <- dnorm(qnorm(1-female_proportionselected))/female_proportionselected
        female_x <- qnorm(female_proportionselected, lower.tail = FALSE)
       
        # Factor of variance reduction k
        # male
        male_k <- male_i*(male_i-male_x)
        # female
        female_k <- female_i*(female_i-female_x)
        
        # Prediction error variance matrix
        # male
        male_PEV <- solve(t(male_Z)%*%solve(male_R)%*%male_Z+male_Ainv%x%solve(G))[1:n,1:n]
        # female
        female_PEV <- solve(t(female_Z)%*%solve(female_R)%*%female_Z+female_Ainv%x%solve(G))[1:n,1:n]
        
        # Covariance Matrix 
        # male
        male_C <- G-male_PEV
        # female
        female_C <- G-female_PEV
        
        # Asymptotic Covariance Matrix
        Ca <- (solve(matrix(c(1+0.5*male_k, 0.5*female_k,0.5*male_k, 1+0.5*female_k),nrow = 2, ncol = 2, byrow=TRUE))%x%diag(n))%*%rbind(male_C,female_C)
        
        # Return
        return(Ca)
      }
```

## Function for genetic gain for index in Sfr./year

```{r FunGenGainIndexSfr}
#' @title
#' Genetic Gain in Sfr. / year for index.
#' @description
#' This function computes the genetic gain in Sfr. / year of the selection on the index. In this index all traits are represented in the aggregate genotype.
#' @param genetic_var_cov   The genetic variance-covariance matrix between the involved traits in the aggregate genotype.
#' @param residual_var_cov  The genetic variance-covariance matrix between the involved traits in the aggregate genotype.
#' @param male_offspring    Number of the assumed offspring of the male selection candidate when selection occurs.
#' @param female_offspring    Number of the assumed offspring of the female selection candidate when selection occurs.
#' @param proportion_calves Proportion of calves in the offspring.
#' @param proportion_adults Proportion of adults in the offspring.
#' @param male_proportionselected Proportion selected of the offspring of a male selection candidate
#' @param female_proportionselected Proportion selected of the offspring of a female selection candidate
#' @param male_generationintervall Generation intervall of the male selection path.
#' @param female_generationintervall Generation intervall of the female selection path.
#' @param economic_weights A vector of economic weights with lenght of number of traits.
#' @return                 Genetic Gain in Sfr. per year
compute_genetic_gain_overall_index <- function(genetic_var_cov,
                                            residual_var_cov,
                                            offspring,
                                            proportion_calves,
                                            proportion_adults,
                                            male_proportionselected,
                                            female_proportionselected,
                                            male_generationintervall,
                                            female_generationintervall,
                                            economic_weights){
        # define vector of economic weights
        a <- economic_weights
        
        # Intesity of selection
        male_i <- dnorm(qnorm(1-male_proportionselected))/male_proportionselected
        female_i <- dnorm(qnorm(1-female_proportionselected))/female_proportionselected
        
        # Asymptotic covariance matrices
        
        Ca <- compute_asymptotic_covariance_matrices(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected) 
        
        # Number of traits
        n <- as.numeric(ncol(Ca))
        
        # male
        male_Ca <- Ca[1:n,]
        # female
        female_Ca <- Ca[(1+n):(2*n),]
        
        # Genetic Gain
        Qoverall_index <- (male_i*sqrt(as.numeric(t(a)%*%male_Ca%*%a))+female_i*sqrt(as.numeric(t(a)%*%female_Ca%*%a)))/(male_generationintervall+female_generationintervall)
        
        return(Qoverall_index)
      }
```

## Function for correlated genetic gain for index in trait unit / year

```{r FunGenGainIndexTrait}
#' @title
#' Correlated genetic gain in trait unit / year for index.
#' @description
#' This function computes the correlated genetic gain in trait unit / year of the selection on the index. In this index all traits are represented in the aggregate genotype.
#' @param genetic_var_cov   The genetic variance-covariance matrix between the involved traits in the aggregate genotype.
#' @param residual_var_cov  The genetic variance-covariance matrix between the involved traits in the aggregate genotype.
#' @param male_offspring    Number of the assumed offspring of the male selection candidate when selection occurs.
#' @param female_offspring    Number of the assumed offspring of the female selection candidate when selection occurs.
#' @param proportion_calves Proportion of calves in the offspring.
#' @param proportion_adults Proportion of adults in the offspring.
#' @param male_proportionselected Proportion selected of the offspring of a male selection candidate
#' @param female_proportionselected Proportion selected of the offspring of a female selection candidate
#' @param male_generationintervall Generation intervall of the male selection path.
#' @param female_generationintervall Generation intervall of the female selection path.
#' @param economic_weights A vector of economic weights with lenght of number of traits.
#' @param trait The name of the trait, of which the genetic gain should be.
#' @return                 Correlated genetic gain in trait unit per year
compute_genetic_gain_trait <- function(genetic_var_cov,
                                            residual_var_cov,
                                            offspring,
                                            proportion_calves,
                                            proportion_adults,
                                            male_proportionselected,
                                            female_proportionselected,
                                            male_generationintervall,
                                            female_generationintervall,
                                            economic_weights,trait){
        # define vector of economic weights
        a <- economic_weights
        
        # Intesity of selection
        male_i <- dnorm(qnorm(1-male_proportionselected))/male_proportionselected
        female_i <- dnorm(qnorm(1-female_proportionselected))/female_proportionselected
        
        # Asymptotic covariance matrices
        
        Ca <- compute_asymptotic_covariance_matrices(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected) 
        
        # Number of traits
        n <- as.numeric(ncol(Ca))
        
        # male
        male_Ca <- Ca[1:n,]
        # female
        female_Ca <- Ca[(1+n):(2*n),]
        
        # Correlated genetic gain
        Qtrait <- (male_i*as.numeric(t(a)%*%male_Ca[,trait])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
                     female_i*as.numeric(t(a)%*%female_Ca[,trait]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)

        return(Qtrait)
      }
```


# Covariance Matrix
## Produce result of function for covariance matrix

```{r CovarianceMatrix}
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

Ca <- compute_asymptotic_covariance_matrices(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected) 
```


# Results without Herd x year interactions
## Produce result of function for genetic gain for index Limousin

```{r GenGainIndexSfrLM}
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "LM_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "LM_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "LM_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

Sfr_LM <- compute_genetic_gain_overall_index(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)
Sfr_LM

```

## Produce results of function for correlated genetic gains for index Limousin

```{r GenGainIndexTraitLM}
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
list_of_traits <- colnames(genetic_var_cov)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "LM_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "LM_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "LM_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

# Loop that produces a matrix with all correlated genetic gains
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_LM <- mat_correlated_gen_gain


```

## Produce result of function for genetic gain for index Angus

```{r GenGainIndexSfrAN}
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "AN_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "AN_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "AN_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

Sfr_AN <- compute_genetic_gain_overall_index(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)


```

## Produce results of function for correlated genetic gains for index Angus

```{r GenGainIndexTraitAN}
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
list_of_traits <- colnames(genetic_var_cov)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "AN_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "AN_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "AN_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

# Loop that produces a matrix with all correlated genetic gains
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_AN <- mat_correlated_gen_gain


```

## Produce barplot genetic gain Sfr.

```{r BarplotSfr}
library(ggplot2)
x <-data.frame(Gain=c(Sfr_AN,Sfr_LM),Breed=c("Angus", "Limousin"))
# Plot
g <- ggplot(x,aes(Breed,Gain))
g + geom_bar(stat="identity", width=0.5)+
  theme_classic()+theme(text = element_text(size = 30))+
  ylab("Genetic gain in Sfr./y")
```

## Produce barplot correlated genetic gains trait units.

```{r}
library(ggplot2)
library(varhandle)
x <- rbind(Trait_AN,Trait_LM)
x <- as.data.frame(x)
x$Breed <- rep(c("Angus", "Limousin"),each=6)
colnames(x)[2] <- "Gain"
x$Gain <- unfactor(x$Gain)
# Plot
g <- ggplot(x,aes(trait,Gain))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in trait unit/y")


# Per genetic standard deviation

SD  <- "adults_calves_genetic_variances_covariances"
SD  <- read.table(file = SD, sep=";", header=TRUE)
SD <- as.matrix(SD)
SD <- diag(SD)
SD <- sqrt(SD)
x$SD <- c(SD,SD)
x$GainSD <- x$Gain/x$SD

g <- ggplot(x,aes(trait,GainSD))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in sd/y")
```







# Results with Herd x year interactions
## Produce result of function for genetic gain for index Limousin

```{r }
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)
# herd x year
herdyear_var_cov <- "adults_calves_herdyear_variances_covariances"
herdyear_var_cov <- read.table(file = herdyear_var_cov, sep=";", header=TRUE)
herdyear_var_cov <- as.matrix(herdyear_var_cov)
#residual_var_cov <- residual_var_cov+herdyear_var_cov

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "LM_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "LM_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "LM_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

Sfr_LM <- compute_genetic_gain_overall_index(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)

Sfr_LM

```

## Produce results of function for correlated genetic gains for index Limousin

```{r }
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
list_of_traits <- colnames(genetic_var_cov)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)
# herd x year
herdyear_var_cov <- "adults_calves_herdyear_variances_covariances"
herdyear_var_cov <- read.table(file = herdyear_var_cov, sep=";", header=TRUE)
herdyear_var_cov <- as.matrix(herdyear_var_cov)

#residual_var_cov <- residual_var_cov+herdyear_var_cov
#residual_var_cov

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "LM_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "LM_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "LM_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

# Loop that produces a matrix with all correlated genetic gains
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_LM <- mat_correlated_gen_gain
Trait_LM

```

## Produce result of function for genetic gain for index Angus

```{r }
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)
# herd x year
herdyear_var_cov <- "adults_calves_herdyear_variances_covariances"
herdyear_var_cov <- read.table(file = herdyear_var_cov, sep=";", header=TRUE)
herdyear_var_cov <- as.matrix(herdyear_var_cov)
#residual_var_cov <- residual_var_cov+herdyear_var_cov

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "AN_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "AN_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "AN_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

Sfr_AN <- compute_genetic_gain_overall_index(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights)


```

## Produce results of function for correlated genetic gains for index Angus

```{r }
library(dplyr)
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
list_of_traits <- colnames(genetic_var_cov)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)
# herd x year
herdyear_var_cov <- "adults_calves_herdyear_variances_covariances"
herdyear_var_cov <- read.table(file = herdyear_var_cov, sep=";", header=TRUE)
herdyear_var_cov <- as.matrix(herdyear_var_cov)
#residual_var_cov <- residual_var_cov+herdyear_var_cov

# input offspring
male_offspring <- 20
female_offspring <- 5
proportion_adults <- 0.5
proportion_calves <- 0.5

# proportion selected
male_proportionselected <- 0.1
female_proportionselected <- 0.5

# economic weight
economic_weights <- "AN_economic_values"
economic_weights <- read.table(file = economic_weights, sep=";", header=TRUE)
economic_weights <- as.matrix(economic_weights)
economic_weights <- as.vector(economic_weights)

# Generation Intervall
male_generationintervall <- "AN_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
female_generationintervall <- "AN_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)

# Loop that produces a matrix with all correlated genetic gains
mat_correlated_gen_gain <- NULL

for(trait in list_of_traits){
  if (is.null(mat_correlated_gen_gain)){
  mat_correlated_gen_gain <- cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait))
} else {
  mat_correlated_gen_gain <- rbind(mat_correlated_gen_gain,cbind(trait,compute_genetic_gain_trait(genetic_var_cov = genetic_var_cov, residual_var_cov = residual_var_cov, offspring = offspring, proportion_calves = proportion_calves, proportion_adults = proportion_adults,male_proportionselected = male_proportionselected,female_proportionselected = female_proportionselected, male_generationintervall=male_generationintervall,female_generationintervall = female_generationintervall,economic_weights = economic_weights, trait=trait)))
}
}
Trait_AN <- mat_correlated_gen_gain


```

## Produce barplot genetic gain Sfr.

```{r }
library(ggplot2)
x <-data.frame(Gain=c(Sfr_AN,Sfr_LM),Breed=c("Angus", "Limousin"))
# Plot
g <- ggplot(x,aes(Breed,Gain))
g + geom_bar(stat="identity", width=0.5)+
  theme_classic()+theme(text = element_text(size = 30))+
  ylab("Genetic gain in Sfr./y")
```

## Produce barplot correlated genetic gains trait units.

```{r}
library(ggplot2)
library(varhandle)
x <- rbind(Trait_AN,Trait_LM)
x <- as.data.frame(x)
x$Breed <- rep(c("Angus", "Limousin"),each=6)
colnames(x)[2] <- "Gain"
x$Gain <- unfactor(x$Gain)
# Plot
g <- ggplot(x,aes(trait,Gain))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in trait unit/y")


# Per genetic standard deviation

SD  <- "adults_calves_genetic_variances_covariances"
SD  <- read.table(file = SD, sep=";", header=TRUE)
SD <- as.matrix(SD)
SD <- diag(SD)
SD <- sqrt(SD)
x$SD <- c(SD,SD)
x$GainSD <- x$Gain/x$SD

g <- ggplot(x,aes(trait,GainSD))
g + geom_bar(stat="identity", width=0.5,aes(fill=Breed),position="dodge")+
  theme_classic()+theme(text = element_text(size = 20))+
  ylab("Genetic gain in sd/y")
```





