---
title: "ResponseToSelection_CarcassTraits_Multivariate"
author: "Silvan"
date: "18 10 2018"
output: pdf_document
---

# Goal

To compute genetic gains of the traits carcass fat, carcass conformation and carcass weight. Each trait for adults and calves. (6 traits in total).

# Plan

* Firstly, to record and name all input parameters either as tables or as variables in separate files.

* Secondly, show all necessary equations/descriptions from bottom to top.

* Thirdly, create R chunks that read the input parameters and solve the equations.

# Material

* Residual, phenotypic and genetic variances and covariances of and between all traits.

* Breeding scenario (number of records of offspring per selection candidate). The scenario will result in a relationsship matrix. For male and female selection paths each a separate relationsship matrix.

* Generation intervall and proportion selected of the population for male and female selection paths.

* Economic value for each trait.

# Implementation

First I import the input parameters using read.table(). 
Then I compute paramteres that do not require equations.
Then I compute all necessary steps using equations (derived from @Phocas1998).

## Input parameters

### Genetic, Residual and Phenotypic Variances/Covariances

With CC,CF,CW.
```{r VariancesCovariances}
# import variance covariance dataframes and compute matrix
## genetic
genetic_var_cov <- "adults_calves_genetic_variances_covariances"
genetic_var_cov <- read.table(file = genetic_var_cov, sep=";", header=TRUE)
genetic_var_cov <- as.matrix(genetic_var_cov)
## residual
residual_var_cov <- "adults_calves_residual_variances_covariances"
residual_var_cov <- read.table(file = residual_var_cov, sep=";", header=TRUE)
residual_var_cov <- as.matrix(residual_var_cov)
residual_var_cov_calves <- residual_var_cov[c(1,3,5),c(1,3,5)]
residual_var_cov_calves
residual_var_cov_adults <- residual_var_cov[c(2,4,6),c(2,4,6)]
residual_var_cov_adults
## phenotypic
phenotypic_var_cov <- "adults_calves_phenotypic_variances_covariances"
phenotypic_var_cov <- read.table(file = phenotypic_var_cov, sep=";", header=TRUE)
phenotypic_var_cov <- as.matrix(phenotypic_var_cov)
```

### Number of Offspring

First the number of relatives is imported.
```{r NumberofRelatives}
library(dplyr)
## male
male_offspring <- "LM_number_of_offspring"
male_offspring <- read.table(file = male_offspring, sep=";", header=TRUE) %>%
  select(male)
male_offspring <- as.numeric(male_offspring)
male_offspring <- 20
## female
female_offspring <- "LM_number_of_offspring"
female_offspring <- read.table(file = female_offspring, sep=";", header=TRUE) %>%
  select(female)
female_offspring <- as.numeric(female_offspring)
female_offspring <- 5
```


### Generation intervall $L$

```{r GenerationIntervall}
library(dplyr)
## male
male_generationintervall <- "LM_generation_intervall"
male_generationintervall <- read.table(file = male_generationintervall, sep=";", header=TRUE) %>%
  select(male)
male_generationintervall <- as.numeric(male_generationintervall)
male_generationintervall
## female
female_generationintervall <- "LM_generation_intervall"
female_generationintervall <- read.table(file = female_generationintervall, sep=";", header=TRUE) %>%
  select(female)
female_generationintervall <- as.numeric(female_generationintervall)
female_generationintervall
```

## Proportion of calves and adults

```{r CalvesAdultsNumber}
number_calves_adults <- "LM_number_calves_adults"
number_calves <- read.table(file = number_calves_adults, sep=";", header=TRUE) %>%
  select(calves)
number_adults <- read.table(file = number_calves_adults, sep=";", header=TRUE) %>%
  select(adults)
proportion_adults <- number_adults/(number_adults+number_calves)
proportion_adults <- 0.5
proportion_calves <- number_calves/(number_adults+number_calves)
proportion_calves <- 0.5
```



### Proportion selected

```{r ProportionSelected}
library(dplyr)
## male
male_proportionselected <- "LM_proportion_selected"
male_proportionselected <- read.table(file = male_proportionselected, sep=";", header=TRUE) %>%
  select(male)
male_proportionselected <- as.numeric(male_proportionselected)
male_proportionselected <- 0.1
## female
female_proportionselected <- "LM_proportion_selected"
female_proportionselected <- read.table(file = female_proportionselected, sep=";", header=TRUE) %>%
  select(female)
female_proportionselected <- as.numeric(female_proportionselected)
female_proportionselected <- 0.5
```

### Economic values $a$

```{r}
library(dplyr)
# always calves first and CC,CF,CW
a <- "LM_economic_values"
a <- read.table(file = a, sep=";", header=TRUE)
aMat <- as.matrix(a)
a <- as.vector(aMat)
a
dim(t(a))
is.vector(a)
dim(aMat)
```

## Computations without equations

### Number of traits $n$

```{r}
n <- as.numeric(nrow(phenotypic_var_cov))
```


### Relationship Matrix $A_y$ and Inverse $A_y^{-1}$

```{r RelationshipMatrix}
## male
# Compute the relationsship matrix dependent on the number of offspring of the selection candidate. The selection candidate is the first animal.
suppressPackageStartupMessages(library(pedigreemm))
mnumb <- male_offspring+1
male_A <- pedigree(sire = c(NA,rep(1,times = male_offspring)), dam =c(NA,rep(NA,times = male_offspring)), label = 1:mnumb)
# Compute inverse of relationsship matrix.
male_Ainv <- getAInv(male_A)
##  female
# Compute the relationsship matrix dependent on the number of offspring of the selection candidate. The selection candidate is the first animal.
suppressPackageStartupMessages(library(pedigreemm))
mnumb <- female_offspring+1
female_A <- pedigree(sire = c(NA,rep(NA,times = female_offspring)), dam =c(NA,rep(1,times = female_offspring)), label = 1:mnumb)
# Compute inverse of relationsship matrix.
female_Ainv <- getAInv(female_A)
```

### Design matrix $Z_y$

```{r DesignMatrix}
# numbers of adults and calves in scenario
male_number_adults <- floor(proportion_adults*male_offspring)[[1]]
male_number_calves <- male_offspring-male_number_adults
proportion_adults
male_number_calves
female_number_adults <- floor(proportion_adults*female_offspring)[[1]]
female_number_calves <- female_offspring-female_number_adults
# Kronecker
kronecker_calves <- cbind(c(1,0,0),c(0,0,0),c(0,1,0),c(0,0,0),c(0,0,1),c(0,0,0))
kronecker_calves
kronecker_adults <- cbind(c(0,0,0),c(1,0,0),c(0,0,0),c(0,1,0),c(0,0,0),c(0,0,1))

# male
male_calves <- diag(1,male_number_calves)%x%kronecker_calves
male_calves
dim(male_calves)
male_calves <- cbind(male_calves,matrix(0, nrow=nrow(male_calves),ncol=male_number_adults*n))
male_adults <- diag(male_number_adults)%x%kronecker_adults
male_adults <- cbind(matrix(0, nrow=nrow(male_adults),ncol=male_number_calves*n),male_adults)
male_adults
male_Z <- rbind(male_calves, male_adults)
male_Z<-cbind(matrix(0, nrow=male_offspring*(n/2),ncol=n),male_Z)
male_Z
dim(male_Z)
# female
female_calves <- diag(1,female_number_calves)%x%kronecker_calves
female_calves
dim(female_calves)
female_calves <- cbind(female_calves,matrix(0, nrow=nrow(female_calves),ncol=female_number_adults*n))
female_adults <- diag(female_number_adults)%x%kronecker_adults
female_adults <- cbind(matrix(0, nrow=nrow(female_adults),ncol=female_number_calves*n),female_adults)
female_adults
female_Z <- rbind(female_calves, female_adults)
female_Z<-cbind(matrix(0, nrow=female_offspring*(n/2),ncol=n),female_Z)
dim(female_Z)
```

### Variance Covariance Matrices $G$ (genetic) and $R_y$ (residual)

```{r}
G <- genetic_var_cov

# male

male_calves_kronecker_residual <- diag(male_number_calves) %x% residual_var_cov_calves 
male_adults_kronecker_residual <- diag(male_number_adults) %x% residual_var_cov_adults 

male_calves_kronecker_residual_extended <- cbind(male_calves_kronecker_residual, matrix(0,nrow=nrow(male_calves_kronecker_residual),ncol=ncol(male_adults_kronecker_residual)))

male_adults_kronecker_residual_extended <- cbind( matrix(0,nrow=nrow(male_adults_kronecker_residual),ncol=ncol(male_calves_kronecker_residual)), male_adults_kronecker_residual)

dim(male_calves_kronecker_residual_extended)
dim(male_adults_kronecker_residual_extended)

male_R <- rbind(male_calves_kronecker_residual_extended,male_adults_kronecker_residual_extended)


# female

female_calves_kronecker_residual <- diag(female_number_calves) %x% residual_var_cov_calves 
female_adults_kronecker_residual <- diag(female_number_adults) %x% residual_var_cov_adults 

female_calves_kronecker_residual_extended <- cbind(female_calves_kronecker_residual, matrix(0,nrow=nrow(female_calves_kronecker_residual),ncol=ncol(female_adults_kronecker_residual)))

female_adults_kronecker_residual_extended <- cbind( matrix(0,nrow=nrow(female_adults_kronecker_residual),ncol=ncol(female_calves_kronecker_residual)), female_adults_kronecker_residual)

dim(female_calves_kronecker_residual_extended)
dim(female_adults_kronecker_residual_extended)

female_R <- rbind(female_calves_kronecker_residual_extended,female_adults_kronecker_residual_extended)
dim(female_R)

```

### Selection intensity $i_y$ and value of trunctation $x_y$

```{r}
# male
male_i <- dnorm(qnorm(1-male_proportionselected))/male_proportionselected
male_x <- qnorm(male_proportionselected, lower.tail = FALSE)
male_i
male_x
# female
female_i <- dnorm(qnorm(1-female_proportionselected))/female_proportionselected
female_x <- qnorm(female_proportionselected, lower.tail = FALSE)
female_i
female_x
```

## Computations with Equations

### Factor of variance reduction $k_y$

$$k_y=i_y(i_y-x_y)$$

```{r}
# male
male_k <- male_i*(male_i-male_x)
male_k
# female
female_k <- female_i*(female_i-female_x)
female_k
```


### Prediction error variance $PEV_y$

$$PEV_y=(Z_y^TR_y^{-1}Z_y+A_y^{-1} \otimes G^{-1})^{-1}[1:n,1:n]$$

```{r PEV}
dim(male_Z)
dim(male_Ainv)
dim(male_R)
dim(female_Z)
dim(female_Ainv)
dim(female_R)
# male
male_PEV <- solve(t(male_Z)%*%solve(male_R)%*%male_Z+male_Ainv%x%solve(G))[1:n,1:n]
n
male_PEV
# female
female_PEV <- solve(t(female_Z)%*%solve(female_R)%*%female_Z+female_Ainv%x%solve(G))[1:n,1:n]
```

### Covariance matrix between true and estimated breeding values $C_y$

$$C_y=G-PEV_y $$

```{r CovarianceMatrix}
# male
male_C <- G-male_PEV
# female
female_C <- G-female_PEV
```

### Asymptotic covariance matrix $C_y^*$ between true and estimated breeding values

$$
\begin{bmatrix}
C_1^* \\
C_2^*
\end{bmatrix}
=
\left( 
\begin{bmatrix}
1+1/2k_1  &  1/2k_2 \\
1/2k_1    &  1+1/2k_2
\end{bmatrix}^{-1}
\otimes I_n
\right)
\bullet
\begin{bmatrix}
C_1 \\
C_2
\end{bmatrix}
$$

```{r AsymptoticCovarianceMatrix}
Ca <- (solve(matrix(c(1+0.5*male_k, 0.5*female_k,0.5*male_k, 1+0.5*female_k),nrow = 2, ncol = 2, byrow=TRUE))%x%diag(n))%*%rbind(male_C,female_C)
# male
male_Ca <- Ca[1:n,]
# female
female_Ca <- Ca[(1+n):(2*n),]

male_Ca
female_Ca

matrix(c(1+0.5*male_k, 0.5*female_k,0.5*male_k, 1+0.5*female_k),nrow = 2, ncol = 2, byrow=TRUE)

```

### Asymptotic genetic variance/covariance matrix $G^*$

$$G^*=G-1/2{\sum_{y=1}^{2}(k_y(a^TC_y^*a)^{-1}C_y^*aa^TC_y^*)}$$

```{r AsymptoticGeneticMatrix}
male_k
Ga<-G-0.5*(as.numeric(male_k*1/as.numeric(t(a)%*%male_Ca%*%a))*male_Ca%*%a%*%t(a)%*%male_Ca+
             as.numeric(female_k*1/as.numeric(t(a)%*%female_Ca%*%a))*female_Ca%*%a%*%t(a)%*%female_Ca)

```

### Accuracy of the estimated overall breeding value $r_y^*$

$$r_y^*=\sqrt{\frac {a^TC_y^*a}{a^TG^*a}}$$

```{r AccuracyOverall}
# male
male_ra <- sqrt(as.numeric(t(a)%*%male_Ca%*%a)/as.numeric(t(a)%*%Ga%*%a))
# female
female_ra <- sqrt(as.numeric(t(a)%*%female_Ca%*%a)/as.numeric(t(a)%*%Ga%*%a))
male_ra
female_ra
```

### Standard deviation of the estimated overall breeding value $\sigma^*$

$$\sigma^*=\sqrt{a^TG^*a}$$

```{r StandardDeviationOverall}
stdev_overall<-sqrt(as.numeric(t(a)%*%Ga%*%a))
stdev_overall
```

### Asymptotic genetic gain of the estimated overall breeding value

$$Q= \frac {\sum_{y=1}^{2} i_yr_y^*\sigma^*}{\sum_{y=1}^{2}L_y}$$

```{r GeneticGainOverall}
Qoverall_index <- (male_i*male_ra*stdev_overall+female_i*female_ra*stdev_overall)/(male_generationintervall+female_generationintervall)
Qoverall_index
```

### Correlated asymptotic genetic gain of traits when selecting for the aggregate genotype.

$$Q_m^*= \frac {\sum_{y=1}^{2} i_ya^T(C_y^*)_m * (\sqrt{a^TC_y^*a})^{-1}}{\sum_{y=1}^{2}L_y}$$

```{r GenGain}
QaCF<- (male_i*as.numeric(t(a)%*%male_Ca[,"aCF"])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
        female_i*as.numeric(t(a)%*%female_Ca[,"aCF"]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)
QaCF

QcCF<- (male_i*as.numeric(t(a)%*%male_Ca[,"cCF"])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
        female_i*as.numeric(t(a)%*%female_Ca[,"cCF"]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)
QcCF

QaCC<- (male_i*as.numeric(t(a)%*%male_Ca[,"aCC"])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
        female_i*as.numeric(t(a)%*%female_Ca[,"aCC"]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)
QaCC

QcCC<- (male_i*as.numeric(t(a)%*%male_Ca[,"cCC"])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
        female_i*as.numeric(t(a)%*%female_Ca[,"cCC"]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)
QcCC

QaCW<- (male_i*as.numeric(t(a)%*%male_Ca[,"aCW"])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
        female_i*as.numeric(t(a)%*%female_Ca[,"aCW"]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)
QaCW

QcCW<- (male_i*as.numeric(t(a)%*%male_Ca[,"cCW"])*1/(sqrt(as.numeric(t(a)%*%male_Ca%*%a))) +  
        female_i*as.numeric(t(a)%*%female_Ca[,"cCW"]) * 1/(sqrt(as.numeric(t(a)%*%female_Ca%*%a))))/(male_generationintervall+female_generationintervall)
QcCW

```



### Correlated asymptotic genetic gain of a trait in the aggregate breeding value involving not all traits

$$b=\sigma_n^{-1}(G_n)^Ta$$
Where $n$ indicates the trait. Here aCF.
```{r}
# B <- (1/G[which( colnames(G)=="aCF" ),"aCF"])*t(G[,"aCF"])*a
# B
# t(G[,"aCF"])*a
# aMat
# Ga[which( colnames(G)=="cCC" ),"aCF"]
# a[which( colnames(G)=="cCC" ),"aCF"]
```


$$Q_m^*= \frac {\sum_{y=1}^{2} i_yb^T(C_y^*)_m \sqrt{b^TC_y^*b}}{\sum_{y=1}^{2}L_y}$$
```{r GeneticGainTrait}
# aCFQ <- male_i*B[which(colnames(G)=="aCF")]*male_Ca[which( colnames(G)=="aCF" ),"aCF"]*sqrt(as.numeric(B[which(colnames(G)=="aCF")]^2*male_Ca[which( colnames(G)=="aCF" ),"aCF"]))
# 
# aCFQ
# 
# cCFQ <- male_i*B[which(colnames(G)=="cCF")]*male_Ca[which( colnames(G)=="cCF" ),"aCF"]*sqrt(as.numeric(B[which(colnames(G)=="cCF")]^2*male_Ca[which( colnames(G)=="cCF" ),"aCF"]))
# 
# cCFQ
# 
# aCCQ <- male_i*B[which(colnames(G)=="aCC")]*male_Ca[which( colnames(G)=="aCC" ),"aCF"]*sqrt(as.numeric(B[which(colnames(G)=="aCC")]^2*male_Ca[which( colnames(G)=="aCC" ),"aCF"]))
# 
# aCCQ
# 
# cCCQ <- male_i*B[which(colnames(G)=="cCC")]*male_Ca[which( colnames(G)=="cCC" ),"aCF"]*sqrt(as.numeric(B[which(colnames(G)=="cCC")]^2*male_Ca[which( colnames(G)=="cCC" ),"aCF"]))
# 
# cCCQ
# 
# CCaQ <- (male_i*as.numeric(t(CCaB)%*%male_Ca[,"aCF"])*sqrt(as.numeric(t(CCaB)%*%male_Ca%*%CCaB))+female_i*as.numeric(t(CCaB)%*%female_Ca[,"aCF"])*sqrt(as.numeric(t(CCaB)%*%female_Ca%*%CCaB)))/(male_generationintervall+female_generationintervall)
# 
# CCcQ <- (male_i*as.numeric(t(CCcB)%*%male_Ca[,"cCF"])*sqrt(as.numeric(t(CCcB)%*%male_Ca%*%CCcB))+female_i*as.numeric(t(CCcB)%*%female_Ca[,"cCF"])*sqrt(as.numeric(t(CCcB)%*%female_Ca%*%CCcB)))/(male_generationintervall+female_generationintervall)
# 
# CWaQ <- (male_i*as.numeric(t(CWaB)%*%male_Ca[,"aCF"])*sqrt(as.numeric(t(CWaB)%*%male_Ca%*%CWaB))+female_i*as.numeric(t(CWaB)%*%female_Ca[,"aCF"])*sqrt(as.numeric(t(CWaB)%*%female_Ca%*%CWaB)))/(male_generationintervall+female_generationintervall)
# 
# CWcQ <- (male_i*as.numeric(t(CWcB)%*%male_Ca[,"cCF"])*sqrt(as.numeric(t(CWcB)%*%male_Ca%*%CWcB))+female_i*as.numeric(t(CWcB)%*%female_Ca[,"cCF"])*sqrt(as.numeric(t(CWcB)%*%female_Ca%*%CWcB)))/(male_generationintervall+female_generationintervall)
# 
# single_trait <- data.frame(trait=c("CFa","CFc","CCa","CCc","CWa","CWc"), Sfr=c(CFaQ,CFcQ,CCaQ,CCcQ,CWaQ,CWcQ))
# sum(c(CFaQ,CFcQ,CCaQ,CCcQ,CWaQ,CWcQ))
```

```{r}
library(ggplot2)
#   
dataframe <- data.frame(names = c("Overall",rep(c("CFa","CFc","CCa","CCc","CWa","CWc"),times=2)), Unit = c(Qoverall_index,CFaQ,CFcQ,CCaQ,CCcQ,CWaQ,CWcQ,QaCF,QcCF,QaCC,QcCC,QaCW,QcCW), Strategy=c("index",rep(c("CFa","index"),each=6)))
# 
barplot <- ggplot(dataframe,aes(x=names,y=Unit,fill=Strategy))
 barplot + geom_bar(stat="identity",position="dodge")

```


### Plots

```{r}
library(ggplot2)
# Plot aggregate genotype
#AN_Qoverall_index <- Qoverall_index
LM_Qoverall_index <- 2
AN_Qoverall_CF <- 2
LM_Qoverall_CF <- 4

#Aggregate_Genotype <- data.frame(Gain=c(AN_Qoverall_index,LM_Qoverall_index,AN_Qoverall_CF,LM_Qoverall_CF),Breed=rep(c("Angus","Limousin"),times=2), Strategy=rep(c("Index","CF"),each=2))

#Aggregate_Genotype <- ggplot(Aggregate_Genotype,aes(Breed,Gain,fill=Strategy))

#Aggregate_Genotype + geom_bar(stat="identity",position="dodge")
```


