---
title: "How to contribute"
author: "Sophie Kunz and Peter von Rohr"
date: "7/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description of Steps
This document describes the steps that it takes to make contributions to this project repository. This website works with `Github Pages` which runs on `github`. A short introduction on how to get started with Github Pages is available at https://pages.github.com/. 

When working with Github Pages it is important to remember that all material that is supposed to appear as a webpage needs to be located in the `gh-pages` branch of the repository. We propose to create new material in the master branch and to deploy the material that appears on the website to the gh-pages branch located in a different directory on the local machine.

The initial steps for our project repository are already done. All you need to do is to work through the following steps. 

* __Step 1__: Create the parent directory that holds the branch-specific subdirectories

```
PARENTDIR=EarlyMaturityBeef
MASTER=master
GHPAGES=gh-pages
mkdir -p $PARENTDIR/$MASTER $PARENTDIR/$GHPAGES
```

* __Step 2__: Clone the two branches into their specific directories

```
cd $PARENTDIR/$MASTER;git clone https://github.com/charlotte-ngs/EarlyMaturityBeef.git;cd ../..
cd $PARENTDIR/$GHPAGES;git clone https://github.com/charlotte-ngs/EarlyMaturityBeef.git -b $GHPAGES;cd ../..
```

* __Step 3__: Develop new material in the master branch. Deploy the HTML-files and other output to the gh-pages branch

* __Step 4__: Commit and push the two branches

```
cd $PARENTDIR/$MASTER;git add .;git commit -m"Comment";git push origin $MASTER;cd ../..
cd $PARENTDIR/$GHPAGES;git add .;git commit -m"Comment";git push origin $GHPAGES;cd ../..
```

* __Step 5__: Check whether new material appeared.


```{r, results='asis'}
cat(rmddochelper::get_latest_change(), "\n")
```

