---
title: "Design Function For Computations Of Economic Values and Index"
output: html_notebook
---


## Disclaimer


## General Function
The general function can be designed as follows

```{r funceconomicvalue, eval=FALSE}
#' @title
#'
#' @description
#'
#' @param pvec_class_freq  discrete empirical distribution of population for given trait
#' @param pvec_threshold   thresholds under continuous distribution given by pricing system
#' @param pvec_price       vector of prices for given categories
#' @param pn_mean          current population phenotypic mean
#' @param pn_sd            current population phenotypic standard deviation
#' @param pn_delta_mean    small change of current phenotypic population mean
#' @return vector of economic values
compute_economic_value <- function( pvec_class_freq = NULL,
                                    pvec_threshold  = NULL,
                                    pvec_price,
                                    pn_mean,
                                    pn_sd,
                                    pn_delta_mean ){
  
  if(is.null(pvec_class_freq)) {
    # case of carcass weight
    
  } else if (is.null(pvec_threshold)){
    # case of cf* and cc*
    
  }
  
  return(vec_ev_result)
  
}
```



## Carcass Weight
The following function computes the economic value of the trait age-adjusted __carcass weight__. The economic value is defined as the change in profit for a small change in the population mean of the trait.


```{r}
#' @title Compute Economic Value
#'
#' @description
#' The economic value of the trait is computed as profit per carcass weight.
#'
#' @param pn_profit the current value of the profit
#' @param pn_carcass_weight  the current population mean for caracass weight
#' @return pn_economic_value result of economic value
compute_economic_value <- function(pn_profit, pn_carcass_weight){
  # compute economic value
  pn_economic_value <- pn_profit / pn_carcass_weight
  return(pn_economic_value)
}
```

Now we are ready to test the defined function

```{r}
my_ev_result <- compute_economic_value(pn_profit = 384, pn_carcass_weight = 271.3)
my_ev_result
```


### Extended Version
```{r}
economic_value_profit <- function(pn_revenue = NA, pn_cost = NA, pn_carcass_weight){
  if (is.na(pn_cost)){
    pn_economic_value <- pn_revenue / pn_carcass_weight
  } else if (is.na(pn_revenue)) {
    pn_economic_value <- pn_cost / pn_carcass_weight
  }
}
```


In the current population, we have the following economic parameters.

$$G = E - K$$
where $G$ is profit, $E$ is revenue and $K$ is costs all per slaughter animal, respectively


$$E = p * SG$$

where $p$ is the price per kg carcass weight and $SG$ is the cracass weight. Hence

$$G = p * SG - K$$


Assume carcass weight is increased by $\Delta_{SG}=1$ kg and hence $SG^* = SG + \Delta_{SG}$

$$E^* = p * SG^*$$

The new profit corresponds to $G^*$
$$G^* = E^* - K = p * SG^* - K$$

The economic value $EV$ is defined as

$$EV = \frac{G^* - G}{\Delta_{SG}} = \frac{E^* - K - (E - K)}{\Delta_{SG}} = \frac{E^* - E}{\Delta_{SG}} = \frac{p * SG^* - p * SG}{\Delta_{SG}} = p$$


Our computation

$$\rho = \frac{G}{SG}$$

$$G^* = G + \rho * \Delta_{SG}$$





## Carcass Fat

```{r}
categorical_economic_value <- function(pvec_trait_distribution, pvec_trait_price){
  
}
```

