---
title: "Frühreife beim Fleischrind"
author: "Sophie Kunz und Peter von Rohr"
date: "21.03.2018"
output: html_document
bibliography: 
- library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style type="text/css">
h1.title {
  font-size: 32px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkRed;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkRed;
}
h3 { /* Header 3 */
  font-size: 18px;
  color: DarkRed;
}
</style>

# Script Silvan Wyss

# Background Silvan

Up until summer 2018, the Swiss beef cattle breeders association has been focusing their genetic evaluations
mainly on growth rate and carcass conformation. There might be evidence that
the level of carcass fatness is decreasing at least for some beef cattle breeds [@Hospenthal2016]. Decreasing levels of carcass fat are a hint that Swiss beef cattle is getting later mature than before.

Early maturity is here defined as the amount of time until an animal reaches the necessary requirements to be slaughtered without any price reductions per kg of carcass weight.

Cattle beef producers get important selling price reductions per carcass weight when the carcass fat (Bild von Rückenspeckdicke dick und dünn), carcass conformation (Bild gute Fleischigkeit, schlechte Fleischigkeit) and carcass weight are not fitting into the desired frame. For example  [@Proviande2018]. 

In order to get no selling price reductions they have to feed their animals for a longer time, when their animals do not mature early. The problem now is that during this time they realize that their costs of feeding and keeping the animals is more than the additional revenue they get by having higher carcass weights. Also, in Switzerland the carcass should not weight too much. Actually generally the carcasses in Switzerland are much smaller than abroad in order to fulfill the wishes of the market. That is why beef cattle in Switzerland has to be earlier mature than abroad [@Hospenthal2016]. 

There are animals of lower age which have more carcass fat, more carcass weight and better carcass conformation than other animals. This trait of an animal is what we call early maturity. Early mature animals should be selected in order to reduce the costs for cattle beef producers. 

But how do you get a strategy for selecting early mature animals? One possibility is to derive it from an already recorded trait.  They build up proteins earlier than fat usually [@Thonney2015]. If you now know that carcass fat is somehow dependent on the already established carcass conformation and carcass weight to the right amount then you could say that you just have to breed for carcass fat corrected by the age at slaughter to have animals that can go early to the slaughterhouse and not receive any price reductions. 

To use this link between early maturity and carcass fat, beef cattle breeders in Switzerland have decided
to estimate breeding values for carcass fat. The heritability would be high enough for carcass fat to efficiently breed for it. 

However you need some evidence that carcass fat and early maturity are closely linked to each other. Otherwise you might eventually select animals that are early in running to fat but are still light and thin. Then the deriving trait carcass fat would not be sufficient to derive the trait early maturity.

Also there is the breed Limousin which underperforms in carcass fat. Nevertheless offspring of Limousin sires are most prevalent in the favoured category of carcass conformation C3. This shows that for breeding you should always combine the two traits carcass conformation and carcass fat [@Hospenthal2016]. 

To prevent that you can also choose to combine carcass weight, carcass conformation and carcass fat to one index which then is called early maturity or early readiness for slaughter. To act at best reasons to improve the income of beef cattle producers you should weight the different traits in the index according to their economic value to the cattle producers [@Englishby2017]. 

Commercial cattle are generally determined as ready for slaughter by visual inspection of the degree of fatness within the appropriate range of live weight [@VanGroningen2006].

Carcass conformation correlates with carcass fat by about 0.31. Age at slaughter correlates positiveley with carcass fat but not linear (concave with decreasing slope) [@Hospenthal2016].

The older the animal the higher the proportion of fat tissue in comparison to muscle tissue and bone tissue [@Thonney2015].

The higher the age at slaughter of an animal is the higher is the impact of genetics on the beef carcass traits [@Englishby2017].

In Ireland the usually cross crossbred suckler cows to purebred beef sires. Also they use an multi-trait across breed animal model. There the include 15 traits including carcass weight and carcass fat. The heritability is 0.31 for carcass fat [@Evans2007].

In Switzerland the "Bundesamt für Landwirtschaft" has to determine the methods to classify carcasses of ruminants. The criteria are the age at slaughter, the carcass conformation and the carcass fat [@Bundesrat2002].

Another problem is, that 

The profit of cattle breeders is dependent on their costs and incomes. Their income is mostly composed of the sale of their animals to slaughterhouses.

## Background Sophie/Peter
Up until summer 2018, the Swiss beef cattle breeders association has been focusing their genetic evaluations
mainly on traits such as growth rate and proportion of carcass lean meat. There might be evidence that
the level of carcass fatness is decreasing at least for some beef cattle breeds (see (Hospenthal 2016) for a
possible source). Decreasing levels of carcass fatness has a negative effect on time of carcass maturity and an
important economic impact for beef cattle producers, because slaughterhouses reduce the price for carcasses
with an insufficient fatness level. To address this problem, beef cattle breeders in Switzerland have decided
to estimate breeding values for carcass fatness. These breeding value estimates represent a first tool for
improving early maturity in beef cattle. The first results of the routine breeding value estimation for carcass
fatness will be published in summer 2018.

## Aim Sophie/Peter
This project aims at comparing different breeding strategies for improving early maturity in beef cattle. The
different strategies that are proposed are described in the following section.

## Strategies Sophie/Peter
* Breeding value estimation for carcass fatness: Starting in summer 2018 breeding values for
carcass fatness are estimated for beef cattle. The estimated breeding values for carcass fatness are a first
tool to improve early maturity. At this stage it is important to describe how the estimated breeding
values of carcass fatness as a single trait can be used to improve early maturity in beef cattle.
* Carcass trait index: In most cases, animal breeders are interested to consider more than one trait
simultaneously for their selection decisions. Selection index theory provides an approach to optimally
combine a set of traits when selecting animals as potential parents.
* Approach by Berry: (Berry, Cromie, and M.Judge 2017) defined a new trait called “deviation in age
at slaughter” (DAGE). They used this trait to access the genetic potential of selection candidates for
early maturity.
* Growth models: In pigs, (de Greef 1992) used specialized growth models to quantify the transformation
of nutrients into the deposition of protein and fat in a carcass. The same type of models can also be
applied to beef cattle. Based on the results of these growth models, the property of early maturity can
be derived.









# German script Sophie/Peter

## Ziel
Das Ziel dieser Arbeit ist es verschiedene züchterische Massnahmen zur Verbesserung der Frühreife in der Fleischrinderzucht vorzuschlagen, diese zu beschreiben und die Vorschläge miteinander zu vergleichen. 

## Hintergrund
Bis im Sommer 2018 wurden in der Routine-Zuchtwertschätzung für Mutterkuh Schweiz (VMS) vor allem die Merkmale Nettozuwachs und  Fleischigkeit berücksichtigt. 

Gewisse Gruppierungen in der Fleischrinderzucht vermuten, dass aufgrund der relativ starken Gewichtung der Fleischigkeit, bei gewissen Rassen eine Abnahme der  Fettabdeckung beobachtet werden kann. Als mögliche Quelle wird hier auf die  Masterarbeit von Andrea Hospenthal [@Hospenthal2016] verwiesen. Eine abnehmende Fettabdeckung würde sich negativ auf die Frühreife auswirken. Für die Mäster oder Mutterkuhhalter hat die Frühreife eine hohe wirtschaftliche Bedeutung. Aufgrund der Bezahlungssysteme in den Schlachthöfen müssen die Schlachtkörper der gemästeten Tiere bezüglich Fleischigkeit und Fettabdeckung bestimmte Anforderungen erfüllen, damit keine Preisabzüge gemacht werden. Wenn ein Tier früher geschlachtet werden kann und trotzdem die Anforderungen des Schlachthofs erfüllt, entstehen für den Mäster oder den Mutterkuhhalter weniger Kosten. Auf dieser Kosteneinsparung basiert die wirtschaftliche Bedeutung der Frühreife.

Aus diesem Grund werden ab Sommer 2018 die Zuchtwerte für Schachtmerkmale überarbeitet. Neu werden Zuchtwerte für Fleischigkeit, Fettabdeckung und Schlachtgewicht geschätzt und publiziert. 

## Massnahmen
In diesem Abschnitt werden verschiedene Massnahmen zur Verbesserung der Frühreife beschrieben. Bei der Einführung des Zuchtwerts für das Merkmal Fettabdeckung steht die Umsetzung kurz bevor, die Einführung eines Schachtleistungsmerkmaleindex und der Ansatz von Berry et al. [@BCJ2017] sind geplant, aber deren Umsetzung ist noch nicht terminiert. Für die Massnahme mit den Wachstumsmodellen wurde noch keine Umsetzung geplant. Ziel dieser Arbeit ist es die vorgeschlagenen Massnahmen zu beschreiben und deren Brauchbarkeit für die Zucht auf Frühreife zu beurteilen.



### Zuchtwert Fettabdeckung
Ab der Routine-Zuchtwertschätzung im Sommer 2018 werden Zuchtwerte für das Merkmal Fettabdeckung (Klassen 1 bis 5) geschätzt und publiziert. Diese Einzelzuchtwerte im Merkmal Fettabdeckung sind ein erstes Werkzeug zur züchterischen Verbesserung der Frühreife. Hier geht es darum, wie der Einzelzuchtwert der Fettabdeckung in der Zuchtarbeit eingesetzt werden kann. 

### Index Schlachtleistungsmerkmale
Da in der Zuchtarbeit selten nur ein Merkmal von Bedeutung ist, müssen wir eine Strategie finden, wie eine Anzahl von Merkmalen gemeinsam für die Auswahl der Elterntiere der nächsten Generation berücksichtigt werden kann. Der optimale Ansatz für dieses Problem ist die Indexselektion, wobei ein Index als Schätzung des Gesamtzuchtwertes aufgestellt wird. Die für den Gesamtzuchtwert benötigten wirtschaftlichen Gewichte können aufgrund der Bezahlungssysteme im Schlachthof abgeleitet werden (siehe dazu [@vonRohr1998]).

### Ansatz von Berry
In einer Arbeit von Berry et al. [@BCJ2017] wird ein Merkmal "differential age" (DAGE) definiert und die genetische Variation für dieses Merkmal wird geschätzt. Dieses Merkmal soll quantifizieren, ob es bei konstanter Schlachtgewicht und konstanter Fettabdeckung genetische Unterschiede beim Schlachtalter der Tiere gibt. Ziel ist es, bei optimalen Schlachtleistungsmerkmalen möglichst junge, das heisst, möglichst frühreife Tiere zu selektieren.


### Wachstumsmodelle
Analog zur Arbeit von [@deGreef1992] bei den Schweinen, kann das Wachstum beim Fleischrind auch mittels Wachstumskurven modelliert werden. Aufgrund der Resultate der Wachstumsmodelle können Frühreife und andere Schlachtleistungsmerkmale abgeleitet werden. Bei diesem Ansatz stellt sich die Frage nach der Verfügbarkeit der Inputparametern für die Wachstumsmodelle. 


## Vorgehen
Wir schlagen vor, die Arbeiten aufgrund der folgenden Schritte umzusetzen

* __Schritt 1__: Beschreibung der Problemstellung und der Relevanz der Zucht auf Frühreife bei den Fleischrindern in der Schweiz. Dabei soll vor allem auf die Heterogenität in den Sektoren Mutterkuhhaltung und Mäster eingegangen werden.
* __Schritt 2__: Literaturübersicht zum gestellten Thema. Was wurde bereits gemacht und welche Ansätze sind im Ausland umgesetzt
* __Schritt 3__: Beschreibung der vorgeschlagenen Massnahmen und eventuell Vorschlag eigener Massnahmen
* __Schritt 4__: Vergleich der Massnahmen untereinander im Bezug auf Einfachheit bei der Umsetzung, Verfügbarkeit der benötigten Informationen und Erfolgsaussichten der züchterischen Verbesserung der Frühreife. 
* __Schritt 5__: Konkrete Ausarbeitung einer Umsetzung für den Index der Schlachtleistungsmerkmale. Dieser Teil beinhaltet die eigentlichen Resultate der Arbeit
* __Schritt 6__: Diskussion der Resultate und Ausblick


## Anforderungen und Unterstützungen
Das gestellte Thema muss vom Studierenden selbstständig bearbeitet werden. Dabei wird sie/er von der Betreuung bei Qualitas unterstützt. Diese __Unterstützung__ umfasst die folgenden Punkte 

* Einführung in das Thema der Frühreife bei den Fleischrindern
* Erklärung der Zuchtwertschätzung der Fettabdeckung
* Vermittlung der Grundlagen der Indexzucht
* Unterstützung bei der Aufbereitung von Daten
* Anleiten bei der Gliederung und dem Verfassen der Arbeit
* Weitere Unterstützung je nach Bedarf

Die Studentin oder der Student soll für einen erfolgreichen Abschluss der Arbeit die folgenden __Anforderungen__ erfüllen 

1. Erstellen einer Literaturübersicht zum Thema Frühreife in der Fleischrinderzucht
2. Beschreibung der Relevanz der Frühreife in der Fleischrinderzucht
3. Beschreibung der vorgeschlagenen Massnahmen zur züchterischen Verbesserung der Frühreife bei Fleischrindern
4. Umsetzung der Eigenschaft der Frühreife in messbare Merkmale gemäss der vorgeschlagenen Massnahmen
5. Ausarbeitung einer Umsetzungsvariante für einen Index der Schlachtleistungsmerkmale 
6. __Erster Zusatz__: Umsetzung eines Indexes für Schlachtleistungsmerkmale mit konkreten Daten aus der Routinezuchtwertschätzung von VMS
7. __Zweiter Zusatz__: Umsetzungen des Ansatzes von Berry et al. [@BCJ2017] und von Wachstumsmodellen


## Bewertung
Dieser Abschnitt beschreibt die Bewertung der eingereichten Masterarbeit. 

* Für das Bestehen der Arbeit müssen die Punkte 1 - 3 zwingend vorhanden sein. 
* Sofern die Punkte 1 - 5 gut umgesetzt sind, wird die Arbeit als sehr gut bewertet werden. 
* Die Zusatzpunkte 6 und 7 können je nach Kapazitäten realisiert werden und fliessen, falls vorhanden positiv in die Bewertung ein.


```{r BiblioDef, echo=FALSE, results='hide'}
vec_bib <- c(bibentry(
  bibtype = "MastersThesis",
  title = "Schlachtdatenauswertung der Markenprogramme von Mutterkuh Schweiz",
  author = as.person("A. Hospenthal [aut]"),
  year = 2016,
  school = "ETH Zürich",
  key = "Hospenthal2016"),
  bibentry(
    bibtype = "Article",
    title = "Rapid Communication: Large exploitable genetic variability exists to shorten age at slaughter in cattle",
    author = c(as.person("D. P. Berry"),
               as.person("A. R. Cromie"),
               as.person("M. M.Judge")),
    journal = "Journal of Animal Science",
    volume = 95,
    number = 10,
    pages = "4526-4532",
    year = 2017,
    doi = "10.2527/jas2017.2016",
    URL = "http://dx.doi.org/10.2527/jas2017.2016",
    key = "BCJ2017"),
  bibentry(
    bibtype = "PhdThesis",
    title = "Wirtschaftliche Gewichte für Mastleistungs- und Schlachtkörperqualitatsmerkmale beim Schwein",
    author = as.person("P. von Rohr"),
    year = 1998,
    school = "ETH Zürich",
    key = "vonRohr1998"),
  bibentry(
    bibtype = "PhdThesis",
    title = "Prediction of production : nutrition induced tissue partitioning in growing pigs",
    author = as.person("K.H. de Greef"),
    year = 1992,
    school = "Wageningen University",
    key = "deGreef1992"
  ))
sBibFile <- "20180321_FruehreifeFleischrind.bib"
if(!file.exists(sBibFile))
  cat(paste(toBibtex(vec_bib), collapse = "\n"), "\n", file = sBibFile)
```

```{r, echo=FALSE, results='asis'}
cat(rmddochelper::get_latest_change(ps_msg = "Letzte Änderung"))
```

---

`r if (knitr:::is_html_output()) '# References {-}'`


