---
title: "Selectionintensity"
output: html_notebook
---

Assume we are given a certain proportion of selected animals for the two sexes `male` and `female`. 

```{r, results='asis'}
tbl_prop_sel <- tibble::data_frame(male=.2, female=.5)
rownames(tbl_prop_sel) <- "proportion selected"
knitr::kable(tbl_prop_sel)
```


Given the proportion selected, we want to compute the selection intensity. For this we need some properties of the normal distribution.

The first quantity to compute are the quantiles that belong to the proportions.

```{r}
(quant_male <- qnorm(tbl_prop_sel$male, lower.tail = FALSE))
(quant_female <- qnorm(tbl_prop_sel$female, lower.tail = FALSE))
(sel_quant <- qnorm(c(tbl_prop_sel$male, tbl_prop_sel$female), lower.tail = FALSE))

```

From the quantiles we can compute the ordinates ($z$)

```{r}
(sel_ords <- dnorm(c(quant_male, quant_female)))
```

Finally the selection intensity is computed as

$$i = z/p$$

```{r}
(sel_int <- sel_ords/tbl_prop_sel["proportion selected",])
```

Computing the values of the variance reductions ($k$)

```{r}
(sel_k <- sel_int * (sel_int - sel_quant))
```


$$X = \begin{bmatrix}1 & x_{1}\\
1 & x_{2}\\
1 & x_{3}
\end{bmatrix}$$


More complicated example

$$
\begin{bmatrix}
C_1^* \\
C_2^*
\end{bmatrix}
=
\left( 
\begin{bmatrix}
1+1/2k_1  &  1/2k_2 \\
1/2k_1    &  1+1/2k_2
\end{bmatrix}^{-1}
\otimes I_n
\right)
\bullet
\begin{bmatrix}
C_1 \\
C_2
\end{bmatrix}
$$












