---
title: "Verify GeneticGainUnivariateSingleSP"
output: html_notebook
---

This notebook is used to verify the computations that are done in GeneticGainUnivariateSingleSP.Rmd

The selection intensity based on the proportion of $p$ 

```{r, echo=FALSE}
#intensity of selection (i) computed by proportian selected (p)
p <- 0.2
(i <- dnorm(qnorm(1-p))/p)
```

The factor for the variance reduction

```{r}
#generation intervall (L) in years
L <- 2
#number of progeny (pr) of the selection candidate
pr<-10
#factor of variance reduction (k)
(k <- i * (i - qnorm(p)))
```

The relationship matrix

```{r}
#relationshipmatrix (A) of the selection candidate
suppressPackageStartupMessages( library(pedigreemm))
numb <- pr+1
ped <- pedigree(sire = c(NA,1,1,1,1,1,1,1,1,1,1), dam = c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA), label = 1:numb)
# A <- getA(ped)
(Ainv <- as.matrix(getAInv(ped)))
```


The univariate parameters (phenotypic, genetic and residual variances)

```{r}
#genetic variance (g) of the trait
g<-0.12067
#phenotypic variance (ph) of the trait
ph<-0.39365
#residual variance (r) of the trait
r<-0.23651
```


The prerequisites for the PEV. Start with design matrix $Z$

```{r}
#design matrix (Z) connecting the records of observations with the breeding values
(Z<-cbind(matrix(0, nrow=pr,ncol=1),diag(pr)))
```

The residual variance matrix

```{r}
#variance-relationship matrix (R) of the residuals for the recorded animals
# R<- r%x%diag(pr)
(Rinv <- (1/r) %x% diag(pr))
```


```{r}
#prediction error variance (PEV)
(PEV1 <- solve( t(Z) %*% Rinv %*% Z + Ainv * (1/g)))
(PEV2 <- solve( crossprod(Z) * 1/r + Ainv * (1/g)))
PEV1-PEV2
```

