---
title: "Breeding strategies for early maturity in beef cattle"
author: "Silvan Wyss"
date: "11/22/2018"
output: beamer_presentation
header-includes:
  # - \setbeameroption{hide notes} # notes are not shown
  - \setbeameroption{show notes}   # notes are shown after slide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Target

* Problem: Negative trend in early maturity.

* Here maturity is readiness for slaughter.

* Bad performence in early maturity --> increased costs.

* Qualitas commissioned by Mutterkuh Schweiz to solve this problem.

* My part: Which proposed strategies are most suitable to breed for early maturity in beef cattle?

\note{
Welcome to my presentation about strategies to breed for early maturity in beef cattle. My name is Silvan and I write my master thesis in association with Qualitas AG and Mutterkuh Schweiz. Mutterkuh Schweiz the Swiss beef breeders association is a customer of Qualitas AG and has a problem to be solved.
The problem is, that Swiss beef cattle is getting worse in early maturity "Frühreife".
This trait is an economically important trait for beef cattle breeders.
With early maturity I mean the readiness for slaughter. 
For example, imagine two beef carcasses which are exactly the same and get exatly the same price. 
For one carcass an animal has lived 250 d and for the other 230 d. 
Then the one that only lived for 230 d is the one which earlier mature than the other.
It is obvious that the one which only lived for 230 d led to much less costs for the breeder than the one which lived for 250 d.
*Beef cattle as title image and labels Mutterkuh Schweiz and Qualitas.*
}


## Strategies

**1. Derivation of early maturity from carcass fat corrected by age at slaughter.**

**2. Index over carcass traits corrected by age at slaughter to breed for early maturity.**

\note{
Qualtitas tries to solve the problem by breeding for animals whith good performances in early maturity. 
However it is not an easily measurable trait, which makes breeding for it difficult.
Probably due this reason breeding for early maturity is not established in any major breeding program.
Even the word early maturity has not been present in any scientific paper I read about beef breeding.
Therefore the question I want to answer in my master thesis is how Qualitas could breed for early maturity in beef cattle.
Nevertheless my supervisors have found 4 possible strategies to breed for early maturity.
I have evaluated the two most feasible and promising strategies. 
The first strategy is already implemented. 
It uses the breeding value carcass fat which is corrected by age at slaughter to derive from it early maturity.
The second strategy is new and tries to use an index over all breeding values for carcass traits to breed for early maturity.
}

## Carcass traits

* Carcass fat (CF)

* Carcass conformation (CC)

* Carcass weight (CW)

\note{
Both are very promising because the data which they use is already available. 
Since 1992 Proviande routenely records data from beef carcass traits.
These carcass traits are carcass fat, carcass conformation and carcass weight. 
Carcass fat and carcass conformation are visually classified into 5 classes and carcass weight
is the weight of the carcass in kg. 
Of all of them there already exist two breeding values. One for carcasses which were calves and one for carcasses which were adults (cows not included)).
}

## 1. Strategy (carcass fat)

* Carcass fat probably correlated with early maturity 

* Tool for evaluation: Genetic gain.

* Genetic gain predicts the progress of traits under a selection scenarium.

* Selection for Carcass fat is called Scenarium 1.

\note{
Carcass fat corrected by age at slaughter could be used to derive early maturity because these traits are assumed to be closely correlated. 
*This assumption is based on practical experience from beef breeders and on the theoretical knowledge of beef cattle growth.* 
The amount of fat tissue during growth is usually the limiting factor for carcass maturity (Image). To evaluate this strategy, I have used a well-established tool: The genetic gain. 
The genetic gain predicts the development of traits under a modelled selection scenarium. 
Usually it is expressed in trait unit per year. 
Here the scenarium is that beef cattle breeders will only select for increased carcass fat. 
Furthermore I assume that breeding occurs only within breeds. 
To get the best overview on all beef breeds I chose to do the evaluations on Angus and Limousin. 
Two important breeds which are very different in terms of early maturity. 
While Angus is assumed to mature early, Limousin is known to mature late. 
Therefore I have computed the genetic gain separateley for these breeds.
}

## Aggregate genotype

* Genetic Gain for aggregate genotype $H$

$$H=\sum{a_mu_m}$$

where 

$a$ is an (economic) weighting factor,

$u$ is a true breeding value and

$m$ indicates the breeding values CFa, CFc, CCa, CCc, CWa and CWc.
CF = Carcass fat, CC = Carcass conformation, CW = Carcass weight, a = adults, c = calves.

\note{
However the genetic gain of the trait carcass fat alone is not very meaningful if I like to find out if this strategy is effective in breeding for early maturity. 
Therefore I computed the genetic gain not only of carcass fat, but also of the economic value of an animal in terms of carcass traits. 
This economic value is called aggregate genotype. 
I computed it by the weighed sum of the breeding values for six carcass traits carcass fat, carcass conformation and carcass weight for calves and adults respecteveley. 
I have computed the weights using economic profit equations based on CHTAX, the payment system for beef carcasses in Switzerland.
However I will not explain this here in detail because it is somehow a topic for itself and is not directly relevant for the understanding of my results. 
Anyway, this aggregate genotype has the unit Swiss Francs which makes the unit of its genetic gain Swiss Francs per year. 
The higher the aggregate genotype's genetic gain the more efficient may be this strategy in breeding for early maturity.
}


## Genetic gain

Dependent on

* Generation intervall

* Selection Intensity

* Standard Deviation of the selection criterion

* Accuracy of the selection criterion

* Selection criterion here = Estimated breeding value for carcass fat.

* Bulmer effect [Bulmer] taken into account

\note{
The genetic gain is dependent on the generation intervall which determines fast selection occurs, 
on the selection intensity, which determines how large the proportion of the selected population is which will produce the offspring for the next generation, 
on the standard deviation of selected criterion in the population which is the potential for breeding 
and on the accuracy of selection which is a measure of how similar the selected parents are to their progeny in the selection criterion.
I have got generation intervall and selection intensity from a population structure report about Swiss beef cattle breeds.
For the value of accuracy and standard deviation I used known genetic variances and covariances between the carcass traits and assumed a certain number of offspring which give information to the estimated breeding values for the carcass traits.
Hier Zeichnungsbilder einfügen um die Begriffe zu klären?
}

## Correlated genetic gain

* Carcass Fat ~ Aggregate genotype

* Carcass Conformation ~ Aggregate genotype

* Carcass Weight ~ Aggregate genotype

\note{
Then I got the genetic gains for the carcass traits by multiplying the genetic gain for the aggregate genotype with the right correlation coefficient. In this graphic you can see again, what a correlation coefficient is. Actually it is just the slope of a line through a lot of points.
}

## 2. Strategy (index)

* Index as selection criterion

* Different standard deviation and accuracy

\note{
In the second strategy the selection is based on an index which has the same shape as the aggregate genotype, including all 6 estimated breeding values for carcass traits and all 6 economic weighing factors.
Again I computed the genetic gain for the aggregate genotype and for its correlated breeding values.
But the values were not the same because the selection is now based on the index and not on the breeding value for carcass fat alone, which changed the standard deviation and the accuracy.
}

## Results

(Here you can see the genetic gain per year for the aggregate genotype in the two scenarios.)













## CHTAX

Whithin carcass categories price reductions if:

- Carcass fat class $\neq$ 3 (optimum)

- Carcass conformation $\neq$ C (maximum)

- Carcass weight above certain limit (dependent on carcass category)

?? Graphics describing areas of price reduction along range of traits. Use Open Office.

## Why

Long-term assignment of Mutterkuh Schweiz for Qualitas AG:

?? Labels of Mutterkuh Schweiz and Qualitas AG + Image of beef cattle.

Developing breeding value estimation for beef cattle in Switzerland.
Until 2018 breeding in Swiss beef cattle focused on daily gain and carcass conformation which means the faster they grow and the meatier they grow the better.

## Why

Until summer 2018 breeding focused on the traits daily gain and carcass conformation.

During this time: 

- Prooved: The trait carcass fat has decreased to significantly below class 3 in most beef cattle breeds.

?? Graphic with mean performance carcass fat along range of breeds as barplot

- Assumed: Performance in early maturity decreased as well.

## Why

Assumed negative effects for breeders and producers:

- Higher carcass price reductions for poor carcass fat performances.

- Combination of high costs and high price reductions.

Mutterkuh Schweiz: "This trend must stop."

## Why
Issue with low carcass fat classes already solved:

- Introduction of breeding value for carcass fat in summer 2018.

However, breeding strategy for early maturity not clear yet.

- Decision for a strategy is planned for 2019.

## How

Evaluation of 4 proposed approaches:

**1. Derivation from carcass fat**

**2. Index over carcass traits**

3. Derivation in age at slaughter (Berry)

4. Derivation over growth models

## How

Different results with 1. and 2.?

Comparison of 

- Animal ranks

- Genetic gains per trait

## How

- Breeding value carcass fat available

- Index computed using economic values from simple profit equations. (Show Equation with $H=a*w+a*w$)



## 

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


