---
title: "Breeding strategies for early maturity in beef cattle"
author: "Silvan Wyss"
date: "11/22/2018"
fontsize: 15pt
bibliography: /Users/silvan/Documents/EarlyMaturityBeef/embc-thesis-bd/library.bib
output: 
  beamer_presentation:
    includes:
      in_header: header_pagenrs.tex 
    slide_level: 2
header-includes:
   - \setbeameroption{hide notes} # notes are not shown
  #- \setbeameroption{show notes}   # notes are shown after slide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
```

## Content

* Present Master Thesis

* Material and Method to get first Results

* First Results

* Outlook

\note{
Welcome to my presentation about my master thesis, my name is Silvan.
I am here tell you what my master thesis is about, how I got my first results and what they are and what I want to do next.
}

## Master Thesis

* Predicting: Which strategy is suitable to breed for early maturity in beef cattle?

Definition

* How early ready for slaughter.

Relevance

* Increased performance in early maturity --> decreased costs.

\note{
The goal of my master thesis is to predict by using models, which breeding strategy will be most suitable to breed for early maturity in beef cattle.
Here it is important that you remember: With early maturity I mean the early readiness for slaughter.
This trait is an economically important trait for beef cattle breeders.
For example, imagine two beef carcasses which are exactly the same and get exatly the same price. 
For one carcass an animal has lived 250 d and for the other an animal has lived 230 d. 
It is obvious that the one which only lived for 230 d led to much less costs for the breeder than the one which lived for 250 d.
This animal is the one which is earlier mature than the other and this is also the animal that you should select with the breeding strategy.
}


## Master Thesis

Four Strategies with increasing complexity:

1. Carcass fat as auxilliary trait.

2. Index over carcass traits.

3. "Deviation in age at slaughter" from @Berry2017.

4. Growth models.

Starting with Strategies one and two.

\note{
However, as you can see it is not a trait which you can measure easily. This makes breeding for it difficult.
Probably due this reason breeding for early maturity is not established in any major breeding program.
Even the word early maturity has not been present in any scientific paper I read about beef breeding.
Nevertheless my supervisors have found 4 possible strategies to breed for early maturity.
I will evaluate the two most feasible and promising strategies in my master thesis.
In the first strategy you breed for early maturity in breeding for the carcass trait carcass fat.
The second strategy is not implemented yet and tries to use an index over all breeding values for multiple carcass traits to breed for early maturity.
Both are very promising because the data which they use is already available. 
Since 1992 Proviande routineley records data from beef carcass traits.
}

## Master Thesis

* Index as selection criterion 

* Selecting for most economic animal

* Main result until this stage of master thesis

## Index

$$I=a^Tu$$

where 

$a$ is the vector of economic weights --> not available,

$u$ is the vector of estimated breeding values --> available.

* Carcass conformation, carcass weight and carcass fat for calves and adults
    * Six economic weights

\note{
As the first strategy is already established I had first to create the basis for the second strategy to compare them.
In the second strategy the selection is based on an index, including all six estimated breeding values for carcass traits and six economic weighing factors.
It should allows to select the most profit yielding animal.
The economic weights determine how important the trait is for the profit.
The index is the main result I have until this stage of the thesis.
The estimated breeding values are available, but the economic weights not.
My task was to compute the economic weights to produce an index.
There I assume that breeding occurs within breeds which requires a separate index for each beef cattle breed.
To get the best overview on all beef breeds I chose to compute the index for the breeds Angus and Limousin, which are very different in carcass traits.
}

## Economic Weights

* Definition: Change in profit per change in carcass trait.

* Simplification: 
    * Costs constant
    * Price per kg carcass weight as Profit
    
* Prices from August 2018.

## Traits

* Carcass fat -> Visual fat coverage

* Carcass conformation -> Visual meat

* Carcass weight -> How heavy?

## Carcass Fat

![](~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/VK_Fett1_SK) ![](~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/VK_Fett4_SK)
Carcass Fat Classes 1 and 4

Image source: Proviande


## Carcass Fat
```{r}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CF <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/CFa_price.csv"
CF  <- read_csv2(file = CF)
colnames(CF) <- "Price"
Class <- c(1:5)
x <- cbind(CF,Class)
g <- ggplot(x,aes(Class,Price))
g + geom_bar(stat="identity")+
  theme_classic()+theme(text = element_text(size = 30))+
  ylab("Relative price in Sfr. / kg")+
  xlab("Carcass Fat Class")
```

## Carcass conformation

```{r}
knitr::include_graphics(path="~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/VK-Gruppe_CHTAX_SK_seitlich")
```
From left to right decreasing carcass conformation.

Image source: Proviande

## Carcass conformation

```{r}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CC <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/CCa_price.csv"
CC  <- read_csv2(file = CC)
colnames(CC) <- "Price"
CC <- CC-as.numeric(CC[1,])
Class <- c(1:7)
x <- cbind(CC,Class)
g <- ggplot(x,aes(Class,Price))
g + geom_bar(stat="identity")+
  theme_classic()+theme(text = element_text(size = 30))+
  ylab("Relative price in Sfr. / kg")+
  xlab("Carcass Conformation Class")
```

## Carcass weight

```{r}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
CW <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/CWa_price.csv"
CW  <- read_csv2(file = CW)
colnames(CW) <- "Price"
Thresh <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/CWa_threshold.csv"
Thresh  <- read_csv2(file = Thresh)
x <- cbind(CW,Thresh)
g <- ggplot(x,aes(threshold,Price))
g + geom_bar(stat="identity")+
  theme_classic()+theme(text = element_text(size = 30))+
  ylab("Relative price in Sfr. / kg")+
  xlab("kg Carcass Weight")
```

## Material Groups

* Calves are less than 180 d old

* Adults are between 180 and 701 d old

* Different prices and distributions

## Material Breeds

* Same prices, different distributions

* Base population from animals in 2010 - 2015

```{r BarplotInitialfrequenciesCF, echo=FALSE}
library(knitr)
library(kableExtra)
#Vectors of animal numbers Carcass fat 
#Angus with a=adults and c=calves.
Ancfc <- c(189,706,935,125,2)
Ancfa <- c(802,3415,15673,6314,481)
#Limousin with a=adults and c=calves.
Lmcfc <- c(735,1504,1419,72,0)
Lmcfa <- c(5102,21958,50705,7169,148)
#frequencies Carcass fat
#Angus with a=adults and c=calves.
Ancfc <- Ancfc/sum(Ancfc)
Ancfa <- Ancfa/sum(Ancfa)
#Limousin with a=adults and c=calves.
Lmcfc <- Lmcfc/sum(Lmcfc)
Lmcfa <- Lmcfa/sum(Lmcfa)

#Values Carcass fat classes
Vcf <- c(1:5)

#define number of rows
#x <- cbind(Vcf,Ancfc,Ancfa,Lmcfc,Lmcfa)
#colnames(x) <- c("class", "ANcalves", "ANadults", "LMcalves", "LMadults")
#kable(x, booktabs=T, caption="Population frequencies for each carcass fat class in Angus and Limousin calves and adults (Kunz, 2018)")
#x <- as.data.frame(x)
# settings barplot
library(ggplot2)
theme_set(theme_classic())
#set dataframe
x <-data.frame(Class=rep(c(1:5),times=2),Category=rep(c("Angus", "Limousin"),each=5), Frequency=c(Ancfa,Lmcfa))
# Plot
g <- ggplot(x,aes(Class,Frequency))
g + geom_bar(stat="identity", width=0.5, aes(fill=Category), position="dodge")+
  theme_classic()+theme(text = element_text(size = 30))+
  xlab("Carcass Fat Class")
```

## Method

* Model potential increase in population mean -> scaling up to one unit

* Prices from August 2018.
 

\note{
Economic weights tell you how much more money you get if a trait increases by a unit.
This money is determined by the payment system CHTAX.
CHTAX gives me a price differences per kg for the ranges in the different carcass categories.
For example the price per kilogramm is higher for the carcass class 3 than 2.
Therefore I had to modell this increase in the whole population and look how the mean price changes in the population in comparison to the initial population.
I will show you how at the example of the trait carcass fat in the breed Angus and for adults.
There I knew the population mean and standard deviation which I used to construct a normal distribution for this population.
}

## Method

```{r increase, message=FALSE, warning=FALSE}
library(ggplot2)
library(knitr)
library(kableExtra)
#Vectors of animal numbers Carcass fat 
#Angus with a=adults and c=calves.
Ancfc <- c(189,706,935,125,2)
Ancfa <- c(802,3415,15673,6314,481)
#Limousin with a=adults and c=calves.
Lmcfc <- c(735,1504,1419,72,0)
Lmcfa <- c(5102,21958,50705,7169,148)
#frequencies Carcass fat
#Angus with a=adults and c=calves.
Ancfc <- Ancfc/sum(Ancfc)
Ancfa <- Ancfa/sum(Ancfa)
#Limousin with a=adults and c=calves.
Lmcfc <- Lmcfc/sum(Lmcfc)
Lmcfa <- Lmcfa/sum(Lmcfa)

#Values Carcass fat classes
Vcf <- c(1:5)

AncfaS <- 0.74
AncfaM <- 3.1

x <- data.frame(Class=Vcf, Probability=Ancfa)
g <- ggplot(x,aes(Class,Probability,linetype="Mean"))
g + stat_function(fun = dnorm, args = list(mean = AncfaM, sd = AncfaS), aes(linetype="Initial distribution"))+
  stat_function(fun = dnorm, args = list(mean = AncfaM+0.1, sd = AncfaS),aes(linetype="New distribution"))+
    scale_linetype_manual(values=c("solid","dashed"), guide = guide_legend(title=NULL))+
  theme_classic()+
  theme(text = element_text(size = 30))
```

\note{
Here you can see the initial distribution, the mean is at class 3.
From the payment system I knew how the classes are priced.
Then I installed thresholds in the distribution which mark where the price changes.
Which was about here and there.
Using the frequencies which is the area under the graphic and multiplying it with the price I could compute the mean price per kg carcass weight.
Then I did the same for the new distribution with an increased population mean by 0.1 fat classes.
The difference between the two prices gave me the economic weight.
}

## Results

```{r}
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
SD  <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/mean_sd.csv"
SD  <- read_csv2(file = SD)

SD_LM <- SD[1:6,"Sd"]
SD_AN <- SD[7:12,"Sd"]

LM <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/LM_economic_values"
LM <- read.table(file = LM, sep=";", header=TRUE)
LM <- gather(LM,"Trait","Limousin")
LM$Limousin <- LM$Limousin*as.numeric(c(SD_LM[4,],SD_LM[3,],SD_LM[2,],SD_LM[1,],SD_LM[6,],SD_LM[5,]))

AN  <- "~/Documents/EarlyMaturityBeef/20182310_Presentation/rmd/AN_economic_values"
AN  <- read.table(file = AN, sep=";", header=TRUE)
AN <- gather(AN,"Trait","Angus")
AN$Angus <- AN$Angus*as.numeric(c(SD_AN[4,],SD_AN[3,],SD_AN[2,],SD_AN[1,],SD_AN[6,],SD_AN[5,]))

table <- inner_join(AN, LM, by="Trait")
table$Trait <- c("Calves Conformation", "Adults Conformation", "Calves Fat", "Adults Fat", "Calves Weight", "Adults Weight")
kable(table, digits=2)
```

* Negative economic weights for carcass weight

* 

\note{
Here you can see that the economically most important trait in Angus is carcass fat in calves.
}

## Discussion

* 

## Outlook

* Evaluation of Strategies

* Tool: Genetic Gain

* Genetic Gain --> Improvement of carcass traits per year

* Characterization of 2 other Strategies

\note{
Now I have got the two strategies which should help to breed for early maturity.
The next and final step in my master thesis will be to evaluate the two strategies
To do so, I will use a well-established tool: The genetic gain. 
The genetic gain predicts the development of traits under a modelled selection scenarium. 
Usually it is expressed in trait unit per year. 
The genetic gain is dependent on the generation intervall which determines how fast selection occurs, 
on the selection intensity, which determines how large the proportion of the selected population is which will produce the offspring for the next generation, 
on the standard deviation of selected criterion in the population which is the potential for breeding 
and on the accuracy of selection which is a measure of how similar the selected parents are to their progeny in the selection criterion.

These results will help to predict how suitable the two strategies are to breed for early maturity.
Thank you for your attention.
}

# Thank you

## References


