---
title: "Breeding strategies for early maturity in beef cattle"
author: "Silvan Wyss"
date: "11/22/2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Target

* Assessing strategies to breed for early maturity in beef cattle.

* Early Maturity here defined as age slaughter of an animal with minimal carcass price reductions.

* Price reductions are dependent on the pricing system CHTAX.

## CHTAX

Whithin carcass categories price reductions if:

- Carcass fat class $\neq$ 3 (optimum)

- Carcass conformation $\neq$ C (maximum)

- Carcass weight above certain limit (dependent on carcass category)

?? Graphics describing areas of price reduction along range of traits. Use Open Office.

## Why

Long-term assignment of Mutterkuh Schweiz for Qualitas AG:

?? Labels of Mutterkuh Schweiz and Qualitas AG + Image of beef cattle.

Developing breeding value estimation for beef cattle in Switzerland.

## Why

Until summer 2018 breeding focused on the traits daily gain and carcass conformation.

During this time: 

- Prooved: The trait carcass fat has decreased to significantly below class 3 in most beef cattle breeds.

?? Graphic with mean performance carcass fat along range of breeds as barplot

- Assumed: Performance in early maturity decreased as well.

## Why

Assumed negative effects for breeders and producers:

- Higher carcass price reductions for poor carcass fat performances.

- Combination of high costs and high price reductions.

Mutterkuh Schweiz: "This trend must stop."

## Why
Issue with low carcass fat classes already solved:

- Introduction of breeding value for carcass fat in summer 2018.

However, breeding strategy for early maturity not clear yet.

- Decision for a strategy is planned for 2019.

## How

Evaluation of 4 proposed approaches:

**1. Derivation from carcass fat**

**2. Index over carcass traits**

3. Derivation in age at slaughter (Berry)

4. Derivation over growth models

## How

Different results with 1. and 2.?

Comparison of 

- Animal ranks

- Genetic gains per trait

## How

- Breeding value carcass fat available

- Index computed using economic values from simple profit equations. (Show Equation with $H=a*w+a*w$)



## 

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


