---
title: "ReferenceManager How-To"
author: "Peter von Rohr"
date: "2018-09-26"
output: html_notebook
bibliography: references.bib
---

This notebook provides some examples on how to work with the package `ReferenceManager` from ropenscie.


## Documentation
The vignette seams to be available from https://arxiv.org/pdf/1403.2036v1.pdf


## Installation
The package is installed via

```{r eval=FALSE}
devtools::install_github("ropensci/RefManageR")
```

## The Plan


## Examples and Tests
Working through the examples in the vignette leads to

```{r}
s_bib_file <- system.file("Bib", "biblatexExamples.bib", package = "RefManageR")
stopifnot(file.exists(s_bib_file))
bib <- RefManageR::ReadBib(s_bib_file, check = FALSE)
print(bib[c("cms", "jcg", "ctan")], .opts = list(check.entries = FALSE))
```


## Output
Writing some records to a bibfile

```{r}
RefManageR::BibOptions(check.entries = FALSE)
RefManageR::toBiblatex(bib[c("cms", "jcg", "ctan")])
```

The whole thing is written to a file using `cat()`. 

```{r}
# cat(RefManageR::toBiblatex(bib[c("cms", "jcg", "ctan")]), file = "references.bib", sep = "\n")
RefManageR::WriteBib(bib = bib[c("cms", "jcg", "ctan")])
```

Then, we try to use the `citr`-package addin to include citations. 

The citations used with `citr` produces the following: [@jcg].

Yet anoter citation in [@ctan].

## References
