---
title: "Strategies to breed for early maturity in beef cattle"
author: "Silvan Wyss"
date: "16.8.2018"
output: html_document
bibliography: 
- library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Background

Up until summer 2018, the Swiss beef cattle breeders association has been focusing their genetic evaluations mainly on growth rate and carcass conformation. 
Lately it has been observed that carcass fat is decreasing at least for some beef cattle breeds, which leads to a price reduction of the carcass [@Hospenthal2016]. (Hier noch Graph zeigen mit Entwicklung)

Several stakeholders derive from the decreasing levels of carcass fat that Swiss beef cattle does not show any improvements in the trait early maturity. Early maturity is of high economical importance because a lower age at slaughter leads to less costs for the farmer and the environment [Berry2017] (decreased feed and environment efficiency).

```
Bitte hier Begründung, weshalb die obige Beobachtung und somit die Frühreife wichtig sind
```

### Early maturity
Terms rooting on the word mature can be confusing. 
The "rate of maturation" describes the amount of time until the adult weight is reached and the "degree of maturity" describes the proportion of the current weight to the adult weight [@Thonney2015]. 
This could lead to the definition used in trout breeding that early maturity is the amount of time until the adult weight is reached [@Kause2003].

Early maturity ("Frühreife") in this context however is defined as the amount of time until an animal meets the necessary requirements (within its category?) to be slaughtered without any price reductions per kg of carcass weight. 

```
Referenz auf andere Defintionen ==> Literatur
```
Price reductions are dependent on the price formation process in the slaughterhouse.

Since 1994 Swiss slaughterhouses value beef cattle based on the classification system CHTAX.  [Kaufmann1995]. 
The first step of valuation is placing the animal in the correct category. The distinct categories differ in physiological age at slaughter, sex and weight. 
Within each category the animal is classified in five classes of carcass fat (Tabelle) and carcass conformation ( Bild).
When the animal does not belong to the optimal class of carcass fat (3) or the maximal class of carcass conformation (C) the price per carcass weight is reduced.



### Pricing
```{r, echo=FALSE, results='hide'}
Gewicht <- 200
C3 <- 9.55
H4 <- 7.9 - 0.9
ErloesC3<-Gewicht * C3
ErloesH4<- Gewicht * H4
```


For example the price of a young bull (MT) of `r Gewicht` kg carcass weight is `r ErloesC3`.- Swiss Francs (SFr) when in the most favoured classes of carcass conformation and carcass fat and `r ErloesH4`.- SFr when in the least favoured classes [@Proviande2018]. 


### Meat quality indicators

Carcass fat and carcass conformation are used as meat quality indicators, because they correlate with important price-determining characteristics of beef meat [@Proviande2015]. 

Positiveley correlated with carcass fat:

* __Marbling (cited in [@Thonney2015])
* __Intramuscular fat content [@Kaufmann1995]
* __Tenderness [@Proviande2015]
* __Trimming effort [@Kaufmann1995]

Negativeley correlated with carcass fat:

* __Cold shortening [@Proviande2015]
* __Storage weight loss [@Proviande2015]
* __Meat yield [@Proviande2015]   

A better carcass conformation positiveley effects meat/bone proportion [@Proviande2015]. 

### CHTAX

The beef meat market in Switzerland is controlled by the sector association "Proviande". Proviande employees classify beef carcasses in large-scale slaughterhouses to determine their price. 
Their classification is based on the classification system CH-TAX [@Proviande2015] and is carried out as follows:

1. The category of the carcass is defined by physiological age at slaughter, sex and carcass weight (Own table according to table on page 5, Proviande2015). 
When weighted the carcass should be already trimmed as shown in this figure [@EDI2013, S.1].

2. The carcass is visually classified for carcass conformation and carcass fat. 
Carcass conformation describes how meaty the carcass is and carcass fat describes how fat the carcass is.

3. The price of the carcass is estimated. For carcass conformation the price is maximal at the end of the scale (C) and for carcass fat at the center of the scale (3).

### Breeding strategy

In Switzerland beef carcasses are generally much smaller than abroad in order to fulfill the wishes of the market. 
Therefore beef cattle in Switzerland has to mature earlier than abroad [@Hospenthal2016]. 

In summer 2018 the new breeding value carcass fat for beef cattle in Switzerland has been launched to meet this need in long-term.
However there may be other strategies to improve early maturity in beef cattle which could be more suitable.

To facilitate the choice this project aims at comparing the existing breeding strategy to other valable breeding strategies.










## Rate of maturation derived from carcass fat (Noch nicht überarbeitet)

Early maturity is a complex and not directly measurable trait which complicates breeding for it. 
One possibility is to derive this trait from an already recorded closely correlated trait. At the moment the trait carcass fat is used to derive the trait rate of maturity.

The first results of the routine breeding value estimation for carcass fatness have been published in summer 2018.

Carcass fat has been chosen because of two reasons. 
First it is being routineley collected in slaughterhouses since 1994 [@Kaufmann1995]. 
Second correlation is given by the fact that "cattle growth and body composition are inextricably linked" [@Thonney2015]. 
Muscels and bones decrease their growth rate with increasing body weight, but fat tissue is growing at an increasing rate with increasing body weight (Figure 21.3 Thonney) [@Thonney2015].
The older the animal the higher the proportion of fat tissue in comparison to muscle tissue and bone tissue [@Thonney2015].
This shows that over time carcass fat is generally the limiting factor to meet the requirements to be slaughtered.

Generally cattle gain weight as slightly sigmoid shaped curve (Fig. 21.1) which means that the weight gain is decreasing with increasing age. 
The adult weight is defined as the asymptotic weight of the growth curve. 
Cattle that is higher in carcass fat at a given carcass weight has higher adult weights (Figure 21.4) . 
As the adult weight decreases the growth rate generally decreases aswell at a given weight [@Thonney2015].
It has been tried to resolve the negative correlation between growth rate and rate of maturation, but often unsuccessful.




## Rate of maturation as index trait

To prevent that you can also choose to combine carcass weight, carcass conformation and carcass fat to one index which then is called early maturity or early readiness for slaughter. 
To act at best reasons to improve the income of beef cattle producers you should weight the different traits in the index according to their economic value to the cattle producers [@Englishby2017].





# Annex

Also there is the breed Limousin which underperforms in carcass fat. 
Nevertheless offspring of Limousin sires are most prevalent in the favoured category of carcass conformation C3. 
This shows that for breeding you should always combine the two traits carcass conformation and carcass fat [@Hospenthal2016]. 

Commercial cattle are generally determined as ready for slaughter by visual inspection of the degree of fatness within the appropriate range of live weight [@VanGroningen2006].

Carcass conformation correlates with carcass fat by about 0.31. 
Age at slaughter correlates positiveley with carcass fat but not linear (concave with decreasing slope) [@Hospenthal2016].

The proportion of weight to adult body weight (asymptotic weight) is degree of maturity [@Thonney2015].

The older the animal the higher the proportion of fat tissue in comparison to muscle tissue and bone tissue [@Thonney2015].

Most selection for growth changed the growth curve by decreasing or increasing adult size. 
Selection rareley changed the shape of the growth curve or the underlying biological relationships between growth and body composition [@Thonney2015].

Weights across different ages are highly correlated. Growth rates at given age are generally related to adult size [@Thonney2015].

The higher the age at slaughter of an animal is the higher is the impact of genetics on the beef carcass traits [@Englishby2017].

In Ireland the usually cross crossbred suckler cows to purebred beef sires. 
Also they use an multi-trait across breed animal model. There they include 15 traits including carcass weight and carcass fat. 
The heritability is 0.31 for carcass fat [@Evans2007].

In Switzerland the "Bundesamt für Landwirtschaft" has to determine the methods to classify carcasses of ruminants. 
The criteria are the age at slaughter, the carcass conformation and the carcass fat [@Bundesrat2002].

In order to get no selling price reductions they have to feed their animals for a longer time, when their animals do not mature early. 
However, in Switzerland the carcass should not weight too much. More than 290 kg carcass weight for MT will result in a price discount of at least 0.1.-/kg carcass weight [@Proviande2018].

# References

