---
title: "EconomicalWeigths"
author: "Silvan"
date: "2 10 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Economical Weights

Economical weights are factors to produce an aggregate genotype from multiple traits.
There is one economical weight per involved trait.
The economical weight per trait is the change in profit (Sfr.) per additional unit of the trait.

Here the aggregate genotype consists of the traits carcass fat, carcass conformation and carcass weight.
Consequently the three traits need an economical weight each.

### Carcass fat
The trait carcass fat has the unit carcass fat class (see table???).
Therefore the economical weight for carcass fat is the additional revenue per unit of carcass fat class.
I choose the unit Swiss Francs (Sfr.) per 0.1 carcass fat class.
To get the mean plus or minus of Sfr. per 0.1 carcass fat class, I need to calculate it for two mean scenarios. 
Thus, I need not assume a standard deviation of the carcass fat score in the population.
A standard deviation is characterized by the mean and the standard deviation of a value in a population.
Therefore I need the mean and the standard deviation of carcass fat scores in the population.
Here I will do the whole game for Angus and Limousin, which have different means and standard deviations

```{r StdvMeanCarcassFat, eval=FALSE}
meanAng <- 3.08
meanLim <- 2.71
stdvAng <-
stdvLim <-
```


This will be the first scenario.
The second scenario is that I shift the standard deviation to the right, so that the mean will be +0.1.
Then I just need to subtract the mean revenue from the first scenario from the mean revenue of the second scenario.
The mean revenue is determined by the price plus or minus of a carcass fat class and by how many animals are classified in the specific class.

I know the share of animals in the different carcass fat classes, but I do not know the mean price plus or minus for the different carcass fat classes.
The group "stirks" consists of the carcass categories MT, OB and RG.
Therefore I will take the mean for the price plus or minus of the three carcass categories.
At the moment it will be sufficient to use the price of the week 33 in 2018 (13.8.18).

```{r StirksMeanCarcassFat, echo=FALSE}
library(knitr)
z<-data.frame(class=c("1","2","3","4","5"))
x<-data.frame(MT=c(-0.9,-0.3,0,-0.3,-0.7), OB=c(-0.9, -0.3,0,-0.4,-0.9), RG=c(-0.9,-0.3,0,-0.5,-1))
y<-as.matrix(x)
x$mean<-rowMeans(y)
x<-cbind(z,x) 
kable(x, digits=1)
```

### Carcass Conformation

### Carcass weight
The trait carcass weight has the unit kg.
For carcass weight the price plus per kg is the same on the whole scale.
Therefore I do not need to assume a standard deviation in the population.
I just need the mean for the first scenario and the function that will tell me how much the profit will change when I change the carcass weight is one kg more.
Important: Here I assume that the carcass weight changes, without a change of age at slaughter.
The profit will be here defined as the revenue minus the fixed and variable costs.

```{r ProfitCarcassWeight, eval=FALSE}
VersProfitAnimal<- 438
KontrProfitAnimal<- 384
VersMeanCW<-
KontrMeanCW<-
pCW<- KontrProfitAnimal/
```






