---
title: "EconomicalWeigths"
author: "Silvan"
date: "2 10 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
```

## Economical Weights

Economical weights are factors to produce an aggregate genotype from multiple traits.
There is one economical weight per involved trait.
The economical weight per trait is the change in profit (Sfr.) per additional unit of the trait.
Here the aggregate genotype consists of the traits carcass fat, carcass conformation and carcass weight.
Consequently the three traits need an economical weight each.
Also aggregate genotypes have to be computed for each breed and animal group separateley.
As an example the economic values will appear for the most distinct breeds, Angus and Limousin and the group stirks.

### Carcass fat
The trait carcass fat has the unit carcass fat class (see table???).
Therefore the economical weight for carcass fat is the additional revenue per unit of carcass fat class.
I choose the unit Swiss Francs (Sfr.) per 1 carcass fat class.

#### Model
To get the minus of Sfr. per 1 carcass fat class, I need to calculate the mean price difference in a population when I change the mean carcass fat score in the population.
To do so I change the population slightly, but try to conserve the intial distribution shape.
The change should predict the possible change when breeding.

I know the initial distribution of the population over the carcass fat scores from the data of Qualitas AG.
The distribution is discrete, which means I know the share of the population within each carcass fat class.

```{r DiscreteInitialcf}
#Vectors of animal numbers Carcass fat 
#Angus with a=stirks and c=calves.
Ancfc <- c(189,706,935,125,2)
Ancfa <- c(802,3415,15673,6314,481)
#Limousin with a=stirks and c=calves.
Lmcfc <- c(735,1504,1419,72,0)
Lmcfa <- c(5102,21958,50705,7169,148)

#Shares Carcass fat
#Angus with a=stirks and c=calves.
Ancfc <- c(189,706,935,125,2)/sum(Ancfc)
Ancfa <- c(802,3415,15673,6314,481)/sum(Ancfa)
#Limousin with a=stirks and c=calves.
Lmcfc <- c(735,1504,1419,72,0)/sum(Lmcfc)
Lmcfa <- c(5102,21958,50705,7169,148)/sum(Lmcfa)

#Values Carcass fat classes
Vcf <- c(1,2,3,4,5)

#Means (M)
#Angus
AncfcM <- sum(Vcf*Ancfc)
AncfaM <- sum(Vcf*Ancfa)
#Limousin
LmcfcM <- sum(Vcf*Lmcfc)
LmcfaM <- sum(Vcf*Lmcfa)

#Standard deviations (S)
#Angus
AncfcS <- sd(Vcf*Ancfc)
AncfaS <- sd(Vcf*Ancfa)
#Limousin
LmcfcS <- sd(Vcf*Lmcfc)
LmcfaS <- sd(Vcf*Lmcfa)

#New means (M2)
#Angus
ac<- 0.01
aa<- 0.01
AncfcM2 <- AncfcM+a
AncfaM2 <- AncfaM-a
#Limousin
lc <- 0.01
la <- 0.01
LmcfcM2 <- LmcfcM+l
LmcfaM2 <- LmcfaM+l


```

Changing the mean is difficult without changing the distribution shape for a discrete distribution.
Therefore I will use the assumption that the data is normally distributed.
The initial normal distribution is defined by the mean and the standard deviation.
I will change then the mean of the normal distribution to get the normal distribution after selection.
I leave the standard deviation as it is, because it ensures that the shape of the normal distribution stays the same.
Afterwards I need to transform the normal distribution back to a discrete distribution.

#### Borders in the normal distribution to get shares in classes of second scenario.
I get the borders of the discrete distribution by the R-command `qnorm()`. 
This command gives me the quantil of the area under the normal distribution, when I know the area.
The area is the share of animals which belong to specific carcass fat classes.

```{r BordersNormDistcf}
#Borders normal distribution carcass fat 
#Angus with a=stirks and c=calves.
AncfcB<- qnorm(cumsum(Ancfc),sd=AncfcS,mean=AncfcM, lower.tail = T)
AncfaB<- qnorm(cumsum(Ancfa),sd=AncfaS,mean=AncfaM, lower.tail = T)
#Limousin with a=stirks and c=calves.
LmcfcB<- qnorm(cumsum(Lmcfc),sd=LmcfcS,mean=LmcfcM, lower.tail = T)
LmcfaB<- qnorm(cumsum(Lmcfa),sd=LmcfaS,mean=LmcfaM, lower.tail = T)
```

Then I take the normal distribution and divide it into different parts according to the computed borders.
Each part represents a fat score, the result is again a discrete distribution.
I get the shares per fat score for the population of the second scenario, when I use the R-command `pnorm()`.

```{r DiscreteSecondcf}
#Shares second mean carcass fat 
#Angus with a=stirks and c=calves.
Ancfc2<- diff(c(0,pnorm(AncfcB,sd=AncfcS,mean=AncfcM2, lower.tail = T)))
Ancfa2<- diff(c(0,pnorm(AncfaB,sd=AncfaS,mean=AncfaM2, lower.tail = T)))
#Limousin with a=stirks and c=calves.
Lmcfc2<- diff(c(0,pnorm(LmcfcB,sd=LmcfcS,mean=LmcfcM2, lower.tail = T)))
Lmcfa2<- diff(c(0,pnorm(LmcfaB,sd=LmcfaS,mean=LmcfaM2, lower.tail = T)))
Ancfa
Ancfa2
```


Afterwards I can compute the mean price in scenario 2 with the second mean.
To do so I multiply each part share of the normal distribution with the attributing price minus.
Then I can do the same with the second mean.
The difference of the two scenarios corrected by the difference of means will result in the economical weight per carcass fat score.


#### Mean price minus per carcass fat class
Then I just need to subtract the mean revenue from the initial scenario from the mean revenue of the second scenario.
The mean revenue is determined by the price plus or minus of a carcass fat class and by how many animals are classified in the specific class.

I know the share of animals in the different carcass fat classes, but I do not know the mean price plus or minus for the different carcass fat classes.
The group "stirks" consists of the carcass categories MT, OB and RG.
Therefore I will take the mean for the price plus or minus of the three carcass categories.
At the moment it will be sufficient to use the price of the week 33 in 2018 (13.8.18).

```{r PriceMeanMinusCarcassFat}
# mean price plus or minus for different carcass fat classes from Proviande 2018, week 33.
library(knitr)
z<-data.frame(class=c("1","2","3","4","5"))
x<-data.frame(MT=c(-0.9,-0.3,0,-0.3,-0.7), 
              OB=c(-0.9, -0.3,0,-0.4,-0.9), RG=c(-0.9,-0.3,0,-0.5,-1))
y<-as.matrix(x)
#compute mean over categories
x$mean<-rowMeans(y)
x<-cbind(z,x) 
kable(x, digits=1)

```

```{r ewdiscrete}
#compute price first scenario for Angus and Limousin
AnPSc1<-t(x$mean)%*%x1$Angus1
LimPSc1<-t(x$mean)%*%x1$Limousin1
#compute price second scenario for Angus and Limousin
AnPSc2<-t(jx$mean)%*%x2$Angus2
LimPSc2<-t(x$mean)%*%x2$Limousin2
#compute difference from second to first scenario
AnDiff<-AnPSc2-AnPSc1
LimDiff<-LimPSc2-LimPSc1
#economical weights in Sfr. per additional score
ewAng<-AnDiff/(meanAng2-meanAng1)
ewAng 
ewLim<-LimDiff/(meanLim2-meanLim1)
ewLim
meanAng2-meanAng1
```





### Carcass Conformation






### Carcass weight
The trait carcass weight has the unit kg.
For carcass weight the price plus per kg is the same on the whole scale.
Therefore I do not need to assume a standard deviation in the population.
I just need the mean for the first scenario and the function that will tell me how much the profit will change when I change the carcass weight is one kg more.
Important: Here I assume that the carcass weight changes, without a change of age at slaughter.
The profit will be here defined as the revenue minus the fixed and variable costs.

```{r ProfitCarcassWeight, eval=FALSE}
#profit per animal in Sfr. from @Burkard2013
VersProfitAnimal<- 438
KontrProfitAnimal<- 384
#mean carcass weight in kg as mean September of categories Stiere, Ochsen and Rinder of Agristat S.33.
k<-mean(c(298,256,260))
k
VersMeanCW<- k
KontrMeanCW<- k
#profit per mean kg carcass weight in Sfr.
pCW<- KontrProfitAnimal/VersMeanCW
pCW
```


#Annex/Jnk

```{r}
cumsum(c(1,2,3,4,5))
x <- cumsum(cumsum(1:10))
x
diff(x, lag = 2)
diff(x, differences = 2)
#shares scenarios Angus
Ang1<-c(pnorm(1.5, mean=meanAng1, sd=stdvAng, lower.tail = T) -pnorm(0.5, mean=meanAng1, sd=stdvAng,lower.tail = T),
        
        pnorm(2.5, mean=meanAng1, sd=stdvAng,lower.tail = T) -pnorm(1.5, mean=meanAng1 ),
        
        (pnorm(3, mean=meanAng1, sd=stdvAng, lower.tail = T) -pnorm(2.5, mean=meanAng1, sd=stdvAng,lower.tail = T)) + (pnorm(3, mean=meanAng1, sd=stdvAng,lower.tail = F) -pnorm(3.5, mean=meanAng1,sd=stdvAng, lower.tail = F)),
        
        pnorm(3.5, mean=meanAng1, sd=stdvAng, lower.tail = F ) -pnorm(4.5, mean=meanAng1,sd=stdvAng, lower.tail = F ),
        
        pnorm(4.5, mean=meanAng1, sd=stdvAng, lower.tail = F ) -pnorm(5.5, mean=meanAng1 ,sd=stdvAng, lower.tail = F))


Ang2<-c(pnorm(1.5, mean=meanAng2, sd=stdvAng, lower.tail = T) -pnorm(0.5, mean=meanAng2, sd=stdvAng,lower.tail = T),
        
        pnorm(2.5, mean=meanAng2, sd=stdvAng,lower.tail = T) -pnorm(1.5, mean=meanAng2 ),
        
        (pnorm(3, mean=meanAng2, sd=stdvAng, lower.tail = T) -pnorm(2.5, mean=meanAng2, sd=stdvAng,lower.tail = T)) + (pnorm(3, mean=meanAng2, sd=stdvAng,lower.tail = F) -pnorm(3.5, mean=meanAng2,sd=stdvAng, lower.tail = F)),
        
        pnorm(3.5, mean=meanAng2, sd=stdvAng, lower.tail = F ) -pnorm(4.5, mean=meanAng2,sd=stdvAng, lower.tail = F ),
        
        pnorm(4.5, mean=meanAng2, sd=stdvAng, lower.tail = F ) -pnorm(5.5, mean=meanAng2 ,sd=stdvAng, lower.tail = F))
```




