---
title: "EconomicalWeigths"
author: "Silvan"
date: "2 10 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Economical Weights

Economical weights are factors to produce an aggregate genotype from multiple traits.
There is one economical weight per involved trait.
The economical weight per trait is the change in profit (Sfr.) per additional unit of the trait.

Here the aggregate genotype consists of the traits carcass fat, carcass conformation and carcass weight.
Consequently the three traits need an economical weight each.

### Carcass fat
The trait carcass fat has the unit carcass fat class (see table???).
Therefore the economical weight for carcass fat is the additional revenue per unit of carcass fat class.
I choose the unit Swiss Francs (Sfr.) per 1 carcass fat class.

#### Discrete distribution
To get the mean plus or minus of Sfr. per 1 carcass fat class, I need to calculate it for two mean scenarios with the discrete distribution of the right shape.
A discrete distribution is characterized by different areas of a scale and the share of records that belong to the different areas.
The areas for carcass fat score are the different scores and the share of records are the share of carcasses that belonged to the different scores.
Here I will do the whole game for Angus and Limousin, which have different shares in the fat scores.

```{r StdvMeanCarcassFat}
# scores (phenotypic) in Limousin and Angus.
#shares of carcasses in the different fat scores
library(knitr)
z<-data.frame(class=c(1,2,3,4,5))
c(3,12.5,58,24,2.5)/100
sum(c(5,26,60,9,0))
c(5,26,60,9,0)/100
x1<-data.frame(class=c(1,2,3,4,5),Angus1=c(0.030, 0.125, 0.580, 0.240, 0.025), Limousin1=c(0.05, 0.26, 0.60, 0.09, 0.00))
#old means
(meanAng1 <- mean(x1$Angus1*x2$class))
(meanLim1 <- mean(x1$Limousin1*x2$class))
#how much i take of 1 and 2 and how much I put to 4 and 5 (d)
d<-0.1
#new shares after transformation
x2<-data.frame(class=c(1,2,3,4,5),Angus2=c(0.030, 0.125, 0.580+2*d, 0.240-d, 0.025-d), Limousin2=c(0.05-d, 0.26-d, 0.60+2*d, 0.09, 0.00))
#new means
(meanAng2 <- mean(x2$Angus2*x2$class))
(meanLim2 <- mean(x2$Limousin2*x2$class))

```


This will be the first scenario.
The second scenario is that I shift the deviation to the right, so that the mean will be a little above the mean of the first scenario.
Then I just need to subtract the mean revenue from the first scenario from the mean revenue of the second scenario.
The mean revenue is determined by the price plus or minus of a carcass fat class and by how many animals are classified in the specific class.

I know the share of animals in the different carcass fat classes, but I do not know the mean price plus or minus for the different carcass fat classes.
The group "stirks" consists of the carcass categories MT, OB and RG.
Therefore I will take the mean for the price plus or minus of the three carcass categories.
At the moment it will be sufficient to use the price of the week 33 in 2018 (13.8.18).

```{r PriceMeanMinusCarcassFat}
# mean price plus or minus for different carcass fat classes from Proviande 2018, week 33.
library(knitr)
z<-data.frame(class=c("1","2","3","4","5"))
x<-data.frame(MT=c(-0.9,-0.3,0,-0.3,-0.7), OB=c(-0.9, -0.3,0,-0.4,-0.9), RG=c(-0.9,-0.3,0,-0.5,-1))
y<-as.matrix(x)
#compute mean over categories
x$mean<-rowMeans(y)
x<-cbind(z,x) 
kable(x, digits=1)

```

```{r ewdiscrete}
#compute price first scenario for Angus and Limousin
AnPSc1<-t(x$mean)%*%x1$Angus1
LimPSc1<-t(x$mean)%*%x1$Limousin1
#compute price second scenario for Angus and Limousin
AnPSc2<-t(x$mean)%*%x2$Angus2
LimPSc2<-t(x$mean)%*%x2$Limousin2
AnPSc2
LimPSc2
#compute difference from second to first scenario
AnDiff<-AnPSc2-AnPSc1
LimDiff<-LimPSc2-LimPSc1
#economical weights per additional score
ewAng<-AnDiff/(meanAng2-meanAng1)
ewAng 
ewLim<-LimDiff/(meanLim2-meanLim1)
ewLim
```

#### Normal distribution
I can do the same but assuming a normal distribution instead of the empiric discrete distribution.
The normal distribution is determined by mean and standard deviation.
```{r NormDistMeanStdv}
#Angus mean
meanAng1
#Limousin mean
meanLim1
#Angus standard deviation
stdvAng<-0.74
#Limousin standard deviation
stdvLim<-0.71
```

Then I take the normal distribution and divide it into different parts.
Each part represents a fat score. 
Afterwards I can compute the mean price in scenario 1 with the first mean.
To do so I multiply each part share of the normal distribution with the attributing price minus.
Then I can do the same with the second mean.
The difference of the two scenarios corrected by the difference of means will result in the economical weight per carcass fat score.

```{r}

```


### Carcass Conformation

### Carcass weight
The trait carcass weight has the unit kg.
For carcass weight the price plus per kg is the same on the whole scale.
Therefore I do not need to assume a standard deviation in the population.
I just need the mean for the first scenario and the function that will tell me how much the profit will change when I change the carcass weight is one kg more.
Important: Here I assume that the carcass weight changes, without a change of age at slaughter.
The profit will be here defined as the revenue minus the fixed and variable costs.

```{r ProfitCarcassWeight, eval=FALSE}
#profit per animal in Sfr. from @Burkard2013
VersProfitAnimal<- 438
KontrProfitAnimal<- 384
#mean carcass weight in kg as mean September of categories Stiere, Ochsen and Rinder of Agristat S.33.
k<-mean(c(298,256,260))
k
VersMeanCW<- k
KontrMeanCW<- k
#profit per mean kg carcass weight in Sfr.
pCW<- KontrProfitAnimal/VersMeanCW
#economical weight for carcass weight (Sfr./kg Carcass weight)
ewCW<- (VersProfitAnimal+1)/VersMeanCW - VersProfitAnimal/VersMeanCW 
ewCW
```






